---
title: "Predicting Binary Climbing"
#output: html_notebook
---


# Predicting climbing from fossil data:

This has been modified on 20250320 up to the "combined" portion.

I have predictions for each fossil for each measurement, but I don't have the combined ones yet. That will require making another `formula` column using the code from the `Fossil_Mass_Predictions_Claude.Rmd` file.

Right now, `pred_all`, saved as `Binary_Preds.csv`, is ready to plot for each fossil species. 

```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, brms, cmdstanr, here, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))


#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```


### Load Data  

```{r}
pred_all <- read_csv(here("Data","Binary_Preds.csv"))
```



### function
```{r}
# shading
shades <- data.frame(xmin=seq(1.5,15-1.5, 2),
                     xmax=seq(2.5,15+.5, 2),
                     ymin=-Inf, ymax=Inf)

hplot <- function(groups, method){
  pred_all %>% mutate(var = recode(var, combined = "Multiple\nRegression")) %>% 
    filter(Genus_species %in% {{groups}},
                         method == {{method}}) %>% 
    mutate(var =  as.factor(var)) %>% 
    mutate(Genus_species = gsub("_", " ", Genus_species)) %>% 
  ggplot(aes(y = Prob_of_Climbing, 
             x = fct_relevel(var,var_acc), 
             #color = Genus_species,
             shape = Genus_species,
             #y = var,
             )) +
  geom_hline(yintercept = 0.5, linetype = 2, linewidth = 0.35, color = "grey30") +
  stat_pointinterval(#.width = c(0.5, 0.68268),
                     #.width = c(0.5, 0.8),
                     .width = 0.8,
                     color = "grey15",
                      linewidth = 1.7,
                     position = position_dodge(width = -.8)#,
                     #aes(shape = Genus_species, fill = Genus_species)
                     ) + 
    ylim(0,1) +
    labs(x = "", y = "Probability of Climbing") +
  #scale_color_manual(values = pal) 
    theme_pander(gM = F) + 
    scale_shape_manual(values = c(1, 15, 17, 19, 8)) +
    geom_rect(inherit.aes = F, 
              data = shades, 
              mapping = aes(xmin=xmin, 
                            xmax=xmax, 
                            ymin = ymin, 
                            ymax = ymax), 
              vjust = -0.2,
              alpha = 0.125) +
  scale_y_continuous(limits = c(0,1), expand = c(0.02, 0.02)) +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.border = element_rect(colour = "grey40", fill=NA, size=0.7),
        legend.text = element_text(face = "italic"),
        legend.title=element_blank()) +
    guides(shape = guide_legend(override.aes = list(size=8)))
}

```


### Big Plot
```{r}
pl5 <- hplot(old, "Fossil") + 
  ggtitle("Mesozoic Therian Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank(),
        panel.grid.major.y = element_blank())

pl6 <- hplot(multi, "Fossil") + 
  ggtitle("Multituberculate Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines")) +
  labs(y = "Probability", x = "")

pl7 <- hplot(primate, "Fossil") + 
  ggtitle("Plesiadapiform Predicitons") + 
  theme(#axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())


t3 <- pl5 / pl6 /pl7

t3

ggsave(here("Plots", "Bin_Pred_Fossil.pdf"), height = 8, width = 13)
ggsave(here("Plots", "Bin_Pred_Fossil.jpg"), height = 8, width = 13)
ggsave(here("Plots", "Figure_5.png"), height = 8, width = 13)
```


```{r}
pl1 <- hplot(extant_climb, "Full") + 
  ggtitle("Climbing species predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl2 <- hplot(extant_climb, "Fossil") + 
  ggtitle("Climbing species predictions without phylogenetic information") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl3 <- hplot(extant_ground, "Full") + 
  ggtitle("Non-climbing species predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl4 <- hplot(extant_ground, "Fossil") + 
  ggtitle("Non-climbing species predictions without phylogenetic information") + 
  theme(#axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),)


t1 <- pl1 / pl2 + plot_layout(guides = "collect")

t2 <- pl3 / pl4 + plot_layout(guides = "collect")

wrap_plots(t1, t2, ncol = 1) + plot_annotation(tag_levels = "a")

ggsave(here("Plots", "Bin_Pred_Extant.pdf"), height = 10, width = 13)
ggsave(here("Plots", "Bin_Pred_Extant.jpg"), height = 10, width = 13)
ggsave(here("Plots", "Figure_3.png"), height = 10, width = 13)
```

