---
title: "Binary Multiple Predictors"
#output: html_notebook
---

Running predictions with multiple predictors based on a dag. This means using **ALL** the top 12 predictors in one model, along with size. No Interactions. Log Mass must be used as I don't have GM for the fossils.

# Preparation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))

source(here("Code","Name_Change.R"))
```

### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  filter(Genus_species !=  c('Leopardus_geoffroyi', 
                             'Urocyon_cinereoargenteus')) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family))
#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

# Model Fits

Get lists of missing fossil data
```{r}
read_csv(here("Data", "Fossil_Master.csv")) %>% 
  group_by(Genus_species) %>% 
  summarise_at(14:93, mean, na.rm = T) %>% 
  select(c(Genus_species, PES2, HPI, PES, MANUS, 
           Ppl, Hl, OLI, Pipl, MANUS2, Rl, Ipl, 
           Uol, Fl, Ul)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  mutate(nas = rowSums(is.na(.)) ) %>% 
  arrange(nas) 
# Unhash to view the matrix of missing measurements in th RStudio viewer
 # %>% 
 # view() 
```

### Model1

#### J. kielanae
#### P. cookei
#### All Extant
```{r  }

bin_mod <-  bf(Loc_bin ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(MANUS2) + mi(HPI) + mi(Ipl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()
  
PES2_mod <- bf(PES2| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

MANUS_mod <- bf(MANUS| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

PES_mod <- bf(PES| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

Ppl_mod <- bf(Ppl| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

MANUS2_mod <- bf(MANUS2| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

HPI_mod <- bf(HPI| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

Ipl_mod <- bf(Ipl| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

Pipl_mod <- bf(Pipl| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

m_form <- bin_mod + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + MANUS2_mod + HPI_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
  
pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

mod1 <- brm(m_form,
                    data=dat,
                    refresh = 0,
                    cores = 4,
                    data2 = list(A = A),
                    prior = pri,
                    seed = 145,
                    control=list(max_treedepth=15)
               )
```


```{r  message = FALSE, warning=FALSE, include = FALSE}
prio <- function(mod){
  get_prior({{mod}},
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))
}
```


### Model 2
No HPI
#### S. szalayi
#### E. scansoria
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod2 <- bf(Loc_bin ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(MANUS2) + mi(Ipl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()


m2_form <- bin_mod2 + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + MANUS2_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
                    
pri = prio(m2_form)

mod2 <- brm(m2_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```


## Model 3 
No PES2, HPI, PES
#### A. zhoui
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod3 <-  bf(Loc_bin ~  mi(MANUS) +  mi(Ppl) + mi(MANUS2)  + mi(Ipl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m3_form <- bin_mod3 +  MANUS_mod  + Ppl_mod + MANUS2_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m3_form)

mod3 <- brm(m3_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```

##Model 4 
no HPI, Ipl, MANUS2
#### R. eurasiaticus
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod4 <- bf(Loc_bin ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m4_form <- bin_mod4 + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + Pipl_mod + set_rescor(FALSE)
            
pri = prio(m4_form)

mod4 <- brm(m4_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```

## Model 5 
no PES2, PES, Pipl
#### I. clarkforkensis
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod5 <-  bf(Loc_bin ~  mi(MANUS) +  mi(Ppl) + mi(MANUS2) + mi(HPI) + mi(Ipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m5_form <- bin_mod5  + MANUS_mod + Ppl_mod + MANUS2_mod + HPI_mod + Ipl_mod + set_rescor(FALSE)
           
pri = prio(m5_form)

mod5 <- brm(m5_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```


#### Model 6 
no HPI, OLI, Uol, Ul
#### Dryomomys_szalayi
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod6 <-  bf(Loc_bin ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(MANUS2) +  mi(Ipl) + mi(Pipl) + Hl + Rl  + Fl  + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m6_form <- bin_mod6 + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + MANUS2_mod + HPI_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m6_form)

mod6 <- brm(m6_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```

## Model 7
#### Kryptobaatar_dashzevegi
no MANUS, Ppl, MANUS2, Ipl
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod7 <-  bf(Loc_bin ~ mi(PES2) + mi(PES) + mi(HPI) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m7_form <- bin_mod7 + PES2_mod +  PES_mod  + HPI_mod  + Pipl_mod + set_rescor(FALSE)
         
pri = prio(m7_form)

mod7 <- brm(m7_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```


## Model 8
#### J. sinensis
#### C. jiufotangensis
no PES, HPI, PES2, Pipl, Fl
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod8 <-  bf(Loc_bin ~  mi(MANUS) + mi(Ppl) + mi(MANUS2) + mi(Ipl) + Hl + Rl + Ul + Uol + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m8_form <- bin_mod8 + MANUS_mod + Ppl_mod + MANUS2_mod + Ipl_mod + set_rescor(FALSE)
         
pri = prio(m8_form)

mod8 <- brm(m8_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```

## Model 9
#### F. primaevus
No PES2, PES, MANUS, Ppl, MANUS2, Pipl
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod9 <-  bf(Loc_bin ~  mi(HPI) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m9_form <- bin_mod9 +  HPI_mod + set_rescor(FALSE)
           
pri = prio(m9_form)

mod9 <- brm(m9_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```

## Model 10
#### P. kummae
No HPI, MANUS, Ppl, Hl, OLI, MANUS2, Rl, Ipl, Uol, Ul
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod10 <-  bf(Loc_bin ~ mi(PES2) + mi(PES) + mi(Pipl) + Fl +  log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m10_form <- bin_mod10 + PES2_mod +  PES_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m10_form)

mod10 <- brm(m10_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```


## Model 11
#### T. wilsoni
only Ppl and Uol
```{r  message = FALSE, warning=FALSE, include = FALSE}
bin_mod11 <- bf(Loc_bin ~  mi(Ppl) + Uol + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + bernoulli()

m11_form <- bin_mod11 + Ppl_mod + set_rescor(FALSE)
           
pri = prio(m11_form)

mod11 <- brm(m11_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, control=list(max_treedepth=15)
               )
```

## Save Models
```{r}
list_b2 <- lst(mod1, mod2, mod3, mod4, mod5, mod6, mod7, mod8, mod9, mod10, mod11) %>% write_rds(here("Data","B_lm_mods_multi.Rds"))
```

# Predicting climbing from fossil data:

Take model lists, then use them one by one to predict climbing in the fossil taxa.
`#``{r message = FALSE, warning=FALSE, include = FALSE}

nms <- read_rds(here("Data", "Order_Names.Rds"))

source(here("Code","Name_Change.R"))
```


### Load Data  

```{r}
dat <- read_csv(here("Data", "Extant_Master.csv"))

fdat <- read_csv(here("Data", "Fossil_Master.csv")) %>% group_by(Genus_species) %>% 
                  summarise_at(14:93, mean, na.rm = T) %>% view()

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

#variables to do fossil predictions with
pred_vars <- fdat_cln[c(9:84)]

```
### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements. 

```{r}
list_b2 <- lst(mod1, mod2, mod3, mod4, mod5, mod6, mod7, mod8, mod9, mod10, mod11)
```
Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model

# Predictions  

```{r}
extant_climb <- c("Caluromys_derbianus", "Tamiasciurus_douglasii","Tupaia_glis", "Cynocephalus_volans", "Glaucomys_sabrinus")

extant_ground <- c("Solenodon_paradoxus", "Atelerix_albiventris",     "Sorex_trowbridgii", "Thomomys_bottae", "Monodelphis_domestica")

old <- c("Eomaia_scansoria", "Sinodelphys_szalayi", "Juramaia_sinensis", "Cokotherium_jiufotangensis", "Ambolestes_zhoui")

multi <- c("Rugosodon_eurasiaticus", "Jeholbaatar_kielanae", "Filikomys_primaevus", "Ptilodus_kummae", "Kryptobaatar_dashzevegi")

primate <- c("Plesiadapis_cookei", "Torrejonia_wilsoni", "Ignacius_clarkforkensis", "Dryomomys_szalayi")

model_dat <- dat %>% filter(Genus_species %in% c(extant_climb, extant_ground))
```

## Extant

```{r}
pred_df_ext_full <- mod1 %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))
    

pred_df_ext_fos <- mod1 %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))
```

## Extinct

```{r}
pred_ext <- function(mod, dat) {
  {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
  mutate(method = "Fossil",
         substrate = NA)
}


df1 <- pred_ext(mod1, fdat %>% filter(Genus_species %in% c('Jeholbaatar_kielanae', 'Plesiadapis_cookei')))

df2 <- pred_ext(mod2, fdat %>% filter(Genus_species %in% c('Eomaia_scansoria', 'Sinodelphys_szalayi')))

df3 <- pred_ext( mod3, fdat %>% filter(Genus_species %in% c('Ambolestes_zhoui')))

df4 <- pred_ext(mod4, fdat %>% filter(Genus_species %in% c('Rugosodon_eurasiaticus')))

df5 <- pred_ext(mod5, fdat %>% filter(Genus_species %in% c('Ignacius_clarkforkensis')))

df6 <- pred_ext(mod6, fdat %>% filter(Genus_species %in% c('Dryomomys_szalayi')))

df7 <- pred_ext(mod7, fdat %>% filter(Genus_species %in% c('Kryptobaatar_dashzevegi')) %>% 
                  select(-Specimen_Num) %>% 
                  mutate(Specimen_Num = "mean_values") %>%
                  group_by(Genus_species, Specimen_Num) %>% 
                  summarise_at(14:93, mean, na.rm = T))

df8 <- pred_ext(mod8, fdat %>% filter(Genus_species %in% c('Juramaia_sinensis', 'Cokotherium_jiufotangensis')))

df9 <- pred_ext(mod9, fdat %>% filter(Genus_species %in% c('Filikomys_primaevus')))

df10 <- pred_ext(mod10, fdat %>% filter(Genus_species %in% c('Ptilodus_kummae')))

df11 <- pred_ext(mod11, fdat %>% filter(Genus_species %in% c('Torrejonia_wilsoni')))

pred_df <- bind_rows(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11) %>% mutate(var = 'combined')

rm(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11)
```


```{r}

pred_all <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_df) %>% #filter(var %in% var_acc) %>% 
  mutate(draw = rep(1:4000, times = nrow(.)/4000)) %>% 
  #THIS IS AVERAGING PER SPECIES
  group_by(substrate, method, Genus_species, draw) %>% 
  summarize(Prob_of_Climbing = mean(Prob_of_Climbing, na.rm = TRUE)) %>% ungroup() %>% mutate(var = "combined") %>% 
  write_csv(here("Data", "Binary_Mult_Preds.csv"))

```

# Whole Shebang  


### function
```{r}

hplot <- function(groups, method){
  pred_all %>% filter(Genus_species %in% {{groups}},
                         method == {{method}}) %>% 
  ggplot(aes(y = Prob_of_Climbing, 
             x = Genus_species, 
             #y = var,
             color = Genus_species)) +
  geom_hline(yintercept = 0.5, linetype = 2, linewidth = 0.5) +
  stat_pointinterval(.width = c(0.5, 0.68268), 
                     #linewidth = c(0.75, 0.5), 
                     position = position_dodge(width = -.6)) + ylim(0,1) +
    labs(x = "", y = "Probability of Climbing") +
  scale_color_manual(values = pal) + theme_bw() + 
  theme(axis.text.x=element_text(angle=45, hjust=1))
}

```

###  big df



### Big Plot
```{r}
pl5 <- hplot(old, "Fossil") + 
  ggtitle("Mesozoic Mammal Predictions") 

pl6 <- hplot(multi, "Fossil") + 
  ggtitle("Multituberculate Predicitons") 

pl7 <- hplot(primate, "Fossil") + 
  ggtitle("Primate Predicitons") 


t3 <- pl5 / pl6 /pl7

t3

ggsave(here("Plots", "Predict_Bin_Mult_Fossil.pdf"), height = 8, width = 13)

```


```{r}
pl1 <- hplot(extant_climb, "Full") + 
  ggtitle("Extant Climb Full Predictions") 

pl2 <- hplot(extant_climb, "Fossil") + 
  ggtitle("Extant Climb Fossil") 

pl3 <- hplot(extant_ground, "Full") + 
  ggtitle("Extant Ground Full Predictions") 

pl4 <- hplot(extant_ground, "Fossil") + 
  ggtitle("Extant Ground Fossil") 


t1 <- pl1 / pl2 + plot_layout(guides = "collect")

t2 <- pl3 / pl4 + plot_layout(guides = "collect")

wrap_plots(t1, t2, ncol = 1)

ggsave(here("Plots", "Predict_Bin_Mult_Extant.pdf"), height = 10, width = 8)

```

```{r}
pl2 / pl4 + plot_layout(guides = "collect")

ggsave(here("Plots", "Predict_Bin_Mult_Extant2.pdf"), height = 6, width = 13)
```



```{r}
wrap_plots(t1, t2, t3, ncol = 1, heights = c(2/7, 2/7, 3/7))

ggsave(here("Plots", "Predict_Bin_Mult_All.pdf"), height = 16, width = 13)
```
