---
title: "R Notebook"
#output: html_notebook
---

# Plotting the Binary Int Mass Model results

Focus on Effect size of the predictor

Packages and Data
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes, ggstar, tidytext, grid)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))

# Models

list_b_lm <- read_rds(here("Data","B_lm_mods_mis.Rds"))
list_b_gm <- read_rds(here("Data","B_gm_mods_mis.Rds"))
list_b_ratio <- read_rds(here("Data","B_ratio_mods_mis.Rds"))

accs <- read_rds(here("Data", "Accuracy_list.rds"))
```



some colors
```{r}
pal = c('#66a61e', '#7570b3',  '#e6ab02', '#62361B')

binpal = c('#66a61e','#5e1ea6')#5e1ea6

cols = c("#7570b3" ,  "#85D4E3" , "#0D7E9A",'#f5f5cb', '#c7e6d4', '#8cd2cd', '#55c3cf', '#3fa4b0', '#187389','#f48a1a', '#e6ab02', '#66a61e', '#85D4E3', '#0D7E9A', '#7570b3','#f6d03d', '#fe7b30', '#ef4a27', '#f384f8', '#625afc', '#0d57ff', '#47a7ff','#5771ff', '#6bae9e', '#31c1bb', '#7af1e1', '#d5e1af', '#f48130','#C60C30', '#00A1DE', '#62361B', '#009B3A', '#f9581c', '#522398', '#E27EA6', '#F9E300', '#565A5C')
pal2 <- LaCroixColoR::lacroix_palette("Orange", n = 30, type = "continuous")[c(1,5,10,12,13,14,15,16,17,18,25,28)]
```

# Forest Plots

Here i'm focusing on the slope of the phenotype

## Extract Slopes  

#### Helper Functions

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[2] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[17] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[17]))

linear = c("Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw", "Ipl", "Pppl", "Mtl", "Ppl", "Mcl", "Tpw", "Isl", "Il", "Pel", "Hpw", "Mcw", "Cl", "Ppw", "Pipl")

index = c("SI", "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "MANUS2",  "PES", "MANUS",  "PRTI", "HPI", "MRI",  "PES2",  "MANUS3")

log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

## Log-Mass Models

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
lms <- map(list_b_lm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_lm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms <- lms %>% bind_rows(lms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(lms2)
```

## Geometric Mean Models  

```{r message = FALSE, warning=FALSE}

# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
gms <- map(list_b_gm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

gms2 <- map(list_b_gm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

gms <- gms %>% bind_rows(gms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA))

rm(gms2)
```

## Ratio Models
Includes functional indices and log-shape ratios

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[2] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[16] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[16]))

linear = c("Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw", "Ipl", "Pppl", "Mtl", "Ppl", "Mcl", "Tpw", "Isl", "Il", "Pel", "Hpw", "Mcw", "Cl", "Ppw", "Pipl")

index = c("SI", "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "MANUS2",  "PES", "MANUS",  "PRTI", "HPI", "MRI",  "PES2",  "MANUS3")

log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
rs <- map(list_b_ratio[2:22], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

rs2 <- map(list_b_ratio[23:44], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

rs <- rs %>% bind_rows(rs2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Functional Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(rs2)
```

## Plot Color

### Plot All
Plotting the metric effect sizes for all metrics, broken up by "type"
```{r}

ms <- bind_rows(lms %>% mutate(mass = "lm"), gms %>% mutate(mass = "gm"), rs %>% mutate(mass = "none"))


ms %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% ungroup() %>% group_by(type)  %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean, shape = mass)) +
  stat_pointinterval(.width = c(.66, .89), 
                     position = position_dodge(width = .75)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  #scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~type, scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))#,
        #legend.position="none")

ggsave(here("Plots", "B_Effects_All.pdf"), height = 8, width = 9)
ggsave(here("Plots", "Bin_Effects_All.jpg"), height = 8, width = 9)
```

### Plot Accurate Predicitons

Plotting accurate predictions
Baed on the `Binary_Prediction_Accuracy` script, these all have an accuracy over 70%. It's worth noting that all of the log-shape-ratios have not-great accuracy except lsPpl.

```{r}
accurate = c("PES2", "HPI", "PES", "MANUS", "Ppl", "Hl", "OLI", "Pipl", "MANUS2", "FEB", "Rl", "Ipl", "Uol", "Fl", "Ul", "Mtl",  "lsPpl", "lsCl", "lsUol", "lsIsl", "lsMtl", "lsTpw", "lsIpl", "lsRl", "lsUl")
```

```{r}
ms %>% filter(var %in% accurate) %>% 
  group_by(mass, var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, val, type), color = mean, shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  #scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~factor(type, levels=c('Log-Shape Ratio','Functional Index','Linear Measurement')), scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))


ggsave(here("Plots", "B_Effects_Some.pdf"),  height = 3, width = 9)
ggsave(here("Plots", "B_Effects_Some.jpg"),  height = 3, width = 9)
```

ppp
grid.force()
grid.ls()

grid.remove('key-5-1-bg.6-2-6-2')
grid.remove('key-5-1-1.6-2-6-2')
grid.remove('label-5-3.6-4-6-4')

## Plot BW

### Plot All
Plotting the metric effect sizes for all metrics, broken up by "type"
```{r}

ms <- bind_rows(lms %>% mutate(mass = "lm"), gms %>% mutate(mass = "gm"), rs %>% mutate(mass = "none"))


ms %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 0.8) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~factor(type, levels=c('Log-Shape Ratio','Functional Index','Linear Measurement')), scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))#,
        #legend.position="none")

ggsave(here("Plots", "B_Effects_All_BW.pdf"), height = 8, width = 9)
ggsave(here("Plots", "Bin_Effects_All_BW.jpg"), height = 8, width = 9)
```

### Plot Accurate Predicitons

Plotting accurate predictions
Based on the `Binary_Prediction_Accuracy` script, these all have an accuracy over 70%. It's worth noting that all of the log-shape-ratios have not-great accuracy except lsPpl.


```{r}
ms %>% filter(var %in% accurate) %>% 
  group_by(mass) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, val, type, fun = mean), shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~factor(type, levels=c('Log-Shape Ratio','Functional Index','Linear Measurement')), scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))


ggsave(here("Plots", "B_Effects_Some_BW.pdf"), height = 3, width = 9)
ggsave(here("Plots", "B_Effects_Some_BW.jpg"), height = 3, width = 9)
```
### Plot Accurate v2

Plotting accurate predictions using patchwork. 

```{r}
source(here("Code","Name_Change.R")) # nm_change function

pa1 <- ms %>% filter(var %in% accurate, type =='Log-Shape Ratio') %>% 
  mutate(var = str_remove(var, '^ls')) %>% 
  nm_change() %>% group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type))) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_y_reordered("") +
  labs(x = "") +
  artyfarty::theme_scientific() +
  labs(title = "Log-Shape Ratios") +
  xlim(-6, 5) +
  theme(strip.background = element_blank(),
        plot.margin = unit(c(0.2, 0, 0.3, 0), "lines"),
        axis.title.x = element_text(size = 6, margin=margin(0,0,-3,0)),
        plot.title = element_text(hjust = 0)) +
  guides(shape = guide_legend(override.aes = list(size=8)))

pa2 <- ms %>% filter(var %in% accurate, type =='Functional Index') %>% 
  #mutate(var = str_remove(var, '^ls')) %>% 
  nm_change() %>% group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type))) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_y_reordered("") +
  labs(x = "") +
  xlim(-6, 5) +
  artyfarty::theme_scientific() +
  labs(title = "Functional Index") +
  theme(strip.background = element_blank(),
        plot.margin = unit(c(0.2, 0, 0.3, 0), "lines"),
        axis.title.x = element_text(size = 6, margin=margin(0,0,-3,0)),
        plot.title = element_text(hjust = 0)) +
  guides(shape = guide_legend(override.aes = list(size=8)))

pa3 <- ms %>% filter(var %in% accurate, type =='Linear Measurement') %>% 
  nm_change() %>% group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type),  shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_y_reordered("") +
  xlim(-6, 5) +
  labs(x = "Phenotypic predictor effect size", title = "Linear Measurements") +
  scale_shape_manual(values=c("lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  theme(strip.background = element_blank(),
        plot.margin = unit(c(0.2, 0, 0.3, 0), "lines"),
        axis.title.x = element_text(margin=margin(0,0,-3,0)),
        plot.title = element_text(hjust = 0)) +
  guides(shape = guide_legend(override.aes = list(size=8)))



(pa1 / pa2 / pa3) 

ggsave(here("Plots", "B_Effects_Somev2_BW.pdf"), height = 11, width = 8)
ggsave(here("Plots", "B_Effects_Somev2_BW.jpg"), height = 11, width = 8)
```




# Mass Plots

## Extract Slopes  

#### Helper Functions

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[3] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[3] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[17]))

linear = c("Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw", "Ipl", "Pppl", "Mtl", "Ppl", "Mcl", "Tpw", "Isl", "Il", "Pel", "Hpw", "Mcw", "Cl", "Ppw", "Pipl")

index = c("SI", "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "MANUS2",  "PES", "MANUS",  "PRTI", "HPI", "MRI",  "PES2",  "MANUS3")

log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

## Log-Mass Models

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
lms <- map(list_b_lm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""), mass = "lm")

lms2 <- map(list_b_lm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""), mass = "lm")

lms <- lms %>% bind_rows(lms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(lms2)
```

## Geometric Mean Models  

```{r message = FALSE, warning=FALSE}

# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
gms <- map(list_b_gm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""), mass = "gm")

gms2 <- map(list_b_gm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""), mass = "gm")

gms <- gms %>% bind_rows(gms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA))

rm(gms2)
```

```{r}
mas <- bind_rows(lms, gms)
```

## Plot ALl

```{r}

mas %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean)) +
  stat_pointinterval(.width = c(.66, .89), 
                     position = position_dodge(width = .75)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  #scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~mass, scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))#,
        #legend.position="none")

ggsave(here("Plots", "B_Mass_All.pdf"), height = 8, width = 9)
ggsave(here("Plots", "Bin_Mass_All.jpg"), height = 8, width = 9)
```

