---
title: "Binary Interaction Plotting"
output: html_notebook
---


There are two parts: Probability plots and Forest Plots

Packages and Data
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes, ggstar)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))

source(here("Code","Name_Change.R"))

# Models

list_b_lm <- read_rds(here("Data","B_lm_int_mods_mis.Rds"))
list_b_gm <- read_rds(here("Data","B_gm_int_mods_mis.Rds"))
```



some colors
```{r}
pal = c('#66a61e', '#7570b3',  '#e6ab02', '#62361B')

binpal = c('#66a61e','#5e1ea6')#5e1ea6

cols = c("#7570b3" ,  "#85D4E3" , "#0D7E9A",'#f5f5cb', '#c7e6d4', '#8cd2cd', '#55c3cf', '#3fa4b0', '#187389','#f48a1a', '#e6ab02', '#66a61e', '#85D4E3', '#0D7E9A', '#7570b3','#f6d03d', '#fe7b30', '#ef4a27', '#f384f8', '#625afc', '#0d57ff', '#47a7ff','#5771ff', '#6bae9e', '#31c1bb', '#7af1e1', '#d5e1af', '#f48130','#C60C30', '#00A1DE', '#62361B', '#009B3A', '#f9581c', '#522398', '#E27EA6', '#F9E300', '#565A5C')

pal2 <- LaCroixColoR::lacroix_palette("Orange", n = 30, type = "continuous")[c(1,5,10,12,13,14,15,16,17,18,25,28)]
```


Here i'm focusing on the slope of the *interactions*

## Extract Slopes  

#### Helper Functions

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[4] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[18] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[17]))

linear = c("Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw", "Ipl", "Pppl", "Mtl", "Ppl", "Mcl", "Tpw", "Isl", "Il", "Pel", "Hpw", "Mcw", "Cl", "Ppw", "Pipl")

index = c("SI", "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "MANUS2",  "PES", "MANUS",  "PRTI", "HPI", "MRI",  "PES2",  "MANUS3")

log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

#### Extract LM interactions

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
lms <- map(list_b_lm[2:35], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_lm[36:71], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms <- lms %>% bind_rows(lms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(lms2)
```


#### Extract GM Interactions  

```{r message = FALSE, warning=FALSE}
gms <- map(list_b_gm[2:35], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

gms2 <- map(list_b_gm[36:71], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

gms <- gms %>% bind_rows(gms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(gms2)
```


# Good LM plot 

```{r}
lms %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean)) +
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "log(Mass):phenotype interaction effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  artyfarty::theme_scientific() + 
  facet_wrap(~type, scales = 'free_y') +
  theme(strip.background = element_blank(),
        legend.position="none")

ggsave(here("Plots", "Bin_Interaction_Effects.pdf"))
```


## Good All Plot
```{r}
lms2 <- lms %>% mutate(mass = "lm")
gms2 <- gms %>% mutate(mass = "gm")

ms <- bind_rows(lms2, gms2)


ms %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean, shape = mass)) +
  stat_pointinterval(.width = c(.66, .89), 
                     position = position_dodge(width = .75)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "mass:phenotype interaction effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c(15, 16)) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~type, scales = 'free_y') +
  theme(strip.background = element_blank())#,
        #legend.position="none")

ggsave(here("Plots", "Bin_Interaction_All_Effects.pdf"), height = 8, width = 9)
ggsave(here("Plots", "Bin_Interaction_All_Effects.jpg"), height = 8, width = 9)

```


# Sigs Stuff
#### Log_mass Slope DF
```{r message = FALSE, warning=FALSE}
#list of slopes in order of means
nms <- lms %>% group_by(var) %>% summarise(mean = mean(val)) %>% arrange(mean) %>%  select(var)

m <- as.factor(nms$var)
m <- fct_rev(m)
m %>% saveRDS(here("Data", "Order_Names.Rds"))

# New df to demonstrate which vars don't overlap 0 at 89%
sigs_lm <- lms %>% group_by(var) %>% 
  median_qi(val , .width = c(0.89)) %>% 
  mutate(sigs = case_when(
    .lower > 0 & .upper > 0 ~ "sig",
    .lower < 0 & .upper < 0 ~ "sig",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
   mutate(dirs = case_when(
    .lower > 0 & .upper > 0 ~ "More Climbing = Larger Measurement",
    .lower < 0 & .upper < 0 ~ "More Climbing = Shorter Measurement",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
  select(var, sigs, dirs)
```

List the variables that have strong non-zero slopes
```{r}
sigs_lm %>% filter(sigs == "sig") %>% select(var) %>% as.list(var)
```

#### Geometric_mean Slope DF  

```{r message = FALSE, warning=FALSE}

# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
gms <- map(list_b_gm[2:23], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

gms2 <- map(list_b_gm[24:44], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

gms <- gms %>% bind_rows(gms2)
rm(gms2)


#list of slopes in order of means
nms_gm <- gms %>% group_by(var) %>% summarise(mean = mean(val)) %>% arrange(mean) %>%  select(var)

# New df to demonstrate which vars don't overlap 0 at 89%
sigs_gm <- gms %>% group_by(var) %>% 
  median_qi(val , .width = c(0.89)) %>% 
  mutate(sigs = case_when(
    .lower > 0 & .upper > 0 ~ "sig",
    .lower < 0 & .upper < 0 ~ "sig",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
 mutate(dirs = case_when(
    .lower > 0 & .upper > 0 ~ "More Climbing = Larger Measurement",
    .lower < 0 & .upper < 0 ~ "More Climbing = Shorter Measurement",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
  select(var, sigs, dirs)
```

## Plot Slopes

#### All LM Slopes
```{r warning = FALSE}

lms %>% right_join(sigs_lm, by = 'var') %>% 
  mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw()

#ggsave(here("Plots","Ord2_sigs.pdf"), height = 15)

#lms %>% right_join(sigs_lm, by = 'var') %>% 
#  filter(sigs == "sig") %>% 
#  mutate(var = fct_relevel(var, nms$var)) %>% 
#  ggplot(aes(x = val, y = var, color = sigs)) + 
#  stat_pointinterval(.width = c(.66, .89)) +
#  geom_vline(xintercept = 0.5, linetype = 3) + 
#  scale_fill_manual(values = pal) +
#  scale_color_manual(values = pal) +
#  theme_bw()

#ggsave(here("Plots","Ord2_sigs2.pdf"), height = 10)
```

#### All GM Slopes  

```{r warning = FALSE}

gms %>% right_join(sigs_gm, by = 'var') %>% 
  mutate(var = fct_relevel(var, nms_gm$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw()

```


Ok, so some large interactions!

# Test Cond Effects Plots 

```{r}

conditions <- data.frame(log_Mass = c(-1.5, 0, 1.5))

#effect = "MANUS2"
xaxis   <- "Rl"   
yaxis   <- "Probability"

conditional_effects(list_b_lm$Rl, 
                          prob = 0.99, 
                          conditions = conditions, 
                          effects= paste(xaxis))[[1]] %>% 
  #extract conditional effects data frame
  as_tibble() %>% 
    mutate(log_Mass = factor(log_Mass, 
                                    levels = c("-1.5", "0", "1.5"),
                                    labels = c("Low Mass", "Mean Mass", "High Mass"))) %>% 
  #rename the objects in the conditional effects df
  rename(Probability = estimate__) %>%
ggplot(aes(x = .data[[xaxis]], y = Probability)) +
  geom_ribbon(aes(ymin = lower__, 
                  ymax = upper__), 
              alpha=0.2) +
  geom_line(size=0.4) +
  facet_wrap(~ log_Mass, 
             ncol = 3) +
  #labs(subtitle = "log_Ppl_length") + 
  theme_bw() +
  ylim(0, 1) +
  theme( #panel.grid.major = element_blank(), 
         #panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         panel.border = element_rect(colour = "black", 
                                     fill = NA,
                                     size = rel(0.8)),
         axis.line = element_line(colour = "NA")
         )
```

