---
title: "R Notebook"
#output: html_notebook
---

Plotting the Binary Int Mass Model results

Focus on Effect size of the predictor

Packages and Data
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes, ggstar, tidytext, grid)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))

# Models

list_b_lm <- read_rds(here("Data","B_lm_mods_mis.Rds"))
list_b_gm <- read_rds(here("Data","B_gm_mods_mis.Rds"))
list_b_ratio <- read_rds(here("Data","B_ratio_mods_mis.Rds"))

accs <- read_rds(here("Data", "Accuracy_list.rds"))
```



some colors
```{r}
pal = c('#66a61e', '#7570b3',  '#e6ab02', '#62361B')

binpal = c('#66a61e','#5e1ea6')#5e1ea6

cols = c("#7570b3" ,  "#85D4E3" , "#0D7E9A",'#f5f5cb', '#c7e6d4', '#8cd2cd', '#55c3cf', '#3fa4b0', '#187389','#f48a1a', '#e6ab02', '#66a61e', '#85D4E3', '#0D7E9A', '#7570b3','#f6d03d', '#fe7b30', '#ef4a27', '#f384f8', '#625afc', '#0d57ff', '#47a7ff','#5771ff', '#6bae9e', '#31c1bb', '#7af1e1', '#d5e1af', '#f48130','#C60C30', '#00A1DE', '#62361B', '#009B3A', '#f9581c', '#522398', '#E27EA6', '#F9E300', '#565A5C')
pal2 <- LaCroixColoR::lacroix_palette("Orange", n = 30, type = "continuous")[c(1,5,10,12,13,14,15,16,17,18,25,28)]
```

# Forest Plots

Here i'm focusing on the slope of the phenotype

## Extract Slopes  

#### Helper Functions

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[2] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[17] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[17]))

linear = c("Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw", "Ipl", "Pppl", "Mtl", "Ppl", "Mcl", "Tpw", "Isl", "Il", "Pel", "Hpw", "Mcw", "Cl", "Ppw", "Pipl")

index = c("SI", "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "MANUS2",  "PES", "MANUS",  "PRTI", "HPI", "MRI",  "PES2",  "MANUS3")

log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

## Log-Mass Models

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
lms <- map(list_b_lm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_lm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms <- lms %>% bind_rows(lms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(lms2)
```

## Geometric Mean Models  

```{r message = FALSE, warning=FALSE}

# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
gms <- map(list_b_gm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

gms2 <- map(list_b_gm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

gms <- gms %>% bind_rows(gms2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA))

rm(gms2)
```

## Ratio Models
Includes functional indices and log-shape ratios

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[2] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[16] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[16]))

linear = c("Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw", "Ipl", "Pppl", "Mtl", "Ppl", "Mcl", "Tpw", "Isl", "Il", "Pel", "Hpw", "Mcw", "Cl", "Ppw", "Pipl")

index = c("SI", "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "MANUS2",  "PES", "MANUS",  "PRTI", "HPI", "MRI",  "PES2",  "MANUS3")

log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
rs <- map(list_b_ratio[2:22], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

rs2 <- map(list_b_ratio[23:44], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

rs <- rs %>% bind_rows(rs2) %>% 
  mutate(type = case_when(
    var %in% linear ~ "Linear Measurement",
    var %in% index ~ "Functional Index",
    var %in% log_shape ~ "Log-Shape Ratio",
    TRUE ~ NA)) 
rm(rs2)
```

## Plot Color

### Plot All
Plotting the metric effect sizes for all metrics, broken up by "type"
```{r}

ms <- bind_rows(lms %>% mutate(mass = "lm"), gms %>% mutate(mass = "gm"), rs %>% mutate(mass = "none"))


ms %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean, shape = mass)) +
  stat_pointinterval(.width = c(.66, .89), 
                     position = position_dodge(width = .75)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  #scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~type, scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))#,
        #legend.position="none")

ggsave(here("Plots", "B_Effects_All.pdf"), height = 8, width = 9)
ggsave(here("Plots", "Bin_Effects_All.jpg"), height = 8, width = 9)
```

### Plot Accurate Predicitons

Plotting accurate predictions
Baed on the `Binary_Prediction_Accuracy` script, these all have an accuracy over 70%. It's worth noting that all of the log-shape-ratios have not-great accuracy except lsPpl.
```{r}
accurate = c("PES2", "HPI", "PES", "MANUS", "Ppl", "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul", "Mtl",  "lsPpl", "lsCl", "lsUol", "lsIsl", "lsMtl", "lsTpw" )
```

```{r}
ms %>% filter(var %in% accurate) %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean, shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  #scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~factor(type, levels=c('Log-Shape Ratio','Functional Index','Linear Measurement')), scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))


ggsave(here("Plots", "B_Effects_Some.pdf"), ppp, height = 3, width = 9)


```

ppp
grid.force()
grid.ls()

grid.remove('key-5-1-bg.6-2-6-2')
grid.remove('key-5-1-1.6-2-6-2')
grid.remove('label-5-3.6-4-6-4')

## Plot Color

### Plot All
Plotting the metric effect sizes for all metrics, broken up by "type"
```{r}

ms <- bind_rows(lms %>% mutate(mass = "lm"), gms %>% mutate(mass = "gm"), rs %>% mutate(mass = "none"))


ms %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 0.8) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~type, scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))#,
        #legend.position="none")

ggsave(here("Plots", "B_Effects_All_BW.pdf"), height = 8, width = 9)
ggsave(here("Plots", "Bin_Effects_All_BW.jpg"), height = 8, width = 9)
```

### Plot Accurate Predicitons

Plotting accurate predictions
Baed on the `Binary_Prediction_Accuracy` script, these all have an accuracy over 70%. It's worth noting that all of the log-shape-ratios have not-great accuracy except lsPpl.
```{r}
accurate = c("PES2", "HPI", "PES", "MANUS", "Ppl", "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul", "Mtl",  "lsPpl", "lsCl", "lsUol", "lsIsl", "lsMtl", "lsTpw" )
```

```{r}
ms %>% filter(var %in% accurate) %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type),  shape = mass)) +
  stat_pointinterval(.width = 0.8, 
                     position = position_dodge(width = .75),
                     linewidth = 1.7) +
  geom_vline(xintercept = 0, linetype = 3) + 
  #scale_fill_manual(values = pal) +
  scale_y_reordered("") +
  labs(x = "Phenotypic predictor effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  #scale_color_gradientn(colours = rev(pal2)) +
  scale_shape_manual(values=c("none" = 16, "lm" = 1, "gm" = 15),
                     breaks = c("lm", "gm"),
                     name = "Body Size\nMetric",
                     labels=c("log(Mass)", "Geometric\nMean")) +
  artyfarty::theme_scientific() + 
  guides(color = "none") +
  facet_wrap(~factor(type, levels=c('Log-Shape Ratio','Functional Index','Linear Measurement')), scales = 'free') +
  theme(strip.background = element_blank()) +
  guides(shape = guide_legend(override.aes = list(size=8)))


ggsave(here("Plots", "B_Effects_Some_BW.pdf"), ppp, height = 3, width = 9)


```

ppp
grid.force()
grid.ls()



#### Log_mass Mass Slope DF
```{r message = FALSE, warning=FALSE}
#list of slopes in order of means
nms <- lms %>% group_by(var) %>% summarise(mean = mean(val)) %>% arrange(mean) %>%  select(var)

m <- as.factor(nms$var)
m <- fct_rev(m)
m %>% saveRDS(here("Data", "Order_Names.Rds"))

# New df to demonstrate which vars don't overlap 0 at 89%
sigs_lm <- lms %>% group_by(var) %>% median_qi(val, .width = c(0.89)) %>% 
  mutate(sigs = case_when(
    .lower > 0 & .upper > 0 ~ "sig",
    .lower < 0 & .upper < 0 ~ "sig",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
   mutate(dirs = case_when(
    .lower > 0 & .upper > 0 ~ "More Climbing = Larger Measurement",
    .lower < 0 & .upper < 0 ~ "More Climbing = Shorter Measurement",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
  select(var, sigs, dirs)
```

List the variables that have strong non-zero slopes
```{r}
sigs_lm %>% filter(sigs == "sig") %>% select(var) %>% as.list(var)
```


#list of slopes in order of means
nms_gm <- gms %>% group_by(var) %>% summarise(mean = mean(val)) %>% arrange(mean) %>%  select(var)

#New df to demonstrate which vars don't overlap 0 at 89%
sigs_gm <- gms %>% group_by(var) %>% median_qi(val, .width = c(0.89)) %>% 
  mutate(sigs = case_when(
    .lower > 0 & .upper > 0 ~ "sig",
    .lower < 0 & .upper < 0 ~ "sig",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
 mutate(dirs = case_when(
    .lower > 0 & .upper > 0 ~ "More Climbing = Larger Measurement",
    .lower < 0 & .upper < 0 ~ "More Climbing = Shorter Measurement",
    #max(var) < 0.5 ~ "sig",
    TRUE ~ "nosig")) %>% 
  select(var, sigs, dirs)
```

## Plot Slopes

#### All LM Slopes
```{r warning = FALSE}

lms %>% right_join(sigs_lm, by = 'var') %>% 
  mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw()

#ggsave(here("Plots","Ord2_sigs.pdf"), height = 15)

lms %>% right_join(sigs_lm, by = 'var') %>% 
  filter(sigs == "sig") %>% 
  mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw()

#ggsave(here("Plots","Ord2_sigs2.pdf"), height = 10)
```

#### All GM Slopes  

```{r warning = FALSE}

gms %>% right_join(sigs_gm, by = 'var') %>% 
  mutate(var = fct_relevel(var, nms_gm$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0.5, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw()

gms %>% right_join(sigs_gm, by = 'var') %>% 
  mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw() + 
  facet_wrap(~type, scales = 'free')
#ggsave(here("Plots","Ord2_sigs.pdf"), height = 15)

gms %>% right_join(sigs_gm, by = 'var') %>% 
  filter(sigs == "sig") %>% 
  mutate(var = fct_relevel(var, nms_gm$var)) %>% 
  ggplot(aes(x = val, y = var, color = sigs)) + 
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0.5, linetype = 3) + 
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  theme_bw()

#ggsave(here("Plots","Ord2_sigs2.pdf"), height = 10)
```

## Combined Forest Plot

Wrangle sigs from both DFs and rename
```{r}
lmsig <- lms %>% 
  #right_join(sigs_lm, by = 'var') %>% 
  #filter(sigs == "sig") %>% 
 #mutate(dirs = case_when(
 #  val > 0.5  ~ "Decreasing",
 #  val < 0.5  ~ "Increasing")) %>% 
  mutate(correction = "log(Mass)")

sigplotdf <- gms %>% 
  #right_join(sigs_gm, by = 'var') %>% 
  #filter(sigs == "sig") %>% 
 #mutate(dirs = case_when(
 #  val > 0.5  ~ "Decreasing",
 #  val < 0.5  ~ "Increasing")) %>% 
  mutate(correction = "Geometric Mean") %>% 
  bind_rows(lmsig)

rm(lmsig)


sigplotdf <- sigplotdf %>% 
  mutate(var = case_when(var == "Sl"  ~ "Scapula Length",
                         var == "SI"  ~ "Scapula Proportion Index",
                         var == "Tl"  ~ "Tibia Length",
                         var == "Tmw"  ~ "Tibia Mid-Shaft Width",
                         var == "Tpw"  ~ "Tibia Proximal End Width",
                         var == "Hl"  ~ "Humerus Length",
                         var == "Il"  ~ "Illium Length",
                         var == "Isl" ~ "Ischium Length",
                         var == "Pel" ~ "Pelvic Length",
                         var == "Hdw"  ~ "Humerus Distal End Width",
                         var == "Hpw"  ~ "Humerus Proximal End Width",
                         var == "Hsw"  ~ "Humerus Mid-Shaft Width",
                         var == "Cl"  ~ "Calcaneus Length",
                         var == "Uol"  ~ "Olecranon Length",
                         var == "Rl" ~ "Radius Length",
                         var == "Fl"  ~ "Femur Length",
                         var == "Ppl" ~ "Proximal Phalanx Length",
                         var == "Ipl" ~ "Intermediate Phalanx Length",
                         var == "Mtl"  ~ "Metatarsal Length",
                         var == "Mcl"  ~ "Metacarpal Length",
                         var == "Mcw"  ~ "Metacarpal Width",
                         var == "Pppl" ~ "Proximal Phalanx Length Pes",
                         var == "Ppw" ~ "Proximal Phalanx Width",
                         var == "HRI" ~ "Humeral Robustness Index",
                         var == "HPI" ~ "Humeral Proximal Index",
                         var == "HEB" ~ "Humeral Epicondyle Index",
                         var == "HHRI" ~ "Humeral Head Index",
                         var == "OLI"  ~ "Olecranon Process Index",
                         var == "PRTI"  ~ "Palm Robustness Index",
                         var == "MANUS" ~ "Manus Proportion Index Proximal",
                         var == "MANUS2"  ~ "Manus Proportion Index Intermediate",
                         var == "IRI" ~ "Illium Robustness Index",
                         var == "FRI" ~ "Femoral Robustness Index",
                         var == "FEB" ~ "Femoral Epicondyle Index",
                         var == "CI" ~ "Crural Index",
                         var == "BI" ~ "Brachial Index",
                         var == "TRI"  ~ "Tibial Robustness Index",
                         var == "PR"  ~ "Pelvic Index",
                         var == "PES" ~ "Pes Proportion Index Proximal",
                         var == "PES2"  ~ "Pes Proportion Index Intermediate",
                         var == "Ul" ~ "Ulna Length",
                         var == "Cal" ~ "Calcaneal Body Length",
                         var == "Anl" ~ "Astragular Neck Length",
                         var == "Ppl" ~ "Proximal Phalanx Length Pes",
                         var == "Fbmw" ~ "Fibula Midshaft Diameter",
                         var == "Fdw" ~ "Femoral Distal End Width",
                         var == "HHW" ~ "Humeral Head Index",
                         var == "IM" ~ "Intermembral Index",
                         var == "MRI" ~ "Metacarpal Robustness Index",
                         var == "Hhl" ~ "Humeral Head Length",
                         var == "Fbl" ~ "Fibula Length",
                         var == "Fsw"  ~ "Femur Mid-Shaft Width",
                         var == "MANUS3" ~ "Manus Proportion Index",
                         TRUE ~ NA)) 

#levs <- c("Humeral Head Index", "Intermediate Phalanx Width Pes", "Metatarsal Width", "Metacarpal Robustness Index", "Tibial Robustness Index", "Humeral Head Index", "Intermediate Phalanx Width", "Distal Phalanx Length", "Distal Phalanx Length", "Humeral Robustness Index", "Palm Robustness Index", "Metatarsal Length", "Humeral Epicondyle Index", "Olecranon Length", "Crural Index", "Femoral Robustness Index", "Femoral Epicondyle Index", "Olecranon Process Index", "Proximal Humeral Index", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, "Fibula Length", NA, "Intermembral Index", "Calcaneal Body Length", "Fibula Midshaft Diameter", "Femoral Head Diameter", "Ulna Length", "Humeral Head Length", "Femur Length", "Manus Proportion Index Intermediate", "Intermediate Phalanx Length Pes", "Pelvic Index", "Astragular Neck Length", "Illium Robustness Index", "Radius Length", "Humerus Length", "Intermediate Phalanx Length", "Manus Proportion Index Proximal", "Pes Proportion Index Intermediate", "Pes Proportion Index Proximal", "Proximal Phalanx Length")
```




#### Big Forest Plot  
```{r}

sigplotdf %>% 
  #mutate(var = fct_relevel(var, levs)) %>%
  ggplot(aes(x = val, y = var, color = correction)) + 
  stat_pointinterval(.width = c(.66, .89), position = position_dodge(width = .5)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = binpal) +
  scale_color_manual(values = binpal) +
  theme_bw(base_size = 14) +
  labs(title = "Binary Modeling: Mass Effect Sizes",
       #subtitle = "The further the estimates are from 0.5, the stronger the effect of the measurement on climbing.\nMeasurements on the left side decrease with decreased climbing (e.g. shorter olecranon)\nand values on the right increase with increased climbing ( e.g. longer phalanges)",
       x = "log-odds",
       y = "") +
  #facet_wrap(~fct_relevel(dirs,'More Climbing = Shorter Measurement','More Climbing = Larger Measurement'), scales = "free")
  facet_wrap(~type, scales = "free")

ggsave(here("Plots", "Binary_Int_Mass_Effects.pdf"), height = 9, width = 14)
#ggsave(here("Plots","Binary_Modeling_Effects.png"), height = 9, width = 14)
```

