---
title: "Predicting Binary Interaction Climbing"
output: html_notebook
---


# Predicting climbing from fossil data:

Take model lists, then use them one by one to predict climbing in the fossil taxa.
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, brms, cmdstanr, here, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
nms <- read_rds(here("Data", "Order_Names.Rds"))

source(here("Code","Name_Change.R"))


```


### Load Data  

```{r}
dat <- read_csv(here("Data", "Extant_Master.csv"))

fdat <- read_csv(here("Data", "Fossil_Master.csv")) %>% 
  mutate(Family = case_when(is.na(Family) ~ "Mesozoicdae",
                            TRUE ~ Family)) %>% 
  mutate(Order = case_when(is.na(Order) ~ "Mesozoicata",
                            TRUE ~ Order))

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

#variables to do fossil predictions with
pred_vars <- fdat_cln[c(9:84)]

#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements. 

```{r}
list_b_lm <- read_rds(here("Data","B_lm_Ord_Fam_int_mods_mis.Rds"))
#purrr keep_at is great!
list_b2 <- list_b_lm %>% keep_at(pred_vars)

names(list_b2)

rm(list_b_lm)
```
Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model

# Predictions  

## Fossil Functions
```{r}
colz <- c("Genus_species", "log_Mass", names(list_b2), "Specimen_Num")

fd <- fdat %>% select(colz)

nnn <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    # This is different
                    re_formula = ~ (1|Order) + (1|Family)) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
    mutate(var = {{nm}})
}

```

# Extant Functions

```{r}
extant_climb <- c("Caluromys_derbianus", "Tamiasciurus_douglasii","Tupaia_glis", "Cynocephalus_volans", "Glaucomys_sabrinus")

extant_ground <- c("Solenodon_paradoxus", "Atelerix_albiventris",     "Sorex_trowbridgii", "Thomomys_bottae", "Monodelphis_domestica")


old <- c("Eomaia_scansoria", "Sinodelphys_szalayi", "Juramaia_sinensis", "Cokotherium_jiufotangensis", "Ambolestes_zhoui")

multi <- c("Rugosodon_eurasiaticus", "Jeholbaatar_kielanae", "Filikomys_primaevus", "Ptilodus_kummae", "Kryptobaatar_dashzevegi")

primate <- c("Plesiadapis_cookei", "Torrejonia_wilsoni", "Ignacius_clarkforkensis", "Dryomomys_szalayi")

model_dat <- dat %>% filter(Genus_species %in% c(extant_climb, extant_ground))

nnn2 <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
    mutate(var = {{nm}})
  
}

nnn3 <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = ~ (1|Order) + (1|Family)) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
    mutate(var = {{nm}})
}



```

### Plot helpers
**Different List with Taxonomic Models**
```{r}

#var_acc = c('PES2', 'MANUS', 'PES', 'Ppl', 'MANUS2', 'HPI', 'Hl', 'Ipl', 'Rl', 'Ul', 'OLI', "Fl")

var_acc = c("PES2", "MANUS", "PES", "HPI", "Ppl", "Ipl", "MANUS2", "Hl", "Fsw", "Sl", "Tpw", "Hsw", "OLI", "Pel", "Fdw", "Mtl", "Hpw", "Uol")

```


```{r}
nm <- names(list_b2)

pred_df <- map2(list_b2, nm, ~nnn(.x, .y)) %>% bind_rows() %>% 
  write_csv(here("Data", "Fossil_Tax_Int_Predictions.csv")) %>% 
  mutate(method = "Fossil",
         substrate = NA)


pred_df_ext_full <- map2(list_b2, nm, ~nnn2(.x, .y)) %>% 
  bind_rows() %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))

pred_df_ext_fos <- map2(list_b2, nm, ~nnn3(.x, .y)) %>% 
  bind_rows() %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


pred_all <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_df) %>% filter(var %in% var_acc) %>% 
  mutate(draw = rep(1:4000, times = nrow(.)/4000)) %>% 
  #THIS IS AVERAGING PER SPECIES
  group_by(substrate, method, var, Genus_species, draw) %>% 
  summarize(Prob_of_Climbing = mean(Prob_of_Climbing, na.rm = TRUE)) %>% ungroup() %>% 
  write_csv(here("Data", "All_Tax_Int_Predictions.csv"))
```
## Add means to the plots?
Isn't really a good idea because there is uneven sampling across measurements
```{r}
#meandf <- pred_all %>% group_by(substrate, method, Genus_species, draw) %>% 
#  summarize(Prob_of_Climbing = mean(Prob_of_Climbing, na.rm = TRUE)) %>% 
#  ungroup() %>% 
#  mutate(var = "Mean")
#
#pred_all <- bind_rows(pred_all, meandf)
```




# Whole Shebang  


### function
```{r}
# shading
shades <- data.frame(xmin=seq(1.5,13-1.5, 2),
                     xmax=seq(2.5,13+.5, 2),
                     ymin=0, ymax=Inf)

hplot <- function(groups, method){
  pred_all %>% filter(Genus_species %in% {{groups}},
                         method == {{method}}) %>% 
    mutate(var =  as.factor(var)) %>% 
  ggplot(aes(y = Prob_of_Climbing, 
             x = fct_relevel(var,var_acc), 
             #y = var,
             color = Genus_species)) +
  geom_hline(yintercept = 0.5, linetype = 2, linewidth = 0.5) +
  stat_pointinterval(.width = c(0.5, 0.68268), 
                     #linewidth = c(0.75, 0.5), 
                     position = position_dodge(width = -.6)) + ylim(0,1) +
    labs(x = "", y = "Probability of Climbing") +
  scale_color_manual(values = pal) + theme_pander(gM = F) + 
    geom_rect(inherit.aes = F, 
              data = shades, 
              mapping = aes(xmin=xmin, 
                            xmax=xmax, 
                            ymin = ymin, 
                            ymax = ymax), 
              alpha = 0.125) +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.border = element_rect(colour = "grey40", fill=NA, size=0.7))
}

```

###  big df



### Big Plot
```{r}
pl5 <- hplot(old, "Fossil") + 
  ggtitle("Mesozoic Mammal Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank(),
        panel.grid.major.y = element_blank())

pl6 <- hplot(multi, "Fossil") + 
  ggtitle("Multituberculate Predicitons") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl7 <- hplot(primate, "Fossil") + 
  ggtitle("Primate Predicitons") + 
  theme(#axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())


t3 <- pl5 / pl6 /pl7

t3

ggsave(here("Plots", "Predict_Tax_Int_Fossil.pdf"), height = 8, width = 12)

```


```{r}
pl1 <- hplot(extant_climb, "Full") + 
  ggtitle("Extant Climb Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl2 <- hplot(extant_climb, "Fossil") + 
  ggtitle("Extant Climb Fossil") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl3 <- hplot(extant_ground, "Full") + 
  ggtitle("Extant Ground Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl4 <- hplot(extant_ground, "Fossil") + 
  ggtitle("Extant Ground Fossil") + 
  theme(#axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),)


t1 <- pl1 / pl2 + plot_layout(guides = "collect")

t2 <- pl3 / pl4 + plot_layout(guides = "collect")

wrap_plots(t1, t2, ncol = 1)

ggsave(here("Plots", "Predict_Tax_Int_Extant.pdf"), height = 10, width = 12)

```

```{r}
pl2 / pl4 + plot_layout(guides = "collect")

ggsave(here("Plots", "Predict_Tax_Int_Extant2.pdf"), height = 6, width = 13)
```



```{r}
wrap_plots(t1, t2, t3, ncol = 1, heights = c(2/7, 2/7, 3/7))

ggsave(here("Plots", "Predict_Tax_Int_All.pdf"), height = 16, width = 10)
```


