---
title: "Data_Processing"
---

# Data Processing

This script pulls the `Master_Data` from the google drive folder, wrangles it to get everything in order, then saves the data s a csv.

This script INCLUDES the fossil data, and scales all the data, extant and extinct, together. This way the two spreadsheets can be easily used when needed. 

Also the `var_complete` and `var_missing` lists are created at the bottom

## Packages
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, here, glue)

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_acc = c( "Ppl",  "Hl",  "Pipl", "Rl", "Ipl", "Uol", "Fl", "Ul", "HPI", "PES", "PES2", "MANUS", "MANUS2", "OLI", "combined")
```

## Load Extant data  

```{r message = FALSE, warning=FALSE}
dat <- read_csv(here('Data', 'Raw_Extant_Data.csv'), na = c("NA", "?", "")) %>% 
  select(!NOTES) %>% 
# Recode Ordinal Rankings
  mutate(Loc_Ord = case_when(Loc_mode_Ordinal == "G"  ~ "G",
                             Loc_mode_Ordinal == "A"  ~ "A",
                             Loc_mode_Ordinal == "Sc" ~ "Sc",
                             Loc_mode_Ordinal == "T"  ~ "T",
                             Loc_mode_Ordinal == "Is" ~ "Is",
                             Loc_mode_Ordinal == "Sf" ~ "Sf",
                             Loc_mode_Ordinal == "Ss" ~ "Ss",
                             TRUE ~ NA),
         Loc_Ord = as.ordered(Loc_Ord),
         Loc_Ord = fct_relevel(Loc_Ord, c("G","A","Sc","T","Is","Sf","Ss")),
         # Combining the Intersurface and Semifossorial
         Loc_Ord2 = case_when(Loc_mode_Ordinal == "G" ~ "A",
                              Loc_mode_Ordinal == "A" ~ "A",
                              Loc_mode_Ordinal == "Sc" ~ "Sc",
                              Loc_mode_Ordinal == "T" ~ "T",
                              Loc_mode_Ordinal == "Is" ~ "B",
                              Loc_mode_Ordinal == "Sf" ~ "B",
                              Loc_mode_Ordinal == "Ss" ~ "B",
                             TRUE ~ NA),
         Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")),
         Loc_bin = case_when(Loc_mode_Binary == "Ground" ~ 0,
                             Loc_mode_Binary == "Tree" ~ 1,
                             TRUE ~ NA
                             ),
        # Loc_bin = as.factor(Loc_bin),
         Loc_mode_Categorical = as.factor(Loc_mode_Categorical),
         log_Mass = log(Mass_grams)) %>% 
    relocate(Loc_bin, .after = Loc_mode_Binary) %>% 
  relocate(Loc_Ord, .after = Loc_mode_Ordinal) %>% 
  relocate(Loc_Ord2, .after = Loc_Ord) %>%
  relocate(log_Mass, .before = Skl) %>% 
#################
#Calculate Indices!
#################
  mutate(
         HPI = Hpw / Hl,           # Humeral Proximal Index
         OLI = Uol / Ul,           # Olecranon Process Length Index
         MANUS = Ppl / Mcl,        # MANUS index
         MANUS2 = (Ppl+Ipl)/Mcl,   # MANUS index with intermed. phalanx
         PES = Pppl / Mtl,         # PES INdex
         PES2 = (Pppl+Pipl)/Mtl,    # PES with intermediate Phalanx
         ) %>% 
    # geometric mean
  drop_na(Tmw, Fdw, Tl, Fl, Fsw , Sl, Hdw, Hl, Hsw, Rl, Ul, Uol) %>%
  mutate_at(vars(Skl:Pdpw), log) %>% 
  mutate(Fos = FALSE) %>% 
  select(!c("Loc_mode_Binary", "Loc_mode_Ordinal", "Loc_mode_source")) |> 
  select(1:8,11:14,17,19:21,26:28,32,35:36,38:39,56,58,66,70:76) |> 
  rename(Specimen_Number = "Specimen_Num")

spp_obs <- dat$Taxon_Upham_style %>% unique()

columns <- colnames(dat)

```

## Load Fossil Data  

```{r}
fdat <- read_csv(here('Data', 'Estimated_Fossil_Data_20250320.csv'), na = c("NA", "?", "", "NULL", "–")) %>% 
  # Selecting only the lines with data
  # THIS NEEDS TO BE UPDATED AS MORE DATA COME IN!!
  slice (1:48) %>% 
  select(!NOTES) %>% 
  #############
  #LOCOMOTION COLUMNS
  ##################
  mutate(Loc_Ord = NA,
         Loc_Ord2 = NA,
         Loc_bin = NA,
         log_Mass = log(Mass_grams)) %>%
  relocate(Loc_bin, .after = Genus_species) %>%
  relocate(Loc_Ord, .after = Loc_bin) %>% 
  relocate(Loc_Ord2, .after = Loc_Ord) %>%
  relocate(log_Mass, .after = Mass_grams) %>% 
#################
#Calculate Indices!
#################
  mutate(
         HPI = Hpw / Hl,           # Humeral Proximal Index
         OLI = Uol / Ul,           # Olecranon Process Length Index
         MANUS = Ppl / Mcl,        # MANUS index
         MANUS2 = (Ppl+Ipl)/Mcl,   # MANUS index with intermed. phalanx
         PES = Pppl / Mtl,         # PES INdex
         PES2 = (Pppl+Pipl)/Mtl,    # PES with intermediate Phalanx
         ) %>% 
  relocate(64:71) |> 
  mutate_at(vars(Skl:Pdpw), log) %>% 
  mutate(Fos = TRUE) |> select(all_of(columns)) 
```


### Combine, scale, and split

```{r}
dat2 <- bind_rows(dat, fdat) %>% 
  mutate_at(vars(log_Mass:PES2), scale2)

dat2 %>% filter(Fos == FALSE) %>% select(!Fos) %>% write_csv(here("Data", "Extant_Master_20250320.csv"))

dat2 %>% filter(Fos == TRUE) %>% select(!Fos) %>% write_csv(here("Data", "Fossil_Master_20250320.csv")) 
```

# Var Compete and Missing
Measurements with missing values or complete. 
Splitting up by measurement type as well.

```{r}
var_complete <- c("log_Mass", "Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw",  "HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw") %>% write_rds(here("Data", "var_complete.Rds"))

var_missing <- c("MANUS2", "MANUS3", "Ipl", "PES", "Pppl", "Mtl", "MANUS", "Ppl", "Mcl", "PRTI", "Tpw", "Isl", "Il", "Pel", "Hpw", "HPI", "Mcw", "MRI", "Ppw", "PES2", "Cl", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "Pipl", "lsPipl") %>% write_rds(here("Data", "var_missing.Rds"))

var_complete_linear <- c("log_Mass", "Sl", "Hl", "Hsw", "Hdw", "Uol", "Ul", "Rl", "Fl", "Fsw", "Fdw", "Tl", "Tmw") %>% write_rds(here("Data", "var_complete_linear.Rds"))

var_missing_linear <- c( "Ipl",  "Pppl", "Mtl",  "Ppl", "Mcl",  "Tpw", "Isl", "Il", "Pel", "Hpw",  "Mcw",  "Ppw",  "Cl", "Pipl") %>% write_rds(here("Data", "var_missing_linear.Rds"))

var_complete_ratio <- c("HRI", "HEB", "OLI", "BI", "IM", "FRI", "FEB", "CI", "TRI", "lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw") #%>% write_rds(here("Data", "var_complete_ratio.Rds"))

var_missing_ratio <- c("MANUS2", "MANUS3",  "PES",  "MANUS", "PRTI",  "HPI",  "MRI", "PES2", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl") #%>% write_rds(here("Data", "var_missing_ratio.Rds"))


tt <- c(var_missing_ratio, var_complete_ratio) %>% write_rds(here("Data", "tt.Rds"))

rm(var_complete_ratio, var_missing_ratio)

rm(tt)
read_rds(here("Data", "tt.Rds"))
```

