---
title: "Mass Prediction"
output: html_notebook
---

Need to predict the mass for a bunch of the new fossils. 


```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

source(here("Code","Name_Change.R"))

dat <- read_csv(here("Data", "Raw_Extant_Data.csv")) |> 
   mutate_at(vars(Mass_grams), log) |> 
  mutate(fossil = "N")

fdat <- read_csv(here("Data", "Fossil_Measurements_20250319.csv")) |>  mutate_at(vars(Mass_grams), log) |> 
  mutate(fossil = "Y")

comb_dat <- dat |> bind_rows(fdat) |> 
  mutate_at(vars(Skl:Pdpw), scale2)

# This is the mean and sd of the log transformed mass in grams. Can be used to reconstruct the actual mass of fossil predicitons. 
mass_vars <- comb_dat |> 
  summarise(mean = mean(Mass_grams, na.rm = T),
            sd = sd(Mass_grams, na.rm = T))

comb_dat <- comb_dat |> mutate(Mass = scale2(Mass_grams))

fdat <- comb_dat |> filter(fossil == "Y")

dat <- comb_dat |> filter(fossil == "N")

var_complete_linear <-  read_rds(here("Data", "var_complete_linear.Rds"))


```

Extant Model
Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Tl + Tmw
```{r}
p1 = c(prior(normal(0, 3), class = Intercept),
       prior(normal(0, 1), class = b),
       prior(normal(0, 1), class = sigma))

mod <- brm(Mass ~   Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Tl + Fdw + Tmw ,
          family = gaussian(),
          data = dat, refresh = 0, 
          cores = 4,
          prior = p1)

```





## Updates

Feredocodon_chowi_IMMNH-PV01035: 
Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Tl
```{r}
mod1 <- update(mod, formula. = ~ Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Tl)
d1 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "IMMNH-PV01035"), 
                    #allow_new_levels = TRUE, 
                    #re_formula =  Mass_grams ~ Sl + Hl + Hsw + Hdw + Uol + Rl + Fl + Fsw + Tl + Tmw
                    ) %>% 
    as.data.frame() %>% 
    summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "IMMNH-PV01035")
```


Feredocodon_chowi_IMMNH-PV01925: 
Sl + Hl + Ul + Rl + Fl + Tl
```{r}
mod1 <- update(mod, formula. = ~ Sl + Hl + Ul + Rl + Fl + Tl)
d2 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "IMMNH-PV01925"), 
                    #allow_new_levels = TRUE, 
                    #re_formula =  Mass_grams ~ Sl + Hl + Hsw + Hdw + Uol + Rl + Fl + Fsw + Tl + Tmw
                    ) %>% 
    as.data.frame() %>% 
    summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "IMMNH-PV01925")
```

Arboroharamiya_allinhopsoni_HG-M017: 
Sl + Hl + Hsw + Hdw + Uol + Rl + Fl + Fsw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~Sl + Hl + Hsw + Hdw + Uol + Rl + Fl + Fsw + Tl + Tmw)
d3 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "HG-M017"), 
                    #allow_new_levels = TRUE, 
                    #re_formula =  Mass_grams ~ Sl + Hl + Hsw + Hdw + Uol + Rl + Fl + Fsw + Tl + Tmw
                    ) %>% 
    as.data.frame() %>% 
    summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "HG-M017")
```

Maiopatagium_fulculiferum_BMNH 2940: 
Sl + Hl + Uol + Ul + Rl + Fl + Fsw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~ Sl + Hl + Uol + Ul + Rl + Fl + Fsw + Tl + Tmw)
d4 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "BMNH 2940")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "BMNH 2940")
```
Xianshou_songae_BMNHC-PM003253:
Hl + Hsw + Uol + Ul + Rl + Fl + Fsw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Uol + Ul + Rl + Fl + Fsw + Tl + Tmw)
d5 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "BMNHC-PM003253")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "BMNHC-PM003253")
```

Akidolestes_cifellii_NIGAPS139381: Hl + Ul + Rl
```{r}
mod1 <- update(mod, formula. = ~ Hl + Ul + Rl)
d6 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "NIGAPS139381")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "NIGAPS139381")
```

Borealestes_cullinensis_NMS G.2020.4.1.1: Hl + Ul
```{r}
mod1 <- update(mod, formula. = ~ Hl + Ul)
d7 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "NMS G.2020.4.1.1")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "NMS G.2020.4.1.1")
```

Agilocodon_scansorius_BMNH 1138: 
Hl + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw)
d8 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "BMNH 1138")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "BMNH 1138")
```

Liaoconodon_hui_IVPP V16051: 
Hl + Hsw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw)
d9 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "IVPP V16051")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "IVPP V16051")
```

Arboroharamiya_allinhopsoni_HG-M018: Hl + Hsw + Hdw + Ul + Rl + Fl + Fsw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Hdw + Ul + Rl + Fl + Fsw + Tl + Tmw)
d10 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "HG-M018")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "HG-M018")
```

Gobiconodon_ostromi_MCZ 19860: Hl + Hsw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw)
d11 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "MCZ 19860")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "MCZ 19860")
```

Repenomamus_robustus_V13605: Hl + Hsw + Ul + Rl + Fl + Fsw + Tl
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Ul + Rl + Fl + Fsw + Tl)
d12 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "V13605")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "V13605")
```

Repenomamus_robustus_V12728: Hl + Hsw + Ul + Rl + Fl + Fsw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Ul + Rl + Fl + Fsw)
d13 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "V12728")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "V12728")
```

Repenomamus_giganticus_V14155: Hl + Hsw + Ul + Rl + Fl + Fsw + Tl
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Ul + Rl + Fl + Fsw + Tl)
d14 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "V14155")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "V14155")
```

Arboroharamiya_jenkinsi_STM33-9: Ul + Rl + Fl + Fsw + Fdw + Tl
```{r}
mod1 <- update(mod, formula. = ~ Ul + Rl + Fl + Fsw + Fdw + Tl)
d15 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "STM33-9")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "STM33-9")
```

Borealestes_serendipitus_NMS G.1992.47.121.1: Rl + Fl
```{r}
mod1 <- update(mod, formula. = ~ Rl + Fl)
d16 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "NMS G.1992.47.121.1")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "NMS G.1992.47.121.1")
```

Litovoi_tholocephalos_LPB FGGUB M.1700: Fl + Fsw
```{r}
mod1 <- update(mod, formula. = ~ Fl + Fsw)
d17 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "LPB FGGUB M.1700")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "LPB FGGUB M.1700")
```

Repenomamus_robustus_V12549: Ul + Rl + Fl + Fsw + Tl
```{r}
mod1 <- update(mod, formula. = ~ Ul + Rl + Fl + Fsw + Tl)
d18 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "V12549")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "V12549")
```

Yubaatar_zhongyuanensis_41HIII0111: Tl
```{r}
mod1 <- update(mod, formula. = ~ Tl)
d19 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num == "41HIII0111")) |>  
    as.data.frame() %>% 
  #group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred), Specimen_Num = "41HIII0111")
```

Jeholodens_jenkinsi_GMV 2139A: 
Maotherium_sinensis_NGMC-97-4-15:
Zhangeotherium_quiquecuspidens_STM38-4:
Hl + Rl + Fl + Tl
```{r}
mod1 <- update(mod, formula. = ~ Hl + Rl + Fl + Tl)
d20 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num %in% c("GMV 2139A", "NGMC-97-4-15", "STM38-4"))) |>  
    as.data.frame() %>% 
  group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred))
```

Vilevolodon_diplomyos_BMNH 2942:
Shenshou_lui_LDNHMF2001:
Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw)
d21 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num %in% c("BMNH 2942", "LDNHMF2001"))) |>  
    as.data.frame() %>% 
  group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred))
```

Yanoconodon_allini_NJU-P06001A: 
Priacodon_fruitaensis_LACM 120451:
Volaticotherium_antiquus_IVPP V14740:
Hl + Hsw
```{r}
mod1 <- update(mod, formula. = ~ Hl + Hsw )
d22 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num %in% c("NJU-P06001A", "LACM 120451", "IVPP V14740"))) |>  
    as.data.frame() %>% 
  group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred))
```

Spinolestes_xenarthrosus_MCCMLH30000: 
Henkelotherium_guimarotae_Gui Mam 138/76:
Hl
```{r}
mod1 <- update(mod, formula. = ~ Hl )
d23 <- mod1 %>% 
    add_epred_draws(newdata = fdat |> filter(Specimen_Num %in% c("MCCMLH30000", "Gui Mam 138/76"))) |>  
    as.data.frame() %>% 
  group_by(Specimen_Num) |> 
  summarise(mean = mean(.epred), sd = sd(.epred))
```

None:
Sinobaatar_lingyuanensis_IVPP V12517: 
Chaoyangodens_lii_JZT005-2010: 
Mirusodens_caii_HT-B-PM-0001: 

```{r}
f_preds <- bind_rows(list(d1, d2, d3, d4, d5, d6, d7, d8, d9, d10,
                              d11, d12, d13, d14, d15, d16, d17, d18, d19, d20,
                              d21, d22, d23)) |> 
  mutate(log_mass = (mean * 2.017734) + 5.554791) |> 
  mutate(Mass_grams = (exp(log_mass))) |> 
  select(Mass_grams, log_mass, Specimen_Num) |> 
  right_join(fdat, by = "Specimen_Num") |> write_csv(here("Data", "Mass_Predictions.csv"))
        
```

x - mean(x) / sd(x) = x

#```{r}
mod %>% 
    add_epred_draws(newdata = fdat[3,], 
                    #allow_new_levels = TRUE, 
                    #re_formula =  Mass_grams ~ Sl + Hl + Hsw + Hdw + Uol + Rl + Fl + Fsw + Tl + Tmw
                    ) %>% 
    as.data.frame() |> 
  mutate(mass_in_g = exp(.epred)) |> 
  ggplot(aes(x = mass_in_g)) +   stat_halfeye(.width = c(.5, .8, .95))
```

