---
title: "Mass Prediction"
output: html_notebook
---

Need to predict the mass for a bunch of the new fossils. 


```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, purrr)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

source(here("Code","Name_Change.R"))

dat <- read_csv(here("Data", "Raw_Extant_Data.csv")) |> 
   mutate_at(vars(Sl:Cl,Mass_grams), log) |> 
  mutate(fossil = "N")

fdat <- read_csv(here("Data", "Fossil_Measurements_20250319.csv")) |>  mutate_at(vars(Sl:Cl,Mass_grams), log) |> 
  mutate(fossil = "Y")

comb_dat <- dat |> bind_rows(fdat) |> 
  select(Order, Family, Genus, species, Genus_species, Taxon_Upham_style, Specimen_Number, Mass_grams, Mass_source, Loc_mode_Categorical, Loc_mode_Ordinal, Loc_mode_binary, Loc_mode_source, Sl,Hl,Hsw,Hdw,Uol,Ul,Rl,Fl,Fsw,Fdw,Tl,Tmw,Ipl,Pppl,Mtl, Ppl,Mcl, Tpw,Isl,Il,Pel,Hpw, Mcw,Ppw,Cl, fossil) |> 
  mutate_at(vars(Sl:Cl), scale2)

# This is the mean and sd of the log transformed mass in grams. Can be used to reconstruct the actual mass of fossil predicitons. 
mass_vars <- comb_dat |> 
  summarise(mean = mean(Mass_grams, na.rm = T),
            sd = sd(Mass_grams, na.rm = T))

comb_dat <- comb_dat |> mutate(Mass = scale2(Mass_grams))

fdat <- comb_dat |> filter(fossil == "Y") |> select(!fossil)

dat <- comb_dat |> filter(fossil == "N") |> select(!fossil)

var_complete_linear <-  read_rds(here("Data", "var_complete_linear.Rds"))


```

Extant Model
Complete Measurements:
Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Tl + Tmw
less that 50% missing measurements:
Sl,Hl,Hsw,Hdw,Uol,Ul,Rl,Fl,Fsw,Fdw,Tl,Tmw,Ipl,Pppl,Mtl, Ppl,Mcl, Tpw,Isl,Il,Pel,Hpw, Mcw,MRI,Ppw,Cl
```{r}
#p1 = c(prior(normal(0, 3), class = Intercept),
#       prior(normal(0, 1), class = b),
#       prior(normal(0, 1), class = sigma))
#
#mod <- brm(Mass ~   Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Tl + Fdw + Tmw ,
#          family = gaussian(),
#          data = dat, refresh = 0, 
#          cores = 4,
#          prior = p1)

```

## Updates 19 March

Using a csv generated in Claude, I have the `Genus_species`, `Specimen_Num`, and `formula` columns. the formula contains all the non-NA variables for each fossil specimen. 


##Formulas

Bind formula's to the fdat data.
```{r}
#formula_data <- read_csv(here("Data", "Fossil_Formulas2.csv")) |> 
 # select(Specimen_Number, formula)

#fdat <- fdat |> right_join(formula_data, by = "Specimen_Number") |> 
 # write_csv(here("Data", "Fdat_formula.csv"))


#Get formulas using GPT code


# Function to generate the formula without NA values
generate_formula <- function(row) {
  # Exclude specific columns (like Mass and existing formula)
  measurement_cols <- names(row)[13:37]  # Adjust indices based on your data
  # Get the non-NA column names and remove any 'NA' string that may be present
  non_na_terms <- measurement_cols[row[measurement_cols] != 'NA' & !is.na(row[measurement_cols])]
  # Construct the formula, ensuring no NA values are included
  new_formula <- paste(non_na_terms, collapse = "+")
  return(new_formula)
}

# Apply the function to each row and create a new column
fdat$formula <- apply(fdat, 1, 
                      generate_formula)

# Save the corrected dataframe to a new CSV file
fdat <- fdat |> filter(formula != "")

fdat |> write.csv(here("Data",  "corrected_fdat.csv"), row.names = FALSE)

specimens <- c("BMNH_PM1343", "CAGS01-IG1A", "MOR_109108A", "STM33-5", "CAGS00-IG03",
               "IVPP_V23387", "IVPP_V20778", "UM_41870", "BMNH1143", "ZPAL_Mgm-I/41")

#fdat <- fdat |> filter(Specimen_Number %in% specimens)

#fdat <- fdat |> filter(Specimen_Number %in% c("BMNH_PM1343", "CAGS01-IG1A"))

#fdat <- fdat |> filter(Specimen_Number %in% specimens)

```


## GPT

```{r}
# Fit model specifying strictly consistent data usages
process_row <- function(Specimen_Number, formula, model_data, fit_data) {
  
  # Combine "Mass ~" with the formula
  formula_text <- paste("Mass ~", formula)
  
  # Fit the model using the fixed data (dat)
  mod <- brm(formula = as.formula(formula_text),
             family = gaussian(),
             data = fit_data,
             refresh = 0,
             cores = 4,
             silent = 2,
             prior = p1)  # Ensure prior is defined earlier in your code

  # Generate predictions for the current fossil using add_epred_draws
  predictions <- mod |> 
    tidybayes::add_epred_draws(newdata = model_data %>% 
                                 filter(Specimen_Number == !!Specimen_Number)) %>%
    as_tibble() %>%
    summarise(mean_mass = mean(.epred, na.rm = TRUE),
              sd_mass = sd(.epred, na.rm = TRUE))
  
  cat('Processed', Specimen_Number, '\n')

  # Ensure Specimen present post-fit
  if(nrow(predictions) == 0) stop("Empty prediction on Specimen ")
  
  # Return a tibble with the Specimen_Number and predictions
  tibble(Specimen_Number = Specimen_Number,
         Mean_Mass = predictions$mean_mass,
         SD_Mass = predictions$sd_mass)
}

# Processing selected Specimen numbers & independently supplying fits
results <- fdat2 %>%
  select(Specimen_Number, formula) %>%
  pmap_dfr(~ process_row(.x, .y, fdat2, dat))

# Convert results
results <- results |> 
  mutate(
    log_mass = (Mean_Mass * 2.010932) + 5.520125,
    Mass_grams = (exp(log_mass))
  )

fdat2 |> select(Specimen_Number, Genus_species) |> 
  right_join(results, by = "Specimen_Number") |> 
   mutate_at(vars(Mean_Mass:Mass_grams), round, 2) |> 
  write_csv(here("Data", "Mass_Predictions.csv"))
```



Combine with raw data


```{r}
mass_dat <- read_csv(here("Data", "Mass_Predictions.csv")) |> select(Specimen_Number, Mass_grams)

fd <- read_csv(here("Data", "Raw_Fossil_Data_20250320.csv")) 

fd2 <- read_csv(here("Data", "Fossil_Measurements_20250319.csv")) |> 
  select(c("Order", "Family", "Genus", "species", "Taxon_Upham_style", "Specimen_Number",  "Loc_mode_Categorical", "Loc_mode_Ordinal", "Loc_mode_binary")) 

fd |> select(!c(Mass_grams, Mass_source)) |> 
  right_join(mass_dat, by = "Specimen_Number") |> 
  relocate(Mass_grams, .after = Specimen_Number) |> 
  relocate(Genus_species, .before = Specimen_Number) |> 
  #select(!c("Mean_Mass", "SD_Mass", "log_mass")) |> 
  right_join(fd2, by = "Specimen_Number") |> 
  rename(NOTES = "Additional Notes",
         Pdpw = "Ppdw") |> 
  write_csv(here("Data", "Estimated_Fossil_Data_20250320.csv"))


```






