---
title: "Binary Interaction Classification"
output: html_notebook
---

Copy of `Binary_Missing_Models.Rmd` but with the interaction term!

Predicting binary climbing classifications (tree vs. ground) using postcranial measurements and interactions. Models will also incorperate intraspecific variation and phylogenetic variation.

# Preparation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()


source(here("Code","Name_Change.R"))
```

### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  filter(Genus_species !=  c('Leopardus_geoffroyi', 
                             'Urocyon_cinereoargenteus')) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family))
#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

## Description of Missing Data
Follows `Binary_Missing_Models.Rmd`

```{r}
var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
```

```{r}
var_complete <- var_complete[c(1, 14:23)]
var_missing <- var_missing[c(1:2,4,7,10,16,18,20)]
```

The percentages are stored in the df `Missing_Data_Percents.csv`

# Fit GM Models

## Geometric Mean Complete  

#### Prior 
same prior as above
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Sl * log_gm + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_b_gm <- vector(mode ="list")

for(i in var_complete){
  list_b_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "*log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing GM

Update cannot be used with multivariate models

Prior must be called in the loop



#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")*log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_gm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_gm %>% write_rds(here("Data","B_Ind_gm_mods.Rds"))
```



# Fit Size Free Models

## Geometric Mean Complete  

#### Prior 
same prior as above
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Sl  + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_b_nm <- vector(mode ="list")

for(i in var_complete){
  list_b_nm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing GM

Update cannot be used with multivariate models

Prior must be called in the loop



#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_nm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_nm %>% write_rds(here("Data","B_Ind_NOMASS_mods.Rds"))
```

# Fit GM NoInt Models


#### Prior  
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Uol + log_gm + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```


#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide'}

list_b_gm <- vector(mode ="list")

for(i in var_complete){
  list_b_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "+log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing log(Mass)

Update cannot be used with multivatiate models

Prior must be called in the loop


#### Run Loop

```{r message = FALSE, warning=FALSE, results = 'hide'}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")+log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_gm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_gm %>% write_rds(here("Data","B_Ind_gmNoInt_mods.Rds"))

```

# Plotting

```{r}
pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes, ggstar)


list_b_gm <- read_rds(here("Data","B_Ind_gmNoInt_mods.Rds"))
list_b_nm <- read_rds(here("Data","B_Ind_NOMASS_mods.Rds"))
list_b_igm <- read_rds(here("Data","B_Ind_gm_mods.Rds"))
```



```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[2] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[17] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[17]))

#for no mass
cln3 <- function(df) as_draws_df(df)[16] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[16]))

```

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
lms <- map(list_b_igm[2:11], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_igm[12:19], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms_int <- lms %>% bind_rows(lms2) %>% 
  mutate(type = "GM_Interation") 
rm(lms, lms2)

lms <- map(list_b_nm[2:11], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_nm[12:19], cln3) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms_no <- lms %>% bind_rows(lms2) %>% 
  mutate(type = "No_GM") 
rm(lms, lms2)

lms <- map(list_b_gm[2:11], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_gm[12:19], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms_gm <- lms %>% bind_rows(lms2) %>% 
  mutate(type = "GM_No_Interaction") 
rm(lms, lms2)

lms_gm <- bind_rows(lms_gm, lms_int, lms_no)
```



##Good  Plot
```{r}
pal2 <- LaCroixColoR::lacroix_palette("Orange", n = 30, type = "continuous")[c(1,5,10,12,13,14,15,16,17,18,25,28)]

lms_gm %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean)) +
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  tidytext::scale_y_reordered("") +
  labs(x = "Measurement effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  artyfarty::theme_scientific() + 
  facet_wrap(~type, scales = 'free_y') +
  theme(strip.background = element_blank(),
        legend.position="none")

ggsave(here("Plots", "Bin_Index_Mass_Test_Compare.pdf"))
```

# Prediction Accuracy

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements. 

```{r}
#purrr keep_at is great!
pred_vars <- c(var_complete[2:11], var_missing)

list_b_gm  <- read_rds(here("Data","B_Ind_gmNoInt_mods.Rds"))  %>% keep_at(pred_vars)
list_b_nm  <- read_rds(here("Data","B_Ind_NOMASS_mods.Rds")) %>% keep_at(pred_vars)
list_b_igm <- read_rds(here("Data","B_Ind_gm_mods.Rds")) %>% keep_at(pred_vars)


dgm <- as.data.frame(names(list_b_gm)) 
colnames(dgm) <- "var"

dnm <- as.data.frame(names(list_b_nm)) 
colnames(dnm) <- "var"

digm <- as.data.frame(names(list_b_igm)) 
colnames(digm) <- "var"


```

Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model

## Fossil Functions
```{r}
colz <- c("Genus_species", "log_Mass", names(list_b_gm), "Specimen_Num")

fdat <- read_csv(here("Data", "Fossil_Master.csv"))

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

fd <- fdat %>% select(all_of(colz))

nnn <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "Locbin",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
    mutate(var = {{nm}})
}

```


```{r}
#WITH PHYLO
bin_pred_phy <- function(model){
  set.seed(124)
  d <-  predict({{model}}, summary = T, probs = c(0.055, 0.945),  resp = 'Locbin')
  d2 <- as.data.frame(d) %>% 
    rename_all(.,
               function(x) case_when(x == 'Estimate.Locbin' | x == 'Estimate' ~ 'pred',
                                     TRUE ~ x)) %>% 
  select(pred) %>% 
  mutate(pred_round = round(pred, digits = 0),
         actual = {{model}}[[2]][[1]],
         #spec = {{model}}[[2]][[]],
        # num = dat[[7]],
         dif = abs(pred_round - actual),
        species = {{model}}[[2]]$Genus_species
        ) #%>% 
  #summarise(accuracy_phy = round((sum(dif == 0)/427) * 100, digits = 1))
  return(d2)
}


bin_pred_phy_fn <- function(df){
  map(df, ~bin_pred_phy(.x)) %>% bind_rows()
}


## NO PHYLO
bin_pred_nophy <- function(model){
  set.seed(124)
  d <-  predict({{model}}, summary = T, probs = c(0.055, 0.945),  re_formula = NA, resp = 'Locbin')
  d2 <- as.data.frame(d) %>% 
    rename_all(.,
               function(x) case_when(x == 'Estimate.Locbin' | x == 'Estimate' ~ 'pred',
                                     TRUE ~ x)) %>% 
  select(pred) %>% 
  mutate(pred_round = round(pred, digits = 0),
         actual = {{model}}[[2]][[1]],
         #spec = {{model}}[[2]][[]],
        # num = dat[[7]],
         dif = abs(pred_round - actual),
        species = {{model}}[[2]]$Genus_species)
}


bin_pred_nophy_fn <- function(df){
  map(df, ~bin_pred_nophy(.x)) %>% bind_rows()
}

# Order and Family

# Phy is the same (all group_levels)

## NO PHYLO is different
bin_pred_tax_nophy <- function(model){
  set.seed(124)
  set.seed(124)
  d <-  predict({{model}}, summary = T, probs = c(0.055, 0.945),  re_formula = ~ (1|Order) + (1|Family), resp = 'Locbin')
  d2 <- as.data.frame(d) %>% 
    rename_all(.,
               function(x) case_when(x == 'Estimate.Locbin' | x == 'Estimate' ~ 'pred',
                                     TRUE ~ x)) %>% 
  select(pred) %>% 
  mutate(pred_round = round(pred, digits = 0),
         actual = {{model}}[[2]][[1]],
         #spec = {{model}}[[2]][[]],
        # num = dat[[7]],
         dif = abs(pred_round - actual),
        species = {{model}}[[2]]$Genus_species)
}


bin_pred_tax_nophy_fn <- function(df){
  map(df, ~bin_pred_tax_nophy(.x)) %>% bind_rows()
}

```

```{r}

pred1 <- map(1, ~bin_pred_phy_fn(list_b_gm)) %>% 
  bind_rows() %>% 
  mutate(var = rep(dgm$var, each = 427),
         method = 'phy',
         mass = 'gm')

pred2 <- map(1, ~bin_pred_nophy_fn(list_b_gm)) %>% 
  bind_rows() %>% 
  mutate(var = rep(dgm$var, each = 427),
         method = 'no_phy',
         mass = 'gm')


pred3 <- map(1, ~bin_pred_phy_fn(list_b_nm)) %>% 
  bind_rows() %>% 
  mutate(var = rep(dnm$var, each = 427),
         method = 'phy',
         mass = 'no_mass')

pred4 <- map(1, ~bin_pred_nophy_fn(list_b_nm)) %>% 
  bind_rows() %>% 
  mutate(var = rep(dnm$var, each = 427),
         method = 'no_phy',
         mass = 'no_mass')

pred5 <- map(1, ~bin_pred_phy_fn(list_b_igm)) %>% 
  bind_rows() %>% 
  mutate(var = rep(digm$var, each = 427),
         method = 'phy',
         mass = 'gm_int')

pred6 <- map(1, ~bin_pred_tax_nophy_fn(list_b_igm)) %>% 
  bind_rows() %>% 
  mutate(var = rep(digm$var, each = 427),
         method = 'no_phy',
         mass = 'gm_int')

preds <- bind_rows(pred1, pred2, 
                   pred3, pred4, 
                   pred5, pred6) %>%
  write_csv(here("Data", "test_extant_predictions.csv"))
preds <- read_csv(here("Data", "test_extant_predictions.csv"))
#This is the full pred df from the `Binary_Prediction_Accuracy.Rmd` script
#preds <- read_csv(here("Data", "extant_predictions.csv"))
```


## Accuracy

```{r}
accuracy <- preds %>% 
  group_by(method, var, mass) %>%  
  filter(method == "no_phy") %>% 
  summarise(accuracy = round((sum(dif == 0)/427) * 100, 
                             digits = 1)) %>% 
  select(var, accuracy, method, mass) %>% 
  #filter(#accuracy > 70,
  #       method %in% c('no_phy', 'no_phy_int', 'no_phy_tax')
  #       ) %>% 
  arrange(desc(accuracy)) 
 #arrange(mass, desc(accuracy)) 


accuracy %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

