---
title: "Ordinal Multiple Predictors - Automated"
#output: html_notebook
---

# Ordinal Fossil Prediction Models

I need to run a series of models to cover all the combinations of measurements found in the fossil data. 

The steps are:
  - Run the "formula" code to get the list of all the variables for each taxon
  - Run a series of models for each combination of missing data.

# Preparation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
var_acc <- read_rds(here("Data", "var_accurate.Rds"))

source(here("Code","Name_Change.R"))
```

### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  filter(Genus_species !=  c('Leopardus_geoffroyi', 
                             'Urocyon_cinereoargenteus')) %>% 
  drop_na(Loc_Ord2) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family)) %>% 
  mutate(Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")))

#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

# Model Fits

### Load fossil data & generate formulas

```{r}
# Function to generate the formula without NA/NaN values
generate_formula <- function(row) {
  measurement_cols <- names(row)[2:15]
  non_na_terms <- measurement_cols[
    row[measurement_cols] != 'NA' &
    !is.na(row[measurement_cols]) &
    !is.nan(as.numeric(row[measurement_cols]))
  ]
  paste(non_na_terms, collapse = "+")
}

fdat_avg <- read_csv(here("Data", "Fossil_Master.csv")) %>% 
  group_by(Genus_species) %>% 
  summarise_at(vars(log_Mass:PES2), mean, na.rm = T) %>% 
  select(c(Genus_species, PES2, HPI, PES, MANUS, 
           Ppl, Hl, OLI, Pipl, MANUS2, Rl, Ipl, 
           Uol, Fl, Ul, log_Mass))

fdat_avg$formula <- apply(fdat_avg, 1, generate_formula)
```

### Review formulas and species groupings

This table shows every species and its formula, with `n` indicating how many species share that formula. Use this to check groupings before running models.

```{r}
fdat_avg |> 
  select(Genus_species, formula) |> 
  arrange(formula) |> 
  group_by(formula) |> 
  mutate(n = n()) |>
  print(n = Inf)
```

### Define species to exclude

Species with too few measurements are excluded automatically based on the threshold below. Review the printed list to confirm.

```{r}
# Exclude species with fewer than 3 predictor variables
# To change threshold: str_count < 1 means fewer than 2 vars,
#                      str_count < 2 means fewer than 3 vars,
#                      str_count < 3 means fewer than 4 vars, etc.
exclude_spp <- fdat_avg |>
  select(Genus_species, formula) |>
  filter(formula == "" | str_count(formula, "\\+") < 1) |>
  pull(Genus_species)

cat("Species excluded due to too few measurements:\n")
cat(paste("-", exclude_spp, collapse = "\n"), "\n")
```

### Define helper functions

```{r}
# Imputation submodels - one per variable with missing data
submodels <- list(
  PES2   = bf(PES2|   mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  MANUS  = bf(MANUS|  mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  PES    = bf(PES|    mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  Ppl    = bf(Ppl|    mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  MANUS2 = bf(MANUS2| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  HPI    = bf(HPI|    mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  Ipl    = bf(Ipl|    mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian(),
  Pipl   = bf(Pipl|   mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()
)

# Variables that get mi() wrapping in the outcome formula
mi_vars <- names(submodels)

# Prior function
prio <- function(mod) {
  get_prior({{mod}},
            data2 = list(A = A),
            data = dat) %>% 
    mutate(
      prior = case_when(
        class == "b"         ~ "normal(0, 2)",
        class == "sd"        ~ "normal(0, 0.3)",
        class == "Intercept" ~ "student_t(5, 0, 0.6)",
        class == "sigma"     ~ "normal(0, 0.5)",
        TRUE ~ prior
      ))
}

# Prediction function
pred_ext <- function(mod, dat) {
  {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, .category, Prob_of_Climbing) %>% 
    mutate(method = "Fossil",
           substrate = NA)
}
```

### Build formula groups

Groups species by shared formula — each unique formula gets one model.

```{r}
formula_groups <- fdat_avg |>
  select(Genus_species, formula) |>
  filter(
    !Genus_species %in% exclude_spp,
    formula != ""
  ) |>
  group_by(formula) |>
  summarise(species = list(Genus_species), .groups = "drop") |>
  deframe()

# Print a summary so you can see what will be fitted
iwalk(formula_groups, \(spp, form) {
  cat("Formula:", form, "\n")
  cat("Species:", paste(spp, collapse = ", "), "\n\n")
})
```

# Run Models

```{r message = FALSE, warning=FALSE}
plan(sequential)  # change to plan(multisession, workers = 3) to parallelise

results <- imap(formula_groups, \(spp, form) {
  
  cat("Fitting model for formula:", form, "\n")
  cat("Species:", paste(spp, collapse = ", "), "\n\n")
  
  # Wrap mi() variables in mi() - sort longest first to avoid substring matches
  # e.g. MANUS2 must be matched before MANUS
  form_mi <- str_replace_all(form,
    paste(mi_vars[order(-nchar(mi_vars))], collapse = "|"),
    \(x) paste0("mi(", x, ")"))
  
  # Build outcome bf()
  outcome_bf <- bf(
    as.formula(paste0(
      "Loc_Ord2 ~ ", form_mi,
      " + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style, cov = A))"
    )),
    family = cumulative()
  )
  
  # Attach only the submodels needed for this formula
  vars_needed <- mi_vars[mi_vars %in% str_split_1(form, "\\+")]
  
  if (length(vars_needed) == 0) {
    m_form <- outcome_bf
  } else {
    m_form <- reduce(c(list(outcome_bf), submodels[vars_needed]), `+`) + 
      set_rescor(FALSE)
  }
  
  pri <- prio(m_form)
  
  mod <- brm(m_form,
             data = dat,
             refresh = 0,
             cores = 4,
             data2 = list(A = A),
             prior = pri,
             seed = 145,
             silent = 2,
             control = list(max_treedepth = 15))
  
  out <- pred_ext(mod, fdat_avg |> filter(Genus_species %in% spp))
  
  rm(mod)
  gc()
  out
}, .progress = TRUE)
```

## Combine Model Outputs

```{r}
pred_df <- bind_rows(results) |> mutate(var = "combined")

pred_df |> write_csv(here("Data", "Fossil_Ord_Preds.csv"))
```

## Derive max_rank

Takes the long-format draws and finds the most probable category per draw per species.

```{r}
pred_wide <- pred_df |>
  arrange(Genus_species, .category) |>
  pivot_wider(
    names_from = .category,
    values_from = Prob_of_Climbing,
    values_fn = list
  ) |>
  unnest(cols = everything()) |>
  rename(P1 = "A", P2 = "Sc", P3 = "T", P4 = "B") |>
  mutate(wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))

pred_all <- pred_wide |>
  rownames_to_column("id") |>
  left_join(
    pred_wide |>
      rownames_to_column("id") |>
      gather(max_rank, max_prob, P1:P4) |>
      group_by(id) |>
      slice(which.max(max_prob)) |>
      select(id, max_rank, max_prob),
    by = "id"
  )
```

# Plots

## All Species

```{r}
pred_all |>
  mutate(
    rank = case_when(
      max_rank == "P1" ~ "Arboreal",
      max_rank == "P2" ~ "Scansorial",
      max_rank == "P3" ~ "Terrestrial",
      max_rank == "P4" ~ "Inter-Substrate"
    ),
    rank = fct_relevel(rank, c("Arboreal", "Scansorial", "Terrestrial", "Inter-Substrate")),
    Genus_species = gsub("_", " ", Genus_species)
  ) |>
  group_by(Genus_species, rank) |>
  count(max_rank) |>
  drop_na() |>
  ggplot(aes(y = Genus_species, x = n, fill = rank)) +
  geom_bar(position = "fill", stat = "identity", alpha = 0.8) +
  scale_fill_grey(start = 0.8, end = 0, name = "") +
  scale_x_continuous(
    breaks = c(0, 0.5, 1),
    label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))
  ) +
  labs(y = "", x = "Proportion of Estimates", title = "Fossil Predictions") +
  theme_classic() +
  theme(
    panel.border = element_blank(),
    axis.line = element_line(colour = "NA"),
    axis.ticks = element_line(linewidth = rel(0.25)),
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(face = "italic"),
    axis.text.y = element_text(face = "italic")
  ) +
  scale_y_discrete(limits = rev)

ggsave(here("Plots", "Ord_Pred_Fossil_All.pdf"), width = 10, height = 10)
ggsave(here("Plots", "Ord_Pred_Fossil_All.jpg"), width = 10, height = 10)
```

## Modified Plot - Selected Species in Order

```{r}
sps <- c("Maiopatagium fulculiferum", "Shenshou lui", "Vilevolodon diplomyos",
         "Arboroharamiya jenkinsi", "Arboroharamiya allinhopsoni", "Xianshou songae",
         "Feredocodon chowi", "Agilocodon scansorius", "Rugosodon eurasiaticus",
         "Juramaia sinensis", "Liaoconodon hui", "Jeholodens jenkinsi",
         "Repenomamus robustus", "Repenomamus giganticus", "Jeholbaatar kielanae",
         "Filikomys primaevus", "Kryptobaatar dashzevegi", "Akidolestes cifellii",
         "Henkelotherium guimarotae", "Eomaia scansoria", "Maotherium senensis",
         "Sinodelphys szalayi", "Cokotherium jiufotangensis", "Ambolestes zhoui")

pred_all |>
  mutate(
    rank = case_when(
      max_rank == "P1" ~ "Arboreal",
      max_rank == "P2" ~ "Scansorial",
      max_rank == "P3" ~ "Terrestrial",
      max_rank == "P4" ~ "Inter-Substrate"
    ),
    rank = fct_relevel(rank, c("Arboreal", "Scansorial", "Terrestrial", "Inter-Substrate")),
    Genus_species = gsub("_", " ", Genus_species)
  ) |>
  filter(Genus_species %in% sps) |>
  group_by(Genus_species, rank) |>
  count(max_rank) |>
  drop_na() |>
  ggplot(aes(y = factor(Genus_species, levels = rev(sps)), x = n, fill = rank)) +
  geom_bar(position = "fill", stat = "identity", alpha = 0.8) +
  scale_fill_grey(start = 0.8, end = 0, name = "") +
  scale_x_continuous(
    breaks = c(0, 0.5, 1),
    label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))
  ) +
  labs(y = "", x = "Proportion of Estimates", title = "Fossil Predictions") +
  theme_classic() +
  theme(
    panel.border = element_blank(),
    axis.line = element_line(colour = "NA"),
    axis.ticks = element_line(linewidth = rel(0.25)),
    legend.position = "bottom",
    axis.text.y = element_text(face = "italic")
  )

ggsave(here("Plots", "Ord_Pred_Fossil_ordered.pdf"), width = 8, height = 8)
ggsave(here("Plots", "Ord_Pred_Fossil_ordered.jpg"), width = 8, height = 8)
```
