---
title: "Ordinal Classification"
output: html_notebook
---

Predicting Ordinal Locomotion classifications (6 rankings) using postcranial measurements. Models will also incorporate intraspecific variation and phylogenetic variation.

## Preperation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()
```

### Load data  
### Load data  
```{r message = FALSE, warning=FALSE}
dat <- read_sheet("https://docs.google.com/spreadsheets/d/1-eknhyZ1JNnXqhg2kViyzVntC8NGZvILQX-aQQb1Jvk/edit#gid=325036460", na = c("NA", "?", "")) %>%
  select(!NOTES) %>% 
# Recode Ordinal Rankings
  mutate(Loc_Ord = case_when(Loc_mode_Ordinal == "G"  ~ "G",
                             Loc_mode_Ordinal == "A"  ~ "A",
                             Loc_mode_Ordinal == "Sc" ~ "Sc",
                             Loc_mode_Ordinal == "T"  ~ "T",
                             Loc_mode_Ordinal == "Is" ~ "Is",
                             Loc_mode_Ordinal == "Sf" ~ "Sf",
                             Loc_mode_Ordinal == "Ss" ~ "Ss",
                             TRUE ~ NA),
         Loc_Ord = as.ordered(Loc_Ord),
         Loc_Ord = fct_relevel(Loc_Ord, c("G","A","Sc","T","Is","Sf","Ss")),
         # Combining the Intersurface and Semifossorial
         Loc_Ord2 = case_when(Loc_mode_Ordinal == "G" ~ "G",
                              Loc_mode_Ordinal == "A" ~ "A",
                              Loc_mode_Ordinal == "Sc" ~ "Sc",
                              Loc_mode_Ordinal == "T" ~ "T",
                              Loc_mode_Ordinal == "Is" ~ "Sf",
                              Loc_mode_Ordinal == "Sf" ~ "Sf",
                              Loc_mode_Ordinal == "Ss" ~ "Ss",
                             TRUE ~ NA),
         Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("G","A","Sc","T","Sf","Ss")),
         Loc_bin = case_when(Loc_mode_Bindary == "Ground" ~ 0,
                             Loc_mode_Bindary == "Tree" ~ 1,
                             TRUE ~ NA
                             ),
        # Loc_bin = as.factor(Loc_bin),
         Loc_mode_Categorical = as.factor(Loc_mode_Categorical),
         log_Mass = log(Mass_grams)) %>% 
    relocate(Loc_bin, .after = Loc_mode_Bindary) %>% 
  relocate(Loc_Ord, .after = Loc_mode_Ordinal) %>% 
  relocate(Loc_Ord2, .after = Loc_Ord) %>%
  relocate(log_Mass, .before = Skl) %>% 
#################
#Calculate Indices!
#################
  mutate(SI = Sh / Sl,             # Scapular Index
         HRI = Hsw / Hl,           # Humeral Robustness Index
         HPI = Hpw / Hl,           # Humeral Proximal Index
         HEB = Hdw / Hl,           # Humeral Epicondyle Breadth
         HHRI = Hhl / Hl,          # Humeral Head Robustness Index
         HHW = Hhw / Hhl,          # Humeral Head Shape Index
         DI = Hdcw / Hsw,          # Deltopectoral Crest Index
         OLI = Uol / Ul,           # Olecranon Process Length Index
         BI = Rl / Hl,             # Brachial Index
         IM = (Hl+Ul)/(Fl+Tl),     # Intermembral Index
         PRTI = Mcl/(Hl+Rl),       # Palm Robustness Index
         MRI = Mcw / Mcl,          # Metacarpal Robustness
         MANUS = Ppl / Mcl,        # MANUS index
         MANUS2 = (Ppl+Ipl)/Mcl,   # MANUS index with intermed. phalanx
         IRI = Fgh / Fl,           # Gluteal Index
         FRI = Fsw / Fl,           # Femoral Robustness
         FEB = Fdw / Fl,           # Femoral Epicondyle Breadth
         CI = Tl / Fl,             # Crural Index
         TRI = Tmw / Tl,           # Tibial Robustness Index
         #ANR = Anl / Al,          # Astragular Neck Robustness Index
         #CAR = Cal / Cl,          # Calcaneal Robustness Index
         IRI = Il / Pel,           # Illium Robustness Index
         PR = Il / Isl,            # Pelvic Index
         PES = Pppl / Mtl,         # PES INdex
         PES2 = (Pppl+Pipl)/Mtl    # PES with intermediate Phalanx
         ) %>% 
    # geometric mean
  drop_na(Tmw, Fdw, Tl, Fl, Fsw , Sh, Sl, Hdw, Hl, Hsw, Rl, Ul, Uol) %>%
  mutate(gm = ( Tmw * Fdw * Tl * Fl * Fsw  * Sh * Sl * Hdw * Hl * Hsw * Rl * Ul * Uol)^(1/13)) %>%
  relocate(gm, .before = log_Mass) %>% 
  mutate_at(vars(19:73), log) %>% 
  mutate_at(vars(17:95), scale2)

spp_obs <- dat$Taxon_Upham_style %>% unique()
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

### Fit Models 


Looping over all of the variables to see which ones do a good job predicting the binary tree vs. no-tree categorization

#### Get Prior

```{r message = FALSE, warning=FALSE, include = FALSE}

p1 <- get_prior(Loc_Ord2 ~ Sl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
  data2 = list(A = A),
           family = cumulative(),
           data = dat) %>% 
    mutate(
      prior = case_when(
        class == "b"  ~ "normal(0, 1)",
        class == "sd" ~ "normal(0, 1)",
        class == "Intercept" ~ "normal(0, 1)",
        TRUE ~ prior
      )
    )
```


```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_Ord2 ~ Sl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```



```{r}

pls = c("#7570b3" ,  "#85D4E3" , "#0D7E9A",'#f5f5cb', '#c7e6d4', '#8cd2cd', '#55c3cf', '#3fa4b0', '#187389','#f48a1a', '#e6ab02', '#66a61e', '#85D4E3', '#0D7E9A', '#7570b3','#f6d03d', '#fe7b30', '#ef4a27', '#f384f8', '#625afc', '#0d57ff', '#47a7ff','#5771ff', '#6bae9e', '#31c1bb', '#7af1e1', '#d5e1af', '#f48130','#C60C30', '#00A1DE', '#62361B', '#009B3A', '#f9581c', '#522398', '#E27EA6', '#F9E300', '#565A5C')
```

```{r}
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#7570b3')
plot(conditional_effects(mm, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)
```

#### Log Mass Loop

```{r  message = FALSE, warning=FALSE, include = FALSE,}
varis <- colnames(dat)[19:95]

list_o_lm <- vector(mode ="list")

for(i in varis){
  list_o_lm[[i]]<- update(mm,
                         formula=(paste0("Loc_Ord ~", i, "+log_Mass+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1
                         ) 
}

list_o_lm %>% write_rds(here("Data","ordinal_lm_models.Rds"))
```


#### Geometric Mean Loop

```{r  message = FALSE, warning=FALSE, include = FALSE,}
varis <- colnames(dat)[19:95]

list_o_gm <- vector(mode ="list")

for(i in varis){
  list_o_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_Ord ~", i, "+gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1
                         ) 
}

list_o_gm %>% write_rds(here("Data","ordinal_gm_models.Rds"))
```



```{r message = FALSE, warning=FALSE}
list_o_lm <- read_rds(here("Data","ordinal_lm_models.Rds"))
list_o_gm <- read_rds(here("Data","ordinal_gm_models.Rds"))
for(i in list_o_lm){
 plots <- plot(conditional_effects(i, categorical = TRUE), plot=F, points = T)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)
 print(plots + theme_bw())
}

for(i in list_o_gm){
 plots <- plot(conditional_effects(i, categorical = TRUE), plot=F, points = T)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)
 print(plots + theme_bw())
}

```

```{r}
p1 <- plot(conditional_effects(list_o_lm$FEB, categorical = TRUE), plot=F, points = T)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)+ ylim(0,1)

p2 <- plot(conditional_effects(list_o_gm$FEB, categorical = TRUE), plot=F, points = T)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) + ylim(0,1)

p1 + p2
```
How to plot the effect sizes?
loop <- not working, problem with paste,  need to try purrr?
```{r}
d1 <- bind_rows(
  as_draws_df(list_o_lm$IM) %>% select(b_IM) %>% gather(var, val),
) %>% 
  mutate(val = inv_logit_scaled(val)) 

lil_lst <- list_o_lm[1:3]

gm_p <- data.frame()

for(i in lil_lst){
  gmp[[i]]<- bind_rows(
  as_draws_df(paste("list_o_lm$",i)) %>% select(paste("b_",i)) #%>% gather(var, val),
)
} 
  %>% 
  mutate(val = inv_logit_scaled(val))
} 
```

    update(mm,
                         formula=(paste0("Loc_Ord ~", i, "+gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1
                         ) 

d1 %>% 
  #mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var)) +   stat_halfeye(.width = c(.66, .95)) +
  geom_vline(xintercept = 0.5, linetype = 3) + theme_tidybayes()




```{r}
loo(list_o_gm$MANUS, list_o_lm$MANUS)
loo(list_o_gm$HPI, list_o_lm$HPI)
loo(list_o_gm$FRI, list_o_lm$FRI)
loo(list_o_gm$OLI, list_o_lm$OLI)
```





```{r}
d1 <- bind_rows(
  as_draws_df(fit_list$Hl) %>% select(b_Hl) %>% gather(var, val),
  as_draws_df(fit_list$Uol) %>% select(b_Uol) %>% gather(var, val),
    as_draws_df(fit_list$Hhl) %>% select(b_Hhl) %>% gather(var, val),
    as_draws_df(fit_list$Ul) %>% select(b_Ul) %>% gather(var, val),
    as_draws_df(fit_list$Rl) %>% select(b_Rl) %>% gather(var, val),
    as_draws_df(fit_list$Anl) %>% select(b_Anl) %>% gather(var, val),
    as_draws_df(fit_list$Mtl) %>% select(b_Mtl) %>% gather(var, val),
  as_draws_df(fit_list$Ppl) %>% select(b_Ppl) %>% gather(var, val),
  as_draws_df(fit_list$Ipl) %>% select(b_Ipl) %>% gather(var, val),
  as_draws_df(fit_list$HPI) %>% select(b_HPI) %>% gather(var, val),
    as_draws_df(fit_list$HEB) %>% select(b_HEB) %>% gather(var, val),
  as_draws_df(fit_list$OLI) %>% select(b_OLI) %>% gather(var, val),
  as_draws_df(fit_list$MANUS) %>% select(b_MANUS) %>% gather(var, val),
    as_draws_df(fit_list$MANUS2) %>% select(b_MANUS2) %>% gather(var, val),
  as_draws_df(fit_list$FRI) %>% select(b_FRI) %>%
    gather(var, val),
  as_draws_df(fit_list$FEB) %>% select(b_FEB) %>% gather(var, val),
  as_draws_df(fit_list$CI) %>% select(b_CI) %>% gather(var, val),
  as_draws_df(fit_list$PR) %>% select(b_PR) %>% gather(var, val),
  as_draws_df(fit_list$PES) %>% select(b_PES) %>% gather(var, val),
  as_draws_df(fit_list$PES2) %>% select(b_PES2) %>% gather(var, val)
  ) %>% 
  mutate(val = inv_logit_scaled(val)) 

nms <- d1 %>% group_by(var) %>% summarise(mean = mean(val)) %>% arrange(mean) %>%  select(var)



d1 %>% 
  mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var)) +   stat_halfeye(.width = c(.66, .95)) +
  geom_vline(xintercept = 0.5, linetype = 3) + theme_tidybayes()
```

```{r}
d1 <- bind_rows(
   as_draws_df(fit_list$Hl) %>% select(b_Hl, b_log_Mass) %>% gather(var, val),
    as_draws_df(fit_list$Uol) %>% select(b_Uol) %>% gather(var, val),
    as_draws_df(fit_list$Hhl) %>% select(b_Hhl) %>% gather(var, val),
    as_draws_df(fit_list$Ul) %>% select(b_Ul) %>% gather(var, val),
    as_draws_df(fit_list$Rl) %>% select(b_Rl) %>% gather(var, val),
    as_draws_df(fit_list$Anl) %>% select(b_Anl) %>% gather(var, val),
    as_draws_df(fit_list$Mtl) %>% select(b_Mtl) %>% gather(var, val),
    as_draws_df(fit_list$Ppl) %>% select(b_Ppl) %>% gather(var, val),
    as_draws_df(fit_list$Ipl) %>% select(b_Ipl) %>% gather(var, val),
    as_draws_df(fit_list$HPI) %>% select(b_HPI) %>% gather(var, val),
    as_draws_df(fit_list$HEB) %>% select(b_HEB) %>% gather(var, val),
    as_draws_df(fit_list$OLI) %>% select(b_OLI) %>% gather(var, val),
    as_draws_df(fit_list$MANUS) %>% select(b_MANUS) %>% gather(var, val),
    as_draws_df(fit_list$MANUS2) %>% select(b_MANUS2) %>% gather(var, val),
    as_draws_df(fit_list$FRI) %>% select(b_FRI) %>% gather(var, val),
    as_draws_df(fit_list$FEB) %>% select(b_FEB) %>% gather(var, val),
    as_draws_df(fit_list$CI) %>% select(b_CI) %>% gather(var, val),
    as_draws_df(fit_list$PR) %>% select(b_PR) %>% gather(var, val),
    as_draws_df(fit_list$PES) %>% select(b_PES) %>% gather(var, val),
    as_draws_df(fit_list$PES2) %>% select(b_PES2) %>% gather(var, val),
    as_draws_df(fit_list$Fbdw) %>% select(b_Fbdw) %>% gather(var, val)
  ) %>% 
  mutate(val = inv_logit_scaled(val)) 

nms <- d1 %>% group_by(var) %>% summarise(mean = mean(val)) %>% arrange(mean) %>%  select(var)



d1 %>% 
  mutate(var = fct_relevel(var, nms$var)) %>% 
  ggplot(aes(x = val, y = var)) +   stat_pointinterval(.width = c(.66, .95)) +
  geom_vline(xintercept = 0.5, linetype = 3)
```


