---
title: "Ordinal Accuracy"
output: html_notebook
---

Calculating Accuracy in the Ordinal models.

Largely taken from carnivoran accuracy calculations script.


```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, furrr)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))

source(here("Code","Name_Change.R"))
```


### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  drop_na(Loc_Ord2) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family)) %>% 
  mutate(Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")))

fdat <- read_csv(here("Data", "Fossil_Master.csv"))

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

pred_vars <- dat %>% select(Sl:lsCl) %>% colnames()
#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements. 

```{r}

list_o_lm <- read_rds(here("Data","O_lm_int_mods_mis.Rds"))
#purrr keep_at is great!
list_o2i <- list_o_lm %>% keep_at(pred_vars)

names(list_o2i)

rm(list_o_lm)



list_o_gm <- read_rds(here("Data","O_gm_int_mods_mis.Rds"))
#purrr keep_at is great!
list_o2gi <- list_o_gm %>% keep_at(pred_vars)

names(list_o2gi)

rm(list_o_gm)
```



# Functions
```{r}

model <- list_o2gi$MANUS
ord_pred <- function(model){
set.seed(124)
  d <-  predict({{model}}, summary = T, probs = c(0.055, 0.945),  resp = 'LocOrd2')
  d2 <- as.data.frame(d) %>% 
    mutate(actual = as.factor({{model}}[[2]][[1]]),
           actual= case_when(actual == "A"  ~ 1,
                             actual == "Sc" ~ 2,
                             actual == "T"  ~ 3,
                             actual == "B" ~ 4,
                             TRUE ~ NA),
           pred   = colnames(d)[max.col(d,ties.method="first")], 
           pred   = str_remove(pred,"P\\(Y = "), 
           pred   = str_remove(pred,"\\)"),
           pred= case_when(pred == "A"  ~ 1,
                             pred == "Sc" ~ 2,
                             pred == "T"  ~ 3,
                             pred == "B" ~ 4,
                             TRUE ~ NA)) %>% 
    as_tibble()  %>% 
    mutate(actual_n = as.numeric(as.character(actual)),
           pred_n = as.numeric(as.character(pred)),
           dif = abs(actual_n - pred_n)) %>%
    select(actual, pred, dif) %>%
    mutate(var = case_when(
      # lm no missing
      colnames(model[[2]][3]) == "log_Mass" ~  colnames(model[[2]][2]),
      # gm no missing
      colnames(model[[2]][3]) == "gm" ~ colnames(model[[2]][2]),
      # lm missing
      colnames(model[[2]][2]) == "gm" ~ colnames(model[[2]][5]),
      # gm missing
      TRUE ~ colnames({{model}}[[2]][5])),
      species = model[[2]]$Genus_species)
}
  
ord_pred_phy <- function(df){
  map(df, ~ord_pred(.x)) %>% bind_rows()
}

ord_pred2 <- function(model){
set.seed(124)
  d <-  predict({{model}}, summary = T, probs = c(0.055, 0.945),  resp = 'LocOrd2',
                re_formula = NA,)
  d2 <- as.data.frame(d) %>% 
    mutate(actual = as.factor({{model}}[[2]][[1]]),
           actual= case_when(actual == "A"  ~ 1,
                             actual == "Sc" ~ 2,
                             actual == "T"  ~ 3,
                             actual == "B" ~ 4,
                             TRUE ~ NA),
           pred   = colnames(d)[max.col(d,ties.method="first")], 
           pred   = str_remove(pred,"P\\(Y = "), 
           pred   = str_remove(pred,"\\)"),
           pred= case_when(pred == "A"  ~ 1,
                             pred == "Sc" ~ 2,
                             pred == "T"  ~ 3,
                             pred == "B" ~ 4,
                             TRUE ~ NA)) %>% 
    as_tibble()  %>% 
    mutate(actual_n = as.numeric(as.character(actual)),
           pred_n = as.numeric(as.character(pred)),
           dif = abs(actual_n - pred_n)) %>%
    select(actual, pred, dif) %>% 
    mutate(var = case_when(
      # lm no missing
      colnames(model[[2]][3]) == "log_Mass" ~  colnames(model[[2]][2]),
      # gm no missing
      colnames(model[[2]][3]) == "gm" ~ colnames(model[[2]][2]),
      # lm missing
      colnames(model[[2]][2]) == "gm" ~ colnames(model[[2]][5]),
      # gm missing
      TRUE ~ colnames({{model}}[[2]][5])),
      species = model[[2]]$Genus_species)
}
  
ord_pred_nophy <- function(df){
  map(df, ~ord_pred2(.x)) %>% bind_rows()
}
```





```{r}
pred1 <- map(1, ~ord_pred_phy(list_o2i)) %>% 
  bind_rows() %>% 
  mutate(method = 'phy_int',
         mass = 'log_mass')

pred2 <- map(1, ~ord_pred_nophy(list_o2i)) %>% 
  bind_rows() %>% 
  mutate(method = 'no_phy_int',
         mass = 'log_mass')

pred3 <- map(1, ~ord_pred_phy(list_o2gi)) %>% 
  bind_rows() %>% 
  mutate(method = 'phy_int',
         mass = 'geo_mean')

pred4 <- map(1, ~ord_pred_nophy(list_o2gi)) %>% 
  bind_rows() %>% 
  mutate(method = 'no_phy_int',
         mass = 'geo_mean')


preds <- bind_rows(pred1, pred2, 
                   pred3, pred4) %>%  #, pred5, pred6) %>% 
  write_csv(here("Data", "extant_ord_predictions.csv"))
preds <- read_csv(here("Data", "extant_ord_predictions.csv"))
```



```{r}
accuracy <- preds %>% 
  group_by(method, var, mass) %>%  
  filter(method == "phy_int") %>% 
  summarise(accuracy = round((sum(dif == 0)/429) * 100, 
                             digits = 1),
            within1 = round((sum(dif <= 1)/429) * 100, digits = 1)) %>% 
  select(var, accuracy, within1, method, mass) %>% 
  arrange(desc(within1)) %>% view()

accuracy %>%
  kbl() %>%
  kable_classic_2(full_width = F)

accuracy %>% write_csv(here("Data", "Accuracy_Ord.csv"))
```

### Big difference preds

```{r}
preds %>% filter(dif ==1) %>% group_by(var) %>% count() %>% arrange(desc(n)) 
preds %>% filter(dif ==2) %>% group_by(var) %>% count() %>% arrange(desc(n)) 
preds %>% filter(dif ==3) %>% group_by(var) %>% count() %>% arrange(desc(n)) 
```


Which species go from scansorial to arboreal, and terrestrial to scansorial, and terrestrial to is?
More than anything, species have the highest probability of being Terrestrial.
```{r}
preds %>% filter(actual == 1 & pred == 2) %>% count(name = "1to2")

preds %>% filter(actual == 1 & pred == 3) %>% count(name = "1to3")

preds %>% filter(actual == 1 & pred == 4) %>% count(name = "1to4")

preds %>% filter(actual == 2 & pred == 1) %>% count(name = "2to1")

preds %>% filter(actual == 2 & pred == 3) %>% count(name = "2to3")

preds %>% filter(actual == 2 & pred == 4) %>% count(name = "2to4")

preds %>% filter(actual == 3 & pred == 1) %>% count(name = "3to1")

preds %>% filter(actual == 3 & pred == 2) %>% count(name = "3to2")

preds %>% filter(actual == 3 & pred == 4) %>% count(name = "3to4")

preds %>% filter(actual == 4 & pred == 1) %>% count(name = "4to1")

preds %>% filter(actual == 4 & pred == 2) %>% count(name = "4to2")

preds %>% filter(actual == 4 & pred == 3) %>% count(name = "4to3")
```

