---
title: "Binary Models"
output: html_notebook
---

# Final Version of Ordinal Models Script

Predicting ordinal climbing ranks (Arboreal, Scansorial, Terrestrial, and Inter-Substrate) using postcranial measurements. Models also incorporate intraspecific variation and phylogenetic variation.

Ordinal Models warrant some prior testing for the prior on the thresholds. student_t(5, 0, 0.6) makes the most sense.

After extensive trials, we have decided on:
  - log-shape ratio models will not include a size covariate
  - functional index models will not include a size covariate. Why? Testing showed that it didn't affect effect sizes or predictions. Go into detail(s) in Sup if needed. 
  - Linear measurements will include size, both gm and log-mass (because log-mass is needed for fossil predictions unless we want to do some big missing data models?)

## Preparation  

#### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

source(here("Code","Name_Change.R"))
```

#### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  drop_na(Loc_Ord2) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family)) %>% 
  mutate(Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")))

#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

# Organizing complete measurements and those with missing values.
# they require different models
var_complete <-  read_rds(here("Data", "var_complete.Rds"))
var_missing <-  read_rds(here("Data", "var_missing.Rds"))
var_complete_linear <-  read_rds(here("Data", "var_complete_linear.Rds"))
var_missing_linear <-  read_rds(here("Data", "var_missing_linear.Rds"))
var_complete_ratio <-  read_rds(here("Data", "var_complete_ratio.Rds"))
var_missing_ratio <-  read_rds(here("Data", "var_missing_ratio.Rds"))
```

#### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

# Fit Models

## Linear Measurements

### Log-Mass Complete

#### Prelim model  
```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
# prior

p1 = c(prior(student_t(5, 0, 0.6), class = Intercept),
       prior(normal(0, 2), class = b),
       prior(normal(0, 0.3), class = sd))

#initial fit
mm <- brm(Loc_Ord2 ~ Sl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_o_lm <- vector(mode ="list")

for(i in var_complete_linear){
  list_o_lm[[i]]<- update(mm,
                         formula=(paste0("Loc_Ord2 ~", i, "+log_Mass+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


### Log-Mass Missing

Update cannot be used with multivatiate models. Prior must be called in the loop


#### Run Loop

```{r message = FALSE, warning=FALSE, results = 'hide'}

for(i in var_missing_linear){
  ord_mod <-  bf(paste0("Loc_Ord2 ~ mi(", i, ")+log_Mass+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + cumulative()
  imp_mod <- bf(paste0(i,"| mi() ~ log_Mass + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- ord_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "student_t(5, 0, 0.6)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_o_lm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}
```

#### Save Models
```{r}
list_o_lm %>% write_rds(here("Data","O_lm_mods_mis.Rds"))


```

### Geo-Mean Complete

#### Prior 
same prior as above

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
# Prior
p1 = c(prior(student_t(5, 0, 0.6), class = Intercept),
       prior(normal(0, 2), class = b),
       prior(normal(0, 0.3), class = sd))

#initial fit
mm <- brm(Loc_Ord2 ~ Sl + gm + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_o_gm <- vector(mode ="list")

for(i in var_complete_linear){
  list_o_gm[[i]]<- update(mm, formula=(paste0("Loc_Ord2 ~", i, "+gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


### Geo-Mean Missing

Update cannot be used with multivariate models. Prior must be called in the loop

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing_linear){
  ord_mod <-  bf(paste0("Loc_Ord2 ~ mi(", i, ")+gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + cumulative()
  imp_mod <- bf(paste0(i,"| mi() ~ gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- ord_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "student_t(5, 0, 0.6)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_o_gm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

```

#### Save Models

```{r}
list_o_gm %>% write_rds(here("Data","O_gm_mods_mis.Rds"))
```



## Ratios

### Ratios Complete

#### Prelim model  
```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
# prior

p1 = c(prior(student_t(5, 0, 0.6), class = Intercept),
       prior(normal(0, 2), class = b),
       prior(normal(0, 0.3), class = sd))

#initial fit
mm <- brm(Loc_Ord2 ~ SI + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_o_ratio <- vector(mode ="list")

for(i in var_complete_ratio){
  list_o_ratio[[i]]<- update(mm, 
                             formula=(paste0("Loc_Ord2 ~", i, "+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


### Ratio Missing

Update cannot be used with multivatiate models. Prior must be called in the loop


#### Run Loop

```{r message = FALSE, warning=FALSE, results = 'hide'}

for(i in var_missing_ratio){
  bin_mod <-  bf(paste0("Loc_Ord2 ~ mi(", i, ")+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + cumulative()
  imp_mod <- bf(paste0(i,"| mi() ~ log_Mass + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "student_t(5, 0, 0.6)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_o_ratio[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}
```

#### Save Models

```{r}
list_o_ratio %>% write_rds(here("Data","O_ratio_mods_mis.Rds"))
```

