---
title: "Predicting Ordinal Climbing"
#output: html_notebook
---

# Predicting climbing from fossil data:

Take model lists, then use them one by one to predict climbing in the fossil taxa. Then run predictions using the "combined" models (with multiple predictors) and add these to the individual measurement predictions.


```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, brms, cmdstanr, here, tidybayes, patchwork, glue, ggthemes, furrr)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
nms <- read_rds(here("Data", "Order_Names.Rds"))


```

### Load Data

```{r}
dat <- read_csv(here("Data", "Extant_Master.csv"))

fdat <- read_csv(here("Data", "Fossil_Master.csv")) %>% 
  group_by(Genus_species) %>%  
   summarise_if(is.numeric, mean, na.rm = T)

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

#variables to do fossil predictions with
pred_vars <- fdat_cln[c(8:78)]

```

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements.

```{r}
list_o_lm1 <- read_rds(here("Data","O_lm_mods_mis.Rds"))
list_o_lm2 <- read_rds(here("Data","O_ratio_mods_mis.Rds"))
#purrr keep_at is great!
list_o2 <- append(list_o_lm1, list_o_lm2)  %>% keep_at(pred_vars)

names(list_o2)

rm(list_o_lm1, list_o_lm2)
```

Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model

# Predictions

## Data & Lists
```{r}
# Taxon Lists
extant_climb <- c("Caluromys_derbianus", "Tamiasciurus_douglasii","Tupaia_glis", "Cynocephalus_volans", "Glaucomys_sabrinus")

extant_ground <- c("Solenodon_paradoxus", "Atelerix_albiventris",     "Sorex_trowbridgii", "Thomomys_bottae", "Monodelphis_domestica")

old <- c("Eomaia_scansoria", "Sinodelphys_szalayi", "Juramaia_sinensis", "Cokotherium_jiufotangensis", "Ambolestes_zhoui")

multi <- c("Rugosodon_eurasiaticus", "Jeholbaatar_kielanae", "Filikomys_primaevus", "Ptilodus_kummae", "Kryptobaatar_dashzevegi")

primate <- c("Plesiadapis_cookei", "Torrejonia_wilsoni", "Ignacius_clarkforkensis", "Dryomomys_szalayi")

## Binary important vars
var_acc = c("PES2", "HPI", "PES", "MANUS", "Ppl",  "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul")

# Fossil Data

# Extant Data

model_dat <- dat %>% filter(Genus_species %in% c(extant_climb, extant_ground))

model_dat_avg <- model_dat %>% 
  group_by(Genus_species, Loc_Ord2, Taxon_Upham_style) %>%
  summarise(across(gm:lsCl, \(x) mean(x, na.rm = TRUE))) %>% 
  ungroup()
#make into list of 45 dataframes

model_dat <- lapply(1:43, function(x) model_dat)
model_dat_avg <-  lapply(1:43, function(x) model_dat_avg)

# Columns to select
sel_cols <- c('Genus_species', 'Specimen_Num', '.draw', '.category', 'Prob_of_Climbing')

sel_cols <- lapply(1:43, function(x) sel_cols)

sel_cols_a <- c('Genus_species','.draw', '.category', 'Prob_of_Climbing')
sel_cols_a <- lapply(1:43, function(x) sel_cols_a)

```


##Functions

```{r}
# FOSSIL
nnn <- function(mod, nm){
 d <-  {{mod}} %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
  select(Genus_species, .draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
 
 d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

# Full Predictions
nnn2 <- function(mod, nm, dat, columns){
  d <- {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    #select(Genus_species, Specimen_Num, .draw, .category, Prob_of_Climbing) %>%
    select({{columns}}) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
   d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

# Fossil Predictions

nnn3 <- function(mod, nm, dat, columns){
 d <- {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    #select(Genus_species, Specimen_Num, .draw, .category, Prob_of_Climbing) %>%
    select({{columns}}) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
  d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

```

## Predict

Decided to do the predictions on the averages. I can't average over the ordinal predictors easily. The non-averaged code is hashed out below. 

```{r}
nm <- names(list_o2)

furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 6)


pred_df <- future_map2(list_o2, nm, ~nnn(.x, .y)) %>% bind_rows()  %>% 
  #write_csv(here("Data", "Fossil_Ord_Int_Predictions.csv")) %>% 
  mutate(method = "Fossil",
         substrate = NA)


#pred_df_ext_full <- future_pmap(list(list_o2, nm, model_dat_avg, sel_cols), 
#                             ~nnn2(..1, ..2, ..3, ..4)) %>% 
#  bind_rows() %>% 
#  mutate(method = "Full",
#         substrate = case_when(
#    Genus_species %in% extant_climb ~ "Climb",
#    TRUE ~ "Ground"
#  ))


pred_df_ext_full_avg <- future_pmap(list(list_o2, nm, model_dat_avg, sel_cols_a), 
                             ~nnn2(..1, ..2, ..3, ..4)) %>% 
  bind_rows() %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


#pred_df_ext_fos <- future_pmap(list(list_o2, nm, model_dat, sel_cols), 
#                             ~nnn3(..1, ..2, ..3, ..4)) %>% 
#  bind_rows() %>% 
#  mutate(method = "Fossil",
#         substrate = case_when(
#    Genus_species %in% extant_climb ~ "Climb",
#    TRUE ~ "Ground"
#  ))


pred_df_ext_fos_avg <- future_pmap(list(list_o2, nm, model_dat_avg, sel_cols_a), 
                             ~nnn3(..1, ..2, ..3, ..4)) %>% 
  bind_rows() %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


plan(sequential)

#pred_all <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_df) %>% filter(var %in% var_acc) %>% 
  #write_csv(here("Data", "Ordinal_Preds.csv")) 

pred_all_avg <- bind_rows(pred_df_ext_full_avg, pred_df_ext_fos_avg, pred_df) %>% filter(var %in% var_acc) %>% 
  write_csv(here("Data", "Ordinal_Preds.csv")) 

rm(#pred_df_ext_full, pred_df_ext_fos, 
   pred_df, pred_df_ext_full_avg, pred_df_ext_fos_avg)

#pred_all <- read_csv(here("Data", "All_Ord_Int_Predictions.csv"))
```


# Combined Predictions

```{r}
list_o2m <- read_rds(here("Data", "O_lm_mods_multi.Rds"))

model_dat <- dat %>% filter(Genus_species %in% c(extant_climb, extant_ground))  %>%  group_by(Genus_species, Taxon_Upham_style) %>%  summarise_if(is.numeric, mean, na.rm = T)

var_acc = c("PES2", "HPI", "PES", "MANUS", "Ppl",  "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul", "combined")
```

## Extant

```{r}
## Full Predictions

d <- list_o2m$mod1 %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    #select(Genus_species, Specimen_Num, .draw, .category, Prob_of_Climbing) %>%
    select('Genus_species',  '.draw', '.category', 'Prob_of_Climbing') %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
pred_df_ext_full <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  ) %>% mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))

d <- list_o2m$mod1 %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    #select(Genus_species, Specimen_Num, .draw, .category, Prob_of_Climbing) %>%
    select('Genus_species', '.draw', '.category', 'Prob_of_Climbing') %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
pred_df_ext_fos <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id') %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))

```


## Extinct

```{r}
pred_ext <- function(mod, dat){
 d <-  {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
  select(Genus_species,.draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
 
 d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

df1 <- pred_ext(list_o2m$mod1, fdat %>% filter(Genus_species %in% c('Jeholbaatar_kielanae', 'Plesiadapis_cookei')))

df2 <- pred_ext(list_o2m$mod2, fdat %>% filter(Genus_species %in% c('Eomaia_scansoria', 'Sinodelphys_szalayi')))

df3 <- pred_ext( list_o2m$mod3, fdat %>% filter(Genus_species %in% c('Ambolestes_zhoui')))

df4 <- pred_ext(list_o2m$mod4, fdat %>% filter(Genus_species %in% c('Rugosodon_eurasiaticus')))

df5 <- pred_ext(list_o2m$mod5, fdat %>% filter(Genus_species %in% c('Ignacius_clarkforkensis')))

df6 <- pred_ext(list_o2m$mod6, fdat %>% filter(Genus_species %in% c('Dryomomys_szalayi')))

df7 <- pred_ext(list_o2m$mod7, fdat %>% filter(Genus_species %in% c('Kryptobaatar_dashzevegi'))) #%>% 
#                  select(-Specimen_Num) %>% 
#                  mutate(Specimen_Num = "mean_values") %>%
#                  group_by(Genus_species, Specimen_Num) %>% 
#                  summarise_at(14:93, mean, na.rm = T))
#
df8 <- pred_ext(list_o2m$mod8, fdat %>% filter(Genus_species %in% c('Juramaia_sinensis', 'Cokotherium_jiufotangensis')))

df9 <- pred_ext(list_o2m$mod9, fdat %>% filter(Genus_species %in% c('Filikomys_primaevus')))

df10 <- pred_ext(list_o2m$mod10, fdat %>% filter(Genus_species %in% c('Ptilodus_kummae')))

df11 <- pred_ext(list_o2m$mod11, fdat %>% filter(Genus_species %in% c('Torrejonia_wilsoni')))

pred_fos <- bind_rows(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11) %>% mutate(var = 'combined')

rm(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11)
```


```{r}

pred_all2 <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_fos) %>% #filter(var %in% var_acc) %>% 
  mutate(draw = rep(1:4000, times = nrow(.)/4000)) %>% 
  #THIS IS AVERAGING PER SPECIES
  #group_by(substrate, method, Genus_species, draw) %>% 
  #summarize(Prob_of_Climbing = mean(Prob_of_Climbing, na.rm = TRUE)) %>% ungroup() 
  mutate(var = "combined") %>% select(!draw) %>% mutate(.draw = as.numeric(.draw),
                                                        id = as.numeric(id))
  #write_csv(here("Data", "Ord_Multiple_Predictions.csv"))

pred_all <- read_csv(here("Data", "Ordinal_Preds.csv")) %>% bind_rows(pred_all2) %>% write_csv(here("Data", "Ordinal_Preds.csv"))

rm(pred_all_avg, pred_all2, pred_df_ext_fos, pred_df_ext_full, pred_fos)

```

# Plots

## Percent Barplots

```{r}
pred_all <- read_csv(here("Data", "Ordinal_Preds.csv"))


d2 <- c('#a6761d','#d95f02','#7570b3','#1b9e77')
d3 <- c('#5e1ea6', '#0d57ff',  '#31c1bb', '#66a61e')

d4 <- c(P4 = '#770194', P3 = '#1981db', P2 = "#2abb9c", P1 = '#79bc23')

pred_all %>%  
  unite("specimen", Genus_species,  sep = " ") %>% 
  filter(method == "Full",
         var == "MANUS") %>% 
  group_by(specimen) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =specimen , x = n, fill = max_rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  labs(y = "") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom'
         ) 
  
```

# Extant Plots

### Full

```{r}

d4 <- c('Inter-Substrate' = '#770194', 'Terrestrial' = '#1981db', 'Scansorial' = "#2abb9c", 'Arboreal' = '#79bc23')

p1 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Full",
         var %in% var_acc,
         Genus_species %in% extant_climb) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p2 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Full",
         var %in% var_acc,
         Genus_species %in% extant_ground) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p1+p2 + plot_annotation(title = "Extant Predicitons With Phylogenetic Information") + plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Predict_Ord_Extant_Full.pdf"), width = 8.5, height = 12)
ggsave(here("Plots", "Predict_Ord_Extant_Full.jpg"), width = 8.5, height = 12)  
```

### Fossil

```{r}

p1 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% extant_climb) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p2 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% extant_ground) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p1+p2 + plot_annotation(title = "Extant Predicitons Without Phylogenetic Information") + plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Predict_Ord_Extant_Fossil.pdf"), width = 8.5, height = 12)
ggsave(here("Plots", "Predict_Ord_Extant_Fossil.jpg"), width = 8.5, height = 12)
```


#### Switched Order

```{r}

p1 <- pred_all %>% 
   
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% extant_climb) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  mutate(var = recode(var, combined = "Multiple\nRegression")) %>%
  mutate(Genus_species = gsub("_", " ", Genus_species)) %>% 
  ggplot(aes(y =fct_relevel(var,var_acc) , 
             x = n, 
             fill = rank)) + 
  geom_bar(position = "fill", 
           stat = 'identity', 
           alpha = 0.8) +
  #scale_fill_manual(values = rev(d4)) + 
  #scale_fill_viridis_d(begin = 0.9, end = 0) +
  scale_fill_grey(start = 0.8, end = 0) +
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank(),
         strip.text = element_text(face = "italic")
         ) + 
  scale_y_discrete(limits=rev) +
  facet_wrap(~Genus_species, ncol = 5)

p2 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% extant_ground) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  mutate(var = recode(var, combined = "Multiple\nRegression"))  %>%
   mutate(Genus_species = gsub("_", " ", Genus_species)) %>% 
  ggplot(aes(y = fct_relevel(var,var_acc) , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  #scale_fill_manual(values = rev(d4)) + 
  #scale_fill_viridis_d(begin = 0.9, end = 0) +
    scale_fill_grey(start = 0.8, end = 0) +
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom',
         strip.background = element_blank(),
         strip.text = element_text(face = "italic")
         ) + 
  scale_y_discrete(limits=rev) +
  facet_wrap(~Genus_species, ncol = 5)

p1/p2 + #plot_annotation(title = "Predicitons for species with known locomotor rankings without phylogenetic information", 
                        #subtitle = "Top row are arboreal except for scansorial Tupaia\nBottom row are inter-substrate except for terrestrial hedgehog & opossum" ) + 
  plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Ord_Pred_Extant2.pdf"), width = 11, height = 8)
ggsave(here("Plots", "Ord_Pred_Extant2.jpg"), width = 11, height = 8)
```



# Fossil Plots


```{r}
p1 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(#method == "Fossil",
         var %in% var_acc,
         Genus_species %in% old) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  mutate(var = recode(var, combined = "Multiple\nRegression"))  %>%
  mutate(Genus_species = gsub("_", " ", Genus_species)) %>% 
  ggplot(aes(y = fct_relevel(var,var_acc) , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  #scale_fill_manual(values = rev(d4)) + 
  #scale_fill_viridis_d(begin = 0.9, end = 0) +
    scale_fill_grey(start = 0.8, end = 0) +
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom',
         strip.background = element_blank(),
         strip.text = element_text(face = "italic")
         ) + 
  scale_y_discrete(limits=rev) +
  facet_wrap(~Genus_species, ncol = 5)

p2 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(#method == "Fossil",
         var %in% var_acc,
         Genus_species %in% multi) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  mutate(var = recode(var, combined = "Multiple\nRegression")) %>%
  mutate(Genus_species = gsub("_", " ", Genus_species)) %>% 
  ggplot(aes(y =fct_relevel(var,var_acc) , 
             x = n, 
             fill = rank)) + 
  geom_bar(position = "fill", 
           stat = 'identity', 
           alpha = 0.8) +
  #scale_fill_manual(values = rev(d4)) + 
  #scale_fill_viridis_d(begin = 0.9, end = 0) +
  scale_fill_grey(start = 0.8, end = 0) +
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank(),
         strip.text = element_text(face = "italic")
         ) + 
  scale_y_discrete(limits=rev) +
  facet_wrap(~Genus_species, ncol = 5)

p3 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(#method == "Fossil",
         var %in% var_acc,
         Genus_species %in% primate) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  mutate(var = recode(var, combined = "Multiple\nRegression")) %>%
  mutate(Genus_species = gsub("_", " ", Genus_species)) %>% 
  ggplot(aes(y =fct_relevel(var,var_acc) , 
             x = n, 
             fill = rank)) + 
  geom_bar(position = "fill", 
           stat = 'identity', 
           alpha = 0.8) +
  #scale_fill_manual(values = rev(d4)) + 
  #scale_fill_viridis_d(begin = 0.9, end = 0) +
  scale_fill_grey(start = 0.8, end = 0) +
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank(),
         strip.text = element_text(face = "italic")
         ) + 
  scale_y_discrete(limits=rev) +
  facet_wrap(~Genus_species, ncol = 5)

p1/p2 / p3 + plot_annotation(title = "Fossil Predicitons from Ranked-Ordinal Models") + plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Ord_Pred_Fossil.pdf"), width = 10, height = 10)
ggsave(here("Plots", "Ord_Pred_Fossil.jpg"), width = 10, height = 10) 
```

