---
title: "Predicting Ordinal Interaction Climbing"
output: html_notebook
---

# Predicting climbing from fossil data:

Take model lists, then use them one by one to predict climbing in the fossil taxa.

```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, brms, cmdstanr, here, tidybayes, patchwork, glue, ggthemes, furrr)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
nms <- read_rds(here("Data", "Order_Names.Rds"))

source(here("Code","Name_Change.R"))


```

### Load Data

```{r}
dat <- read_csv(here("Data", "Extant_Master.csv"))

fdat <- read_csv(here("Data", "Fossil_Master.csv"))

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

#variables to do fossil predictions with
pred_vars <- fdat_cln[c(9:84)]

#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

```

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements.

```{r}
list_o_lm <- read_rds(here("Data","O_lm_int_mods_mis.Rds"))
#purrr keep_at is great!
list_o2 <- list_o_lm %>% keep_at(pred_vars)

names(list_o2)

rm(list_o_lm)
```

Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model

# Predictions

## Data & Lists
```{r}
# Taxon Lists
extant_climb <- c("Caluromys_derbianus", "Tamiasciurus_douglasii","Tupaia_glis", "Cynocephalus_volans", "Glaucomys_sabrinus")

extant_ground <- c("Solenodon_paradoxus", "Atelerix_albiventris",     "Sorex_trowbridgii", "Thomomys_bottae", "Monodelphis_domestica")

old <- c("Eomaia_scansoria", "Sinodelphys_szalayi", "Juramaia_sinensis", "Cokotherium_jiufotangensis", "Ambolestes_zhoui")

multi <- c("Rugosodon_eurasiaticus", "Jeholbaatar_kielanae", "Filikomys_primaevus", "Ptilodus_kummae", "Kryptobaatar_dashzevegi")

primate <- c("Plesiadapis_cookei", "Torrejonia_wilsoni", "Ignacius_clarkforkensis", "Dryomomys_szalayi")

## Binary important vars
var_acc = c("PES2", "HPI", "PES", "MANUS", "Ppl",  "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul")

# Fossil Data
colz <- c("Genus_species", "log_Mass", names(list_o2), "Specimen_Num")

fd <- fdat %>% select(all_of(colz))

# Extant Data

model_dat <- dat %>% filter(Genus_species %in% c(extant_climb, extant_ground))

model_dat_avg <- model_dat %>% 
  group_by(Genus_species, Loc_Ord2, Taxon_Upham_style) %>%
  summarise(across(gm:lsCl, \(x) mean(x, na.rm = TRUE))) %>% 
  ungroup()
#make into list of 45 dataframes

model_dat <- lapply(1:45, function(x) model_dat)
model_dat_avg <-  lapply(1:45, function(x) model_dat_avg)

# Columns to select
sel_cols <- c('Genus_species', 'Specimen_Num', '.draw', '.category', 'Prob_of_Climbing')

sel_cols <- lapply(1:45, function(x) sel_cols)

sel_cols_a <- c('Genus_species','.draw', '.category', 'Prob_of_Climbing')
sel_cols_a <- lapply(1:45, function(x) sel_cols_a)

```


##Functions

```{r}
# FOSSIL
nnn <- function(mod, nm){
 d <-  {{mod}} %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
  select(Genus_species, Specimen_Num,.draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
 
 d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

# Full Predictions
nnn2 <- function(mod, nm, dat, columns){
  d <- {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    #select(Genus_species, Specimen_Num, .draw, .category, Prob_of_Climbing) %>%
    select({{columns}}) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
   d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

# Fossil Predictions

nnn3 <- function(mod, nm, dat, columns){
 d <- {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    #select(Genus_species, Specimen_Num, .draw, .category, Prob_of_Climbing) %>%
    select({{columns}}) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
  d2 <- d %>% rownames_to_column('id') %>%
  left_join(
    d %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}

```

### Plot helpers

```{r}
var_acc = c("PES2", "HPI", "PES", "MANUS", "Ppl",  "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul")
```

########## 

## DEAL WTIH "CLIMB" & "GROUND" categories

## MULTIPLE SAMPLES PER SPECIES - one T glis is quite different from the other.

## TRYING TO INCLUDE SPECIMEN NUMBERS - works!!

############ 

modes() is really slow, but whatevs

```{r}
nm <- names(list_o2)

furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 6)

tictoc::tic()
pred_df <- future_map2(list_o2, nm, ~nnn(.x, .y)) %>% bind_rows()  %>% 
  write_csv(here("Data", "Fossil_Ord_Int_Predictions.csv")) %>% 
  mutate(method = "Fossil",
         substrate = NA)

tictoc::toc()

pred_df_ext_full <- future_pmap(list(list_o2, nm, model_dat, sel_cols), 
                             ~nnn2(..1, ..2, ..3, ..4)) %>% 
  bind_rows() %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


pred_df_ext_full_avg <- future_pmap(list(list_o2, nm, model_dat_avg, sel_cols_a), 
                             ~nnn2(..1, ..2, ..3, ..4)) %>% 
  bind_rows() %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


pred_df_ext_fos <- future_pmap(list(list_o2, nm, model_dat, sel_cols), 
                             ~nnn3(..1, ..2, ..3, ..4)) %>% 
  bind_rows() %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))

tictoc::toc()

tictoc::tic()

pred_df_ext_fos_avg <- future_pmap(list(list_o2, nm, model_dat_avg, sel_cols_a), 
                             ~nnn3(..1, ..2, ..3, ..4)) %>% 
  bind_rows() %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


plan(sequential)

pred_all <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_df) %>% filter(var %in% var_acc) %>% 
  write_csv(here("Data", "All_Ord_Int_Predictions.csv")) 

pred_all_avg <- bind_rows(pred_df_ext_full_avg, pred_df_ext_fos_avg) %>% filter(var %in% var_acc) %>% 
  write_csv(here("Data", "All_Ord_Int_Avg_Predictions.csv")) 

rm(pred_df_ext_full, pred_df_ext_fos, pred_df, pred_df_ext_full_avg, pred_df_ext_fos_avg)

pred_all <- read_csv(here("Data", "All_Ord_Int_Predictions.csv"))
```

## Percent Barplots

```{r}
d2 <- c('#a6761d','#d95f02','#7570b3','#1b9e77')
d3 <- c('#5e1ea6', '#0d57ff',  '#31c1bb', '#66a61e')

d4 <- c(P4 = '#770194', P3 = '#1981db', P2 = "#2abb9c", P1 = '#79bc23')

pred_all %>%  
  unite("specimen", Genus_species, Specimen_Num, sep = " ") %>% 
  filter(method == "Full",
         var == "Ul") %>% 
  group_by(specimen) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =specimen , x = n, fill = max_rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  labs(y = "") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom'
         ) 
  
```

# Extant Plots

### Full

```{r}

d4 <- c('Inter-Substrate' = '#770194', 'Terrestrial' = '#1981db', 'Scansorial' = "#2abb9c", 'Arboreal' = '#79bc23')

p1 <- pred_all_avg %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Full",
         var %in% var_acc,
         Genus_species %in% extant_climb) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p2 <- pred_all_avg %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Full",
         var %in% var_acc,
         Genus_species %in% extant_ground) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p1+p2 + plot_annotation(title = "Extant Predicitons With Phylogenetic Information") + plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Predict_Ord_Extant_Full.pdf"), width = 8.5, height = 12)
  
```

### Fossil

```{r}

p1 <- pred_all_avg %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% extant_climb) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p2 <- pred_all_avg %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% extant_ground) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='bottom',
         strip.background = element_blank()
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p1+p2 + plot_annotation(title = "Extant Predicitons Without Phylogenetic Information") + plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Predict_Ord_Extant_Fossil.pdf"), width = 8.5, height = 12)
  
```

# Fossil Plots


```{r}
p1 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% old) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x="Proportion of Estimates") +
  theme_classic() +
    coord_cartesian(xlim = c(0,1),
                  expand = FALSE)+
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank(),
         panel.background = element_rect(fill = 'grey85')
         ) + 
  facet_wrap(~fct_relevel(var,rev(c("PES2", "HPI",  "MANUS", "PES",  "Hl", "Ppl",  "Pipl", "OLI", "Rl", "MANUS2",  "Uol", "Ipl",  "Ul", "Fl"))), ncol = 2, as.table = F)

p2 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% multi) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
      coord_cartesian(xlim = c(0,1),
                  expand = FALSE)+
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank(),
         panel.background = element_rect(fill = 'grey85')
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p3 <- pred_all %>% 
   mutate(rank= case_when(max_rank == "P1"  ~ "Arboreal",
                          max_rank == "P2"  ~ "Scansorial",
                          max_rank == "P3"  ~ "Terrestrial",
                          max_rank == "P4"  ~ "Inter-Substrate"),
          rank = fct_relevel(rank, 
                             c("Arboreal", 
                               "Scansorial", 
                               "Terrestrial", 
                               "Inter-Substrate"))) %>%
  filter(method == "Fossil",
         var %in% var_acc,
         Genus_species %in% primate) %>% 
  group_by(var, Genus_species, rank) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y =Genus_species , x = n, fill = rank)) + 
  geom_bar(position = "fill", stat = 'identity', alpha = 0.8) +
  scale_fill_manual(values = rev(d4)) + 
  scale_x_continuous(breaks = c(0,0.5, 1), label = ~ scales::comma(.x, accuracy = c(1, 0.1, 1))) +
  labs(y = "", x = "Proportion of Estimates") +
  theme_classic() +
      coord_cartesian(xlim = c(0,1),
                  expand = FALSE)+
  theme( panel.border = element_blank(),
         axis.line = element_line(colour = "NA"),
         axis.ticks = element_line(linewidth = rel(0.25)),
         legend.position='none',
         strip.background = element_blank(),
         panel.background = element_rect(fill = 'grey85')
         ) + 
  facet_wrap(~fct_relevel(var,var_acc),  ncol = 2)

p1+p2 + p3 + plot_annotation(title = "Fossil Predicitons") + plot_layout(guides = "collect") &
  theme(legend.position='bottom')

ggsave(here("Plots", "Predict_Ord_Fossil.pdf"), width = 12.7, height = 12)
  
```



# Whole Shebang

### function

```{r}
# shading
shades <- data.frame(xmin=seq(1.5,13-1.5, 2),
                     xmax=seq(2.5,13+.5, 2),
                     ymin=0, ymax=Inf)

hplot <- function(groups, method){
  pred_all %>% filter(Genus_species %in% {{groups}},
                         method == {{method}}) %>% 
    mutate(var =  as.factor(var)) %>% 
  ggplot(aes(y = Prob_of_Climbing, 
             x = fct_relevel(var,var_acc), 
             #y = var,
             color = Genus_species)) +
  geom_hline(yintercept = 0.5, linetype = 2, linewidth = 0.5) +
  stat_pointinterval(.width = c(0.5, 0.68268), 
                     #linewidth = c(0.75, 0.5), 
                     position = position_dodge(width = -.6)) + ylim(0,1) +
    labs(x = "", y = "Probability of Climbing") +
  scale_color_manual(values = pal) + theme_pander(gM = F) + 
    geom_rect(inherit.aes = F, 
              data = shades, 
              mapping = aes(xmin=xmin, 
                            xmax=xmax, 
                            ymin = ymin, 
                            ymax = ymax), 
              alpha = 0.125) +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.border = element_rect(colour = "grey40", fill=NA, size=0.7))
}

```

### big df

### Big Plot

```{r}
pl5 <- hplot(old, "Fossil") + 
  ggtitle("Mesozoic Mammal Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank(),
        panel.grid.major.y = element_blank())

pl6 <- hplot(multi, "Fossil") + 
  ggtitle("Multituberculate Predicitons") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl7 <- hplot(primate, "Fossil") + 
  ggtitle("Primate Predicitons") + 
  theme(#axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())


t3 <- pl5 / pl6 /pl7

t3

ggsave(here("Plots", "Predict_Ord_Int_Fossil.pdf"), height = 8, width = 13)

```

```{r}
pl1 <- hplot(extant_climb, "Full") + 
  ggtitle("Extant Climb Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl2 <- hplot(extant_climb, "Fossil") + 
  ggtitle("Extant Climb Fossil") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl3 <- hplot(extant_ground, "Full") + 
  ggtitle("Extant Ground Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl4 <- hplot(extant_ground, "Fossil") + 
  ggtitle("Extant Ground Fossil") + 
  theme(#axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),)


t1 <- pl1 / pl2 + plot_layout(guides = "collect")

t2 <- pl3 / pl4 + plot_layout(guides = "collect")

wrap_plots(t1, t2, ncol = 1)

ggsave(here("Plots", "Predict_Int_Extant.pdf"), height = 10, width = 13)

```

```{r}
pl2 / pl4 + plot_layout(guides = "collect")

ggsave(here("Plots", "Predict_Int_Extant2.pdf"), height = 6, width = 13)
```

```{r}
wrap_plots(t1, t2, t3, ncol = 1, heights = c(2/7, 2/7, 3/7))

ggsave(here("Plots", "Predict_Int_All.pdf"), height = 16, width = 13)
```
