---
title: "Predicting Ordinal Climbing"
output: html_notebook
---


# Predicting climbing from fossil data:

Take model lists, then use them one by one to predict climbing in the fossil taxa.
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, here, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
nms <- read_rds(here("Data", "Order_Names.Rds"))

source(here("Code","Name_Change.R"))


```

### Load Extant data  

```{r message = FALSE, warning=FALSE}
dat <- read_sheet("https://docs.google.com/spreadsheets/d/1-eknhyZ1JNnXqhg2kViyzVntC8NGZvILQX-aQQb1Jvk/edit#gid=325036460", na = c("NA", "?", "")) %>%
  select(!NOTES) %>% 
# Recode Ordinal Rankings
  mutate(Loc_Ord = case_when(Loc_mode_Ordinal == "G"  ~ "G",
                             Loc_mode_Ordinal == "A"  ~ "A",
                             Loc_mode_Ordinal == "Sc" ~ "Sc",
                             Loc_mode_Ordinal == "T"  ~ "T",
                             Loc_mode_Ordinal == "Is" ~ "Is",
                             Loc_mode_Ordinal == "Sf" ~ "Sf",
                             Loc_mode_Ordinal == "Ss" ~ "Ss",
                             TRUE ~ NA),
         Loc_Ord = as.ordered(Loc_Ord),
         Loc_Ord = fct_relevel(Loc_Ord, c("G","A","Sc","T","Is","Sf","Ss")),
         # Combining the Intersurface and Semifossorial
         Loc_Ord2 = case_when(Loc_mode_Ordinal == "G" ~ "A",
                              Loc_mode_Ordinal == "A" ~ "A",
                              Loc_mode_Ordinal == "Sc" ~ "Sc",
                              Loc_mode_Ordinal == "T" ~ "T",
                              Loc_mode_Ordinal == "Is" ~ "B",
                              Loc_mode_Ordinal == "Sf" ~ "B",
                              Loc_mode_Ordinal == "Ss" ~ "B",
                             TRUE ~ NA),
         Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")),
         Loc_bin = case_when(Loc_mode_Bindary == "Ground" ~ 0,
                             Loc_mode_Bindary == "Tree" ~ 1,
                             TRUE ~ NA
                             ),
        # Loc_bin = as.factor(Loc_bin),
         Loc_mode_Categorical = as.factor(Loc_mode_Categorical),
         log_Mass = log(Mass_grams)) %>% 
    relocate(Loc_bin, .after = Loc_mode_Bindary) %>% 
  relocate(Loc_Ord, .after = Loc_mode_Ordinal) %>% 
  relocate(Loc_Ord2, .after = Loc_Ord) %>%
  relocate(log_Mass, .before = Skl) %>% 
#################
#Calculate Indices!
#################
  mutate(SI = Sh / Sl,             # Scapular Index
         HRI = Hsw / Hl,           # Humeral Robustness Index
         HPI = Hpw / Hl,           # Humeral Proximal Index
         HEB = Hdw / Hl,           # Humeral Epicondyle Breadth
         HHRI = Hhl / Hl,          # Humeral Head Robustness Index
         HHW = Hhw / Hhl,          # Humeral Head Shape Index
         DI = Hdcw / Hsw,          # Deltopectoral Crest Index
         OLI = Uol / Ul,           # Olecranon Process Length Index
         BI = Rl / Hl,             # Brachial Index
         IM = (Hl+Ul)/(Fl+Tl),     # Intermembral Index
         PRTI = Mcl/(Hl+Rl),       # Palm Robustness Index
         MRI = Mcw / Mcl,          # Metacarpal Robustness
         MANUS = Ppl / Mcl,        # MANUS index
         MANUS2 = (Ppl+Ipl)/Mcl,   # MANUS index with intermed. phalanx
         IRI = Fgh / Fl,           # Gluteal Index
         FRI = Fsw / Fl,           # Femoral Robustness
         FEB = Fdw / Fl,           # Femoral Epicondyle Breadth
         CI = Tl / Fl,             # Crural Index
         TRI = Tmw / Tl,           # Tibial Robustness Index
         #ANR = Anl / Al,          # Astragular Neck Robustness Index
         #CAR = Cal / Cl,          # Calcaneal Robustness Index
         IRI = Il / Pel,           # Illium Robustness Index
         PR = Il / Isl,            # Pelvic Index
         PES = Pppl / Mtl,         # PES INdex
         PES2 = (Pppl+Pipl)/Mtl    # PES with intermediate Phalanx
         ) %>% 
    # geometric mean
  drop_na(Tmw, Fdw, Tl, Fl, Fsw , Sl, Hdw, Hl, Hsw, Rl, Ul, Uol) %>%
  mutate(gm = ( Tmw * Fdw * Tl * Fl * Fsw * Sl * Hdw * Hl * Hsw * Rl * Ul * Uol)^(1/12)) %>%
  relocate(gm, .before = log_Mass) %>% 
  mutate_at(vars(19:73), log) %>% 
  mutate(Fos = FALSE)

spp_obs <- dat$Taxon_Upham_style %>% unique()

pal = c( '#62361B', '#e6ab02',  '#7570b3', '#66a61e')
```

### Load Fossil Data  

```{r}
fdat <- read_sheet("https://docs.google.com/spreadsheets/d/1k19eAQP7NY9kjht8HfhcJNJ-jtYK10qlsdLi4i38tVc/edit#gid=0", na = c("NA", "?", "", "NULL")) %>% 
  # Selecting only the lines with data
  # THIS NEEDS TO BE UPDATED AS MORE DATA COME IN!!
  slice (1:9) %>% 
  select(!NOTES) %>% 
  mutate(log_Mass = log(Mass_grams)) %>% 
#################
#Calculate Indices!
#################
  mutate(SI = Sh / Sl,             # Scapular Index
         HRI = Hsw / Hl,           # Humeral Robustness Index
         HPI = Hpw / Hl,           # Humeral Proximal Index
         HEB = Hdw / Hl,           # Humeral Epicondyle Breadth
         HHRI = Hhl / Hl,          # Humeral Head Robustness Index
         HHW = Hhw / Hhl,          # Humeral Head Shape Index
         DI = Hdcw / Hsw,          # Deltopectoral Crest Index
         OLI = Uol / Ul,           # Olecranon Process Length Index
         BI = Rl / Hl,             # Brachial Index
         IM = (Hl+Ul)/(Fl+Tl),     # Intermembral Index
         PRTI = Mcl/(Hl+Rl),       # Palm Robustness Index
         MRI = Mcw / Mcl,          # Metacarpal Robustness
         MANUS = Ppl / Mcl,        # MANUS index
         MANUS2 = (Ppl+Ipl)/Mcl,   # MANUS index with intermed. phalanx
         IRI = Fgh / Fl,           # Gluteal Index
         FRI = Fsw / Fl,           # Femoral Robustness
         FEB = Fdw / Fl,           # Femoral Epicondyle Breadth
         CI = Tl / Fl,             # Crural Index
         TRI = Tmw / Tl,           # Tibial Robustness Index
         #ANR = Anl / Al,          # Astragular Neck Robustness Index
         #CAR = Cal / Cl,          # Calcaneal Robustness Index
         IRI = Il / Pel,           # Illium Robustness Index
         PR = Il / Isl,            # Pelvic Index
         PES = Pppl / Mtl,         # PES INdex
         PES2 = (Pppl+Pipl)/Mtl    # PES with intermediate Phalanx
         ) %>% 
  mutate_at(vars(14:68), log) %>% 
  mutate(Fos = TRUE)
```

### Combine, scale, and split

```{r}
dat2 <- bind_rows(dat, fdat) %>% 
  mutate_at(vars(17:95), scale2)

dat <- dat2 %>% filter(Fos == FALSE) %>% select(!Fos)

fdat <- dat2 %>% filter(Fos == TRUE) %>% select(!Fos)

rm(dat2)

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

pred_vars <- fdat_cln[c(13:79)]
```

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements. 

```{r}
list_o_lm <- read_rds(here("Data","O_lm_mods_mis.Rds"))
#purrr keep_at is great!
list_o2 <- list_o_lm %>% keep_at(pred_vars)

names(list_o2)

rm(list_o_lm)
```
Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model
# Predictions  

## Fossil Functions
```{r}
colz <- c("Genus_species", "log_Mass", names(list_o2), "Specimen_Num")

fd <- fdat %>% select(colz)

nnn <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "LocOrd2",
                    allow_new_levels = TRUE, 
                    re_formula = NA,
                    ndraws = 100) %>% 
    as.data.frame() %>% 
    select(Genus_species, .draw, .category, .epred) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, values_from = .epred) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
}

```

# Extant Functions

```{r}
model_dat <- dat %>% filter(Genus_species %in% c("Didelphis_virginiana", "Sciurus_carolinensis",  "Tupaia_glis", "Cynocephalus_volans", "Glis_glis", "Hemicentetes_semispinosus", "Atelerix_albiventris", "Tupaia_tana", "Callospermophilus_lateralis", "Monodelphis_domestica"))

nnn2 <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
    mutate(var = {{nm}})
  
}

nnn3 <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, Prob_of_Climbing, Specimen_Num) %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
}


extant_climb <- c("Didelphis_virginiana", "Sciurus_carolinensis",  "Tupaia_glis", "Cynocephalus_volans", "Glis_glis")

extant_ground <- c("Hemicentetes_semispinosus", "Atelerix_albiventris", "Tupaia_tana", "Callospermophilus_lateralis", "Monodelphis_domestica")

extant <- c("Didelphis_virginiana", "Sciurus_carolinensis",  "Tupaia_glis", "Cynocephalus_volans", "Glis_glis", "Hemicentetes_semispinosus", "Atelerix_albiventris", "Tupaia_tana", "Callospermophilus_lateralis", "Monodelphis_domestica")


old <- c("Eomaia_scansoria", "Sinodelphys_szalayi", "Juramaia_sinensis", "Cokotherium_jiufotangensis", "Ambolestes_zhoui")

new <- c("Filikomys_primaevus", "Torrejonia_wilsoni", "Ignacius_clarkforkensis", "Dryomomys_szalayi")
```



```{r}
nm <- names(list_o2)

pred_df <- map2(list_o2, nm, ~nnn(.x, .y)) %>% bind_rows() %>% 
  write_csv(here("Data", "Ord_Fossil_Predictions.csv")) %>% 
  mutate(method = "Fossil",
        substrate = NA)

pred_df %>% group_by(var, Genus_species) %>% 
   summarise(wa_rank = mean(wa_rank)) %>% 
  mutate(rounded_pred_rank = round(wa_rank, digits = 0)) 


pred_df_ext_full <- map2(list_o2, nm, ~nnn2(.x, .y)) %>% 
  bind_rows() %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))

pred_df_ext_fos <- map2(list_o2, nm, ~nnn3(.x, .y)) %>% 
  bind_rows() %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


pred_all <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_df) %>% filter(var %in% var_ord3) %>% 
  mutate(draw = rep(1:4000, times = nrow(.)/4000)) %>% 
  #THIS IS AVERAGING PER SPECIES
  group_by(substrate, method, var, Genus_species, draw) %>% 
  summarize(Prob_of_Climbing = mean(Prob_of_Climbing, na.rm = TRUE)) %>% ungroup() %>% 
  write_csv(here("Data", "Ord_All_Predictions.csv"))
```

```{r}
pred_df %>% filter(var %in% var_ord3) %>% group_by(var, Genus_species) %>% 
   summarise(wa_rank = mean(wa_rank)) %>% 
  mutate(rounded_pred_rank = round(wa_rank, digits = 0),
         rounded_pred_rank = as.factor(rounded_pred_rank),
         var = as.factor(var)) %>% 
  ggplot(aes( x = fct_relevel(var,var_ord3), y = factor(Genus_species))) + 
  geom_tile(aes(fill = fct_relevel(rounded_pred_rank, c("1", "2", "3")), width = 0.92, height = 0.92),
            color = NA,
            lwd = 1,
            linetype = 1) +
# scico::scale_fill_scico(palette = "lajolla", begin  = 0.15, end = 1,
#                         limits=c(1,4),
#                         breaks = seq(1,4, by = 0.25),
#                         labels = c( "1", "", "", "", "2", "", "", "", "3", "", "","", "4"),
                          #guide = guide_legend(byrow = TRUE, reverse=T, size = 2)
                         # ) +
  #labs(fill='Weighted\nDietary\nImportance\nScores\n') +
  theme_minimal() +
  coord_fixed(ratio=1) +
  #scale_y_discrete(limits=rev) +
  #NEW
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(angle = 45, 
                                       hjust = 1, 
                                       vjust = 1.1,  
                                       size=10),
        
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y = element_text(face = "italic", 
                                   size=12),
        axis.ticks.y=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        strip.background = element_blank(),
        panel.border = element_blank(),
        #plot.background = element_blank(),
        legend.spacing.y = unit(-1, 'mm'),
        legend.key.height = unit(1, 'mm'))
```


```{r}
pred_df %>% filter(var %in% var_ord3) %>% mutate(var = as.factor(var)) %>% 
  ggplot(aes( x = fct_relevel(var,var_ord3), y = wa_rank, color = Genus_species)) +
  geom_hline(yintercept = c(3.5, 2.5, 1.5), linetype = 2, linewidth = 0.5) +
  stat_pointinterval(.width = c(0.5, 0.68268), 
                     #linewidth = c(0.75, 0.5), 
                     position = position_dodge(width = -.6)
                     ) + ylim(1,4) +
   theme_pander() + 
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.border = element_rect(colour = "grey40", fill=NA, size=0.7) ) +
  scale_y_reverse(limits=c(4,1), expand=c(0.01,0.01))
```


## Add means to the plots?
Isn't really a good idea because there is uneven sampling across measurements
```{r}
#meandf <- pred_all %>% group_by(substrate, method, Genus_species, draw) %>% 
#  summarize(Prob_of_Climbing = mean(Prob_of_Climbing, na.rm = TRUE)) %>% 
#  ungroup() %>% 
#  mutate(var = "Mean")
#
#pred_all <- bind_rows(pred_all, meandf)
```




# Whole Shebang  

### Plot helpers
```{r}
var_ord = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Mtl", "TRI", "Ppw", "Cl", "Mcw", "MRI", "Tmw", "BI", "Pel", "Fsw", "Fdw", "Mcl", "Hdw", "Tl", "Pppl", "Hsw", "IM", "Ul", "Fl", "Rl", "MANUS2", "Hl", "Ipl", "MANUS", "Ppl", "PES", "PES2") 
#just the "sigs"
var_ord2 = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Mtl", "TRI", "Ppw", "Cl", "Mcw", "MRI", "IM", "Ul", "Fl", "Rl", "MANUS2", "Hl", "Ipl", "MANUS", "Ppl", "PES", "PES2")
# just the really important sigs
var_ord3 = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Rl", "MANUS2", "Hl", "Ipl", "MANUS", "Ppl", "PES", "PES2")
#pal = c('#66a61e', '#5e1ea6',  '#e6ab02', '#f9581c','#0d57ff')
#with the mean probability
var_ord4 = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Rl", "MANUS2", "Hl", "Ipl", "MANUS", "Ppl", "PES", "PES2", "Mean")


pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')

```


### function
```{r}
hplot <- function(groups, method){
  pred_all %>% filter(Genus_species %in% {{groups}},
                         method == {{method}}) %>% 
    mutate(var =  as.factor(var)) %>% 
  ggplot(aes(y = Prob_of_Climbing, 
             x = fct_relevel(var,var_ord3), 
             #y = var,
             color = Genus_species)) +
  geom_hline(yintercept = 0.5, linetype = 2, linewidth = 0.5) +
  stat_pointinterval(.width = c(0.5, 0.68268), 
                     #linewidth = c(0.75, 0.5), 
                     position = position_dodge(width = -.6)) + ylim(0,1) +
    labs(x = "", y = "Probability of Climbing") +
  scale_color_manual(values = pal) + theme_pander() + 
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.border = element_rect(colour = "grey40", fill=NA, size=0.7) )
}


```

###  big df



### Big Plot
```{r}
pl5 <- hplot(old, "Fossil") + 
  ggtitle("Extinct Predicitons 1") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl6 <- hplot(new, "Fossil") + 
  ggtitle("Extinct Predicitons 2") + 
  theme(#axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())


t3 <- pl5 / pl6 

t3

ggsave(here("Plots", "Predict_Fossil.pdf"), height = 6, width = 13)

```


```{r}
pl1 <- hplot(extant_climb, "Full") + 
  ggtitle("Extant Climb Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl2 <- hplot(extant_climb, "Fossil") + 
  ggtitle("Extant Climb Fossil") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl3 <- hplot(extant_ground, "Full") + 
  ggtitle("Extant Ground Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl4 <- hplot(extant_ground, "Fossil") + 
  ggtitle("Extant Ground Fossil") + 
  theme(#axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),)


t1 <- pl1 / pl2 + plot_layout(guides = "collect")

t2 <- pl3 / pl4 + plot_layout(guides = "collect")

wrap_plots(t1, t2, ncol = 1)

ggsave(here("Plots", "Predict_Extant.pdf"), height = 11, width = 13)

```

```{r}
wrap_plots(t1, t2, t3, ncol = 1)

ggsave(here("Plots", "Predict_All.pdf"), height = 16, width = 13)
```



```{r}
library(distributional)

theme_set(theme_ggdist())

# ON SAMPLE DATA
set.seed(1234)
df = data.frame(
  group = c("a", "b", "c"),
  value = rnorm(1500, mean = c(5, 7, 9), sd = c(1, 1.5, 1))
)
tt <- df %>%
  ggplot(aes(x = value, y = group)) +
  stat_pointinterval()

tt + scale_x_reverse()
```

