---
title: "Predicting Ordinal Interaction Climbing"
output: html_notebook
---


# Predicting climbing from fossil data:

Take model lists, then use them one by one to predict climbing in the fossil taxa.
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, brms, cmdstanr, here, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
nms <- read_rds(here("Data", "Order_Names.Rds"))

source(here("Code","Name_Change.R"))


```


### Load Data  

```{r}
dat <- read_csv(here("Data", "Extant_Master.csv"))

fdat <- read_csv(here("Data", "Fossil_Master.csv"))

fdat_cln <- fdat %>% janitor::remove_empty(which = "cols") %>% colnames()

#variables to do fossil predictions with
pred_vars <- fdat_cln[c(9:84)]

#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load & Subset Models

Loading our list of log(Mass) models and selecting the ones for which we have fossil measurements. 

```{r}
list_o_lm <- read_rds(here("Data","O_lm_int_mods_mis.Rds"))
#purrr keep_at is great!
list_o2 <- list_o_lm %>% keep_at(pred_vars)

names(list_o2)

rm(list_o_lm)
```
Now, loop through (or purrr) models and predict the climbing scores for each fossil for each model

# Predictions  

## Fossil Functions
```{r}
colz <- c("Genus_species", "log_Mass", names(list_o2), "Specimen_Num")

fd <- fdat %>% select(all_of(colz))

nnn <- function(mod, nm){
 d <-  {{mod}} %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
  select(Genus_species, .draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
}


modes <- function(df){ 
  {{df}} %>% rownames_to_column('id') %>%
  left_join(
    {{df}} %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
}
```

# Extant Functions

```{r}
extant_climb <- c("Caluromys_derbianus", "Tamiasciurus_douglasii","Tupaia_glis", "Cynocephalus_volans", "Glaucomys_sabrinus")

extant_ground <- c("Solenodon_paradoxus", "Atelerix_albiventris",     "Sorex_trowbridgii", "Thomomys_bottae", "Monodelphis_domestica")


old <- c("Eomaia_scansoria", "Sinodelphys_szalayi", "Juramaia_sinensis", "Cokotherium_jiufotangensis", "Ambolestes_zhoui")

multi <- c("Rugosodon_eurasiaticus", "Jeholbaatar_kielanae", "Filikomys_primaevus", "Ptilodus_kummae", "Kryptobaatar_dashzevegi")

primate <- c("Plesiadapis_cookei", "Torrejonia_wilsoni", "Ignacius_clarkforkensis", "Dryomomys_szalayi")

model_dat <- dat %>% filter(Genus_species %in% c(extant_climb, extant_ground))

nnn2 <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NULL) %>% 
    as.data.frame() %>% 
    select(Genus_species, .draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
  
}

nnn3 <- function(mod, nm){
  {{mod}} %>% 
    add_epred_draws(newdata = model_dat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    #allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, .draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4))
}



```

### Plot helpers
```{r}
#var_ord = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Mtl", "TRI", "Ppw", "Cl", #"Mcw", "MRI", "Tmw", "BI", "Pel", "Fsw", "Fdw", "Mcl", "Hdw", "Tl", "Pppl", "Hsw", "IM", "Ul", "Fl", #"Rl", "MANUS2", "Hl", "Ipl", "MANUS", "Ppl", "PES", "PES2") 
##just the "sigs"
#var_ord2 = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Mtl", "TRI", "Ppw", #"Cl", "Mcw", "MRI", "IM", "Ul", "Fl", "Rl", "MANUS2", "Hl", "Ipl", "MANUS", "Ppl", "PES", "PES2")
## just the really important sigs
#var_ord3 = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Rl", "MANUS2", "Hl", #"Ipl", "MANUS", "Ppl", "PES", "PES2")
##pal = c('#66a61e', '#5e1ea6',  '#e6ab02', '#f9581c','#0d57ff')
##with the mean probability
#var_ord4 = c("HPI", "OLI", "FRI", "CI", "FEB", "Uol", "PRTI", "HEB", "HRI", "Rl", "MANUS2", "Hl", #"Ipl", "MANUS", "Ppl", "PES", "PES2", "Mean")

# first one with no ls
# ls cant be used!
#var_acc = c('PES2', 'MANUS', 'PES', 'Ppl', 'MANUS2', 'HPI', 'Hl', 'Ipl', 'Rl', 'Ul', 'OLI', "Fl")

var_acc = c("PES2", "HPI", "PES", "MANUS", "Ppl",  "Hl", "OLI", "Pipl", "MANUS2", "Rl", "Ipl", "Uol", "Fl", "Ul")

```


##TESTING
#### Works

```{r}
ttt <- list_o2$Hl

tt <- ttt %>% 
    add_epred_draws(newdata = fdat, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
  select(Genus_species, .draw, .category, Prob_of_Climbing) %>% 
    arrange(Genus_species, .draw, .category) %>% 
    pivot_wider(names_from = .category, 
                values_from = Prob_of_Climbing,
                #VERY IMPORTANT!!!!
                values_fn = list) %>% 
  # SECOND IMPORTANT THING!!
  unnest(cols = everything()) %>% 
    mutate(.draw = as.factor(.draw)) %>% 
    rename(P1 = "A",
           P2 = "Sc",
           P3 = "T",
           P4 = "B") %>% 
    mutate(var = {{nm}},
           wa_rank = P1 + (2 * P2) + (3 * P3) + (4 * P4)) %>%
  ungroup() 




tt <- tt %>% 
  rownames_to_column('id') %>%
  left_join(
    tt %>% 
      rownames_to_column('id') %>%
      gather(max_rank, max_prob, P1:P4) %>% 
      group_by(id) %>% 
      slice(which.max(max_prob)) %>% select(id, max_rank, max_prob), 
    by = 'id'
  )
```

## TEST PLOTS
```{r}

tt %>% group_by(Genus_species) %>% count(max_rank) %>% drop_na() %>% 
  ggplot(aes(y = Genus_species, x = n, fill = max_rank)) + geom_bar(position = "fill", stat = 'identity')

tt %>% ggplot(aes(y = Genus_species, x = wa_rank)) + stat_halfeye() + xlim(1, 4)
```

##########
## DEAL WTIH "CLIMB" & "GROUND" categories
#############
```{r}
nm <- names(list_o2)

pred_df <- map2(list_o2, nm, ~nnn(.x, .y)) %>% bind_rows() %>% modes() %>% 
  write_csv(here("Data", "Fossil_Ord_Int_Predictions.csv")) %>% 
  mutate(method = "Fossil",
         substrate = NA)


pred_df_ext_full <- map2(list_o2, nm, ~nnn2(.x, .y)) %>% 
  bind_rows() %>% modes() %>% 
  mutate(method = "Full",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))

pred_df_ext_fos <- map2(list_o2, nm, ~nnn3(.x, .y)) %>% 
  bind_rows() %>% modes() %>% 
  mutate(method = "Fossil",
         substrate = case_when(
    Genus_species %in% extant_climb ~ "Climb",
    TRUE ~ "Ground"
  ))


pred_all <- bind_rows(pred_df_ext_full, pred_df_ext_fos, pred_df) %>% filter(var %in% var_acc) %>% 
  write_csv(here("Data", "All_Ord_Int_Predictions.csv"))
```

 
# Whole Shebang  


### function
```{r}
# shading
shades <- data.frame(xmin=seq(1.5,13-1.5, 2),
                     xmax=seq(2.5,13+.5, 2),
                     ymin=0, ymax=Inf)

hplot <- function(groups, method){
  pred_all %>% filter(Genus_species %in% {{groups}},
                         method == {{method}}) %>% 
    mutate(var =  as.factor(var)) %>% 
  ggplot(aes(y = Prob_of_Climbing, 
             x = fct_relevel(var,var_acc), 
             #y = var,
             color = Genus_species)) +
  geom_hline(yintercept = 0.5, linetype = 2, linewidth = 0.5) +
  stat_pointinterval(.width = c(0.5, 0.68268), 
                     #linewidth = c(0.75, 0.5), 
                     position = position_dodge(width = -.6)) + ylim(0,1) +
    labs(x = "", y = "Probability of Climbing") +
  scale_color_manual(values = pal) + theme_pander(gM = F) + 
    geom_rect(inherit.aes = F, 
              data = shades, 
              mapping = aes(xmin=xmin, 
                            xmax=xmax, 
                            ymin = ymin, 
                            ymax = ymax), 
              alpha = 0.125) +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.border = element_rect(colour = "grey40", fill=NA, size=0.7))
}

```

###  big df



### Big Plot
```{r}
pl5 <- hplot(old, "Fossil") + 
  ggtitle("Mesozoic Mammal Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank(),
        panel.grid.major.y = element_blank())

pl6 <- hplot(multi, "Fossil") + 
  ggtitle("Multituberculate Predicitons") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl7 <- hplot(primate, "Fossil") + 
  ggtitle("Primate Predicitons") + 
  theme(#axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())


t3 <- pl5 / pl6 /pl7

t3

ggsave(here("Plots", "Predict_Ord_Int_Fossil.pdf"), height = 8, width = 13)

```


```{r}
pl1 <- hplot(extant_climb, "Full") + 
  ggtitle("Extant Climb Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl2 <- hplot(extant_climb, "Fossil") + 
  ggtitle("Extant Climb Fossil") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl3 <- hplot(extant_ground, "Full") + 
  ggtitle("Extant Ground Full Predictions") + 
  theme(axis.text.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),
        axis.title.y = element_blank())

pl4 <- hplot(extant_ground, "Fossil") + 
  ggtitle("Extant Ground Fossil") + 
  theme(#axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "lines"),)


t1 <- pl1 / pl2 + plot_layout(guides = "collect")

t2 <- pl3 / pl4 + plot_layout(guides = "collect")

wrap_plots(t1, t2, ncol = 1)

ggsave(here("Plots", "Predict_Int_Extant.pdf"), height = 10, width = 13)

```

```{r}
pl2 / pl4 + plot_layout(guides = "collect")

ggsave(here("Plots", "Predict_Int_Extant2.pdf"), height = 6, width = 13)
```



```{r}
wrap_plots(t1, t2, t3, ncol = 1, heights = c(2/7, 2/7, 3/7))

ggsave(here("Plots", "Predict_Int_All.pdf"), height = 16, width = 13)
```

