---
title: "Ordinal Multiple Predictors"
#output: html_notebook
---

# Ordinal Fossil Prediction Models

I need to run a series of models to cover all the combinations of measurements found in the fossil data. 

The steps are:
  - Run the "formula" code to get the list of all the variables for each taxon
  - Run a series of models for each combination of missing data. 
  
Importantly, the names of the fossils need to be updated! I think you added a lot of fossils. These will need to be added to the appropriate spots. 

# Preparation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
var_acc <- read_rds(here("Data", "var_accurate.Rds"))

source(here("Code","Name_Change.R"))
```

### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  filter(Genus_species !=  c('Leopardus_geoffroyi', 
                             'Urocyon_cinereoargenteus')) %>% 
  drop_na(Loc_Ord2) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family)) %>% 
  mutate(Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")))

#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

# Model Fits

Get lists of missing fossil data

```{r}

# Function to generate the formula without NA values
generate_formula <- function(row) {
  # Exclude specific columns (like Mass and existing formula)
  measurement_cols <- names(row)[2:15]  # Adjust indices based on your data
  # Get the non-NA column names and remove any 'NA' string that may be present
  non_na_terms <- measurement_cols[row[measurement_cols] != 'NA' & !is.na(row[measurement_cols])]
  # Construct the formula, ensuring no NA values are included
  new_formula <- paste(non_na_terms, collapse = "+")
  return(new_formula)
}


fdat_avg <- read_csv(here("Data", "Fossil_Master.csv")) %>% 
  group_by(Genus_species) %>% 
  summarise_at(vars(log_Mass:PES2), mean, na.rm = T) %>% 
  select(c(Genus_species, PES2, HPI, PES, MANUS, 
           Ppl, Hl, OLI, Pipl, MANUS2, Rl, Ipl, 
           Uol, Fl, Ul, log_Mass)) 
# Apply the function to each row and create a new column
fdat_avg$formula <- apply(fdat_avg, 1, 
                      generate_formula)

#fdat_avg |> janitor::get_dupes(formula) |> view()
```

### Fossil Formulas
Here's the list of formula's and species

*** THIS NEEDS TO BE UPDATED TO INCLUDE NEW FOSSILS!!**

6 species
- PES2 + PES + MANUS + Ppl + Hl + OLI + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Agilocodon_scansorius, Eomaia_scansoria, Feredocodon_chowi, Maiopatagium_fulculiferum, Rugosodon_eurasiaticus, Sinodelphys_szalayi


3 species
- HPI + MANUS + Ppl + Hl + OLI + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Ignacius_clarkforkensis, Liaoconodon_hui, Vilevolodon_diplomyos

2 species
- PES2 + HPI + PES + MANUS + Ppl + Hl + OLI + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Jeholbaatar_kielanae, Plesiadapis_cookei

2 species
- PES2 + PES + MANUS + Ppl + Hl + Pipl + MANUS2 + Rl + Ipl + Fl : Dryomomys_szalayi, Maotherium_senensis

2 species
- Hl + Rl + Fl + Ul :Repenomamus_giganticus, Repenomamus_robustus

2 species
- MANUS + Ppl + Hl + OLI + MANUS2 + Rl + Ipl + Uol + Ul : Cokotherium_jiufotangensis, Juramaia_sinensis

2 species
- PES + MANUS + Ppl + Hl + OLI + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Shenshou_lui, Xianshou_songae


1 Species:

- MANUS + Ppl + Hl + MANUS2 + Rl + Ipl + Ul : Akidolestes_cifellii

- MANUS + Ppl + Hl + OLI + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Ambolestes_zhoui

- PES2 + PES + MANUS + Ppl + Hl + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Arboroharamiya_allinhopsoni

- PES2 + PES + MANUS + Ppl + Pipl + MANUS2 + Rl + Ipl + Fl + Ul : Arboroharamiya_jenkinsi

- HPI+Hl+OLI+Rl+Uol+Fl+Ul : Filikomys_primaevus

- PES2+PES+Ppl+Hl+Pipl+Ipl : Henkelotherium_guimarotae

- PES2+PES+Hl+Pipl+Rl+Fl : Jeholodens_jenkinsi

- PES2+HPI+PES+Hl+OLI+Pipl+Rl+Uol+Fl+Ul : Kryptobaatar_dashzevegi

- PES2+PES+Pipl+Fl : Ptilodus_kummae



### Too Few Measurements: 

2 species
- FL: Chaoyangodens_lii, Litovoi_tholocephalos

4 species
- Hl + Fl :Gobiconodon_ostromi, Spinolestes_xenarthrosus, Volaticotherium antiquus, Yanoconodon_allini

2 species
- NA: Catopsbaatar_catopsaloides, Yubaatar_zhongyuanensi

1 species
- Hl+Ul : Borealestes_cullinensis

- Rl+Fl : Borealestes_serendipitus

- Fl+Ul : Mirusodens_caii

- Hl : Priacodon_fruitaensis

- Ppl+Uol : Torrejonia_wilsoni

- Hl+Rl+Fl : Zhangeotherium_quiquecuspidens




#### 14 Accurate Variables
```{r}
print(var_acc)
```

#### Extinct Prediction Formula & Prior formula
```{r}
pred_ext <- function(mod, dat) {
  {{mod}} %>% 
    add_epred_draws(newdata = {{dat}}, 
                    resp = "LocOrd2",
                    value = "Prob_of_Climbing",
                    allow_new_levels = TRUE, 
                    re_formula = NA) %>% 
    as.data.frame() %>% 
    select(Genus_species, .category, Prob_of_Climbing) %>% 
  mutate(method = "Fossil",
         substrate = NA)
}

prio <- function(mod){
  get_prior({{mod}},
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "student_t(5, 0, 0.6)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))
}
```


### Model Formulas
These are the variables with missing data that need their values predicted when running the models.

```{r}
PES2_mod <- bf(PES2| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

MANUS_mod <- bf(MANUS| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

PES_mod <- bf(PES| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

Ppl_mod <- bf(Ppl| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

MANUS2_mod <- bf(MANUS2| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

HPI_mod <- bf(HPI| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

Ipl_mod <- bf(Ipl| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()

Pipl_mod <- bf(Pipl| mi() ~ log_Mass + Sl + Hl + Hsw + Hdw + Uol + Ul + Rl + Fl + Fsw + Fdw + Tl + Tmw + (1|gr(Taxon_Upham_style, cov = A))) + gaussian()
```


### Model1
6 species - 13 variables
- PES2 + PES + MANUS + Ppl + Hl + OLI + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul
Agilocodon_scansorius, Eomaia_scansoria, Feredocodon_chowi, Maiopatagium_fulculiferum, Rugosodon_eurasiaticus, Sinodelphys_szalayi

```{r  }

ord_mod <-  bf(Loc_Ord2 ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(MANUS2) +  + mi(Ipl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m_form <- ord_mod + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + MANUS2_mod +  Ipl_mod + Pipl_mod + set_rescor(FALSE)
  
pri = prio(m_form)

mod1 <- brm(m_form,
                    data=dat,
                    refresh = 0,
                    cores = 4,
                    data2 = list(A = A),
                    prior = pri,
                    seed = 145, silent = 2,
                    control=list(max_treedepth=15)
               )

df1 <- pred_ext(mod1, fdat_avg %>% filter(Genus_species %in% c('Agilocodon_scansorius', 'Eomaia_scansoria', 'Feredocodon_chowi', 'Maiopatagium_fulculiferum', 'Rugosodon_eurasiaticus', 'Sinodelphys_szalayi')))

rm(mod1)
```


### Model 2
3 species
- HPI + MANUS + Ppl + Hl + OLI + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Ignacius_clarkforkensis, Liaoconodon_hui, Vilevolodon_diplomyos
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod2 <- bf(Loc_Ord2 ~ mi(HPI) + mi(MANUS) + mi(Ppl) + mi(MANUS2) + mi(Ipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()


m2_form <- ord_mod2 + HPI_mod + MANUS_mod + Ppl_mod + MANUS2_mod + Ipl_mod + set_rescor(FALSE)
                    
pri = prio(m2_form)

mod2 <- brm(m2_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df2 <- pred_ext(mod2, fdat_avg %>% filter(Genus_species %in% c('Ignacius_clarkforkensis', 'Liaoconodon_hui', 'Vilevolodon_diplomyos')))

rm(mod2)
```



### Model 3 
2 species
- PES2 + HPI + PES + MANUS + Ppl + Hl + OLI + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Jeholbaatar_kielanae, Plesiadapis_cookei
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod3 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(MANUS2)  + mi(Ipl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m3_form <- ord_mod3 + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + MANUS2_mod +  Ipl_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m3_form)

mod3 <- brm(m3_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df3 <- pred_ext(mod3, fdat_avg %>% filter(Genus_species %in% c('Jeholbaatar_kielanae', 'Plesiadapis_cookei')))

rm(mod3)
```

### Model 4 
2 species
- MANUS + Ppl + Hl + OLI + MANUS2 + Rl + Ipl + Uol + Ul : Cokotherium_jiufotangensis, Juramaia_sinensis
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod4 <- bf(Loc_Ord2 ~ mi(MANUS) + mi(MANUS2) + mi(Ipl) + mi(Ppl) + Hl + Rl + Ul + Uol + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m4_form <- ord_mod4 + MANUS2_mod + MANUS_mod + Ipl_mod + Ppl_mod  + set_rescor(FALSE)
            
pri = prio(m4_form)

mod4 <- brm(m4_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df4 <- pred_ext(mod4, fdat_avg %>% filter(Genus_species %in% c('Cokotherium_jiufotangensis', 'Juramaia_sinensis')))

rm(mod4)
```

### Model 5 
2 species
- Hl + Rl + Fl + Ul :Repenomamus_giganticus, Repenomamus_robustus
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod5 <-  bf(Loc_Ord2 ~  Hl + Rl + Ul  + Fl + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m5_form <- ord_mod5  
           
pri = prio(m5_form)

mod5 <- brm(m5_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df5 <- pred_ext(mod5, fdat_avg %>% filter(Genus_species %in% c('Repenomamus_giganticus', 'Repenomamus_robustus')))

rm(mod5)
```



### Model 6 
2 species
- PES2 + PES + MANUS + Ppl + Hl + Pipl + MANUS2 + Rl + Ipl + Fl : Dryomomys_szalayi, Maotherium_senensis
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod6 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(MANUS) + mi(PES) + mi(Ppl) + mi(MANUS2) +  mi(Ipl) + mi(Pipl) + Hl + Rl  + Fl + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m6_form <- ord_mod6 + PES2_mod + MANUS_mod + PES_mod + Ppl_mod + MANUS2_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m6_form)

mod6 <- brm(m6_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df6 <- pred_ext(mod6, fdat_avg %>% filter(Genus_species %in% c('Dryomomys_szalayi', 'Maotherium_senensis')))

rm(mod6)
```

### Model 7
2 species
- PES + MANUS + Ppl + Hl + OLI + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Shenshou_lui, Xianshou_songae
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod7 <-  bf(Loc_Ord2 ~ + mi(PES) + mi(MANUS) + mi(Ppl) + mi(MANUS2) + mi(Ppl)+ Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m7_form <- ord_mod7 + MANUS_mod +  PES_mod  + MANUS2_mod  + Pipl_mod + Ppl_mod + set_rescor(FALSE)
         
pri = prio(m7_form)

mod7 <- brm(m7_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df7 <- pred_ext(mod7, fdat_avg %>% filter(Genus_species %in% c('Shenshou_lui', 'Xianshou_songae')))

rm(mod7)
```


## Model 8
- MANUS + Ppl + Hl + MANUS2 + Rl + Ipl + Ul : Akidolestes_cifellii
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod8 <-  bf(Loc_Ord2 ~  mi(MANUS) + mi(Ppl) + mi(MANUS2) + mi(Ipl) + Hl + Rl + Ul + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m8_form <- ord_mod8 + MANUS_mod + Ppl_mod + MANUS2_mod + Ipl_mod + set_rescor(FALSE)
         
pri = prio(m8_form)

mod8 <- brm(m8_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df8 <- pred_ext(mod8, fdat_avg %>% filter(Genus_species %in% c('Akidolestes_cifellii')))

rm(mod8)
```

## Model 9
- MANUS + Ppl + Hl + OLI + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Ambolestes_zhoui
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod9 <-  bf(Loc_Ord2 ~   mi(MANUS) + mi(Ppl) + mi(MANUS2) + mi(Ipl) + mi(Pipl) + Hl + Rl + Ul + Uol + Fl + OLI + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m9_form <- ord_mod9 +  MANUS_mod + Ppl_mod + MANUS2_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m9_form)

mod9 <- brm(m9_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df9 <- pred_ext(mod9, fdat_avg %>% filter(Genus_species %in% c('Ambolestes_zhoui')))

rm(mod9)
```

### Model 10
- PES2 + PES + MANUS + Ppl + Hl + Pipl + MANUS2 + Rl + Ipl + Uol + Fl + Ul : Arboroharamiya_allinhopsoni
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod10 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(PES) + mi(MANUS) + mi(Ppl) + mi(Pipl) + mi(MANUS2) + mi(Ipl) + Hl + Rl + Uol + Fl + Ul +log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m10_form <- ord_mod10 + MANUS2_mod +  MANUS_mod + PES2_mod +PES_mod + Ppl_mod + Pipl_mod + Ipl_mod + set_rescor(FALSE)
           
pri = prio(m10_form)

mod10 <- brm(m10_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df10 <- pred_ext(mod10, fdat_avg %>% filter(Genus_species %in% c('Arboroharamiya_allinhopsoni')))

rm(mod10)
```


### Model 11
- PES2 + PES + MANUS + Ppl + Pipl + MANUS2 + Rl + Ipl + Fl + Ul : Arboroharamiya_jenkinsi
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod11 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(PES) + mi(MANUS) + mi(Ppl) + mi(Pipl) + mi(MANUS2) + mi(Ipl) + Rl  + Fl + Ul + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m11_form <- ord_mod11 + PES2_mod +  PES_mod + MANUS2_mod + MANUS_mod + Ppl_mod + Ipl_mod + Pipl_mod + set_rescor(FALSE)
           
pri = prio(m11_form)

mod11 <- brm(m11_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df11 <- pred_ext(mod11, fdat_avg %>% filter(Genus_species %in% c('Arboroharamiya_jenkinsi')))

rm(mod11)
```

### Model 12
- HPI + Hl + OLI + Rl + Uol + Fl + Ul : Filikomys_primaevus
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod12 <-  bf(Loc_Ord2 ~ mi(HPI) + Hl + OLI + Rl + Uol + Fl + Ul + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m12_form <- ord_mod12 + HPI_mod + set_rescor(FALSE)
           
pri = prio(m12_form)

mod12 <- brm(m12_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df12 <- pred_ext(mod12, fdat_avg %>% filter(Genus_species %in% c('Filikomys_primaevus')))

rm(mod12)
```

### Model 13
- PES2 + PES + Ppl + Hl + Pipl + Ipl : Henkelotherium_guimarotae
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod13 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(PES) + mi(Ppl) + mi(Pipl) + mi(Ipl) + Hl +log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m13_form <- ord_mod13 + PES2_mod +  PES_mod + Ppl_mod + Pipl_mod + Ipl_mod + set_rescor(FALSE)
           
pri = prio(m13_form)

mod13 <- brm(m13_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df13 <- pred_ext(mod13, fdat_avg %>% filter(Genus_species %in% c('Henkelotherium_guimarotae')))

rm(mod13)
```

### Model 14
PES2 + PES + Hl + Pipl + Rl + Fl  Jeholodens_jenkinsi
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod14 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(PES) + mi(Pipl) + Hl + Rl  + Fl  +log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m14_form <- ord_mod14 + PES2_mod +  PES_mod + Pipl_mod  + set_rescor(FALSE)
           
pri = prio(m14_form)

mod14 <- brm(m14_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df14 <- pred_ext(mod14, fdat_avg %>% filter(Genus_species %in% c('Jeholodens_jenkinsi')))

rm(mod14)
```


### Model 15
- PES2 + HPI + PES + Hl + OLI + Pipl + Rl + Uol + Fl + Ul : Kryptobaatar_dashzevegi
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod15 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(PES) + mi(HPI) + mi(Pipl) + Hl + OLI + Rl + Uol + Fl + Ul + log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m15_form <- ord_mod15 + PES2_mod + PES_mod + Pipl_mod + HPI_mod + set_rescor(FALSE)
           
pri = prio(m15_form)

mod15 <- brm(m15_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df15 <- pred_ext(mod15, fdat_avg %>% filter(Genus_species %in% c('Kryptobaatar_dashzevegi')))

rm(mod15)
```


### Model 16
- PES2 + PES + Pipl + Fl : Ptilodus_kummae
```{r  message = FALSE, warning=FALSE, include = FALSE}
ord_mod16 <-  bf(Loc_Ord2 ~ mi(PES2) + mi(PES) + mi(Pipl) + Fl  +log_Mass + (1|Genus_species) + (1|gr(Taxon_Upham_style,cov = A))) + cumulative()

m16_form <- ord_mod16 + PES2_mod +  PES_mod  + Pipl_mod  + set_rescor(FALSE)
           
pri = prio(m16_form)

mod16 <- brm(m16_form, data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = pri, seed = 145, silent = 2, control=list(max_treedepth=15)
               )

df16 <- pred_ext(mod16, fdat_avg %>% filter(Genus_species %in% c('Ptilodus_kummae')))

rm(mod16)
```

## Combine Model Outputs
```{r}
pred_df <- bind_rows(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11, df12, df13, df14, df15, df16) %>% mutate(var = 'combined')

pred_df |> write_csv(here("Data", "Fossil_Ord_Preds.csv"))

rm(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11, df12, df13, df14, df15, df16, ord_mod2, ord_mod3, ord_mod4, ord_mod5, ord_mod6, ord_mod7, ord_mod8, ord_mod9, ord_mod10, ord_mod11, ord_mod12, ord_mod13, m2_form, m3_form, m4_form, m5_form, m6_form, m7_form, m8_form, m9_form, m10_form, m11_form, m12_form, m13_form, m14_form, m15_form, m16_form)
```
