---
title: "Tree Plot"
---

# Tree Plot
Plotting the phylogeny with the tips labeled as the locomotor modes

```{r}
pacman::p_load(tidyverse, ggtree, ggtreeExtra, tidytree, treeio, here)

if(!require("tidytree", quietly=TRUE))
     install_version("tidytree", version = "0.4.2")
```

#### Load Data
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  drop_na(Loc_Ord2) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family)) %>% 
  mutate(Loc_bin = case_when(is.na(Loc_bin) ~ 1,
                             TRUE ~ Loc_bin)) %>% 
  mutate(Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A"))) %>% 
  mutate(Loc_bin = as.factor(as.numeric(Loc_bin))) %>% 
  filter(Genus_species != "Apomys_banahao") %>% 
  group_by(Genus_species, Taxon_Upham_style, Loc_Ord2, Loc_bin) %>%  
   summarise_if(is.numeric, mean, na.rm = T) %>% 
  ungroup() %>% 
  select(Genus_species, Taxon_Upham_style, Loc_Ord2, Loc_bin) %>% 
  rename(label = Taxon_Upham_style)


#species in dataset
spp_obs <- dat$label %>% unique()


tree <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tree <- ape::keep.tip(tree, spp_obs)

tr <- tree %>% as_tibble() %>% #as.treedata()
  #rename(Taxon_Upham_style = label) %>% 
  full_join(dat, by = 'label') %>% as.treedata()

```

# Fan Tree

```{r}
p1 <-  ggtree(tr, layout="fan", open.angle=5) +  theme_tree2()


p2 <- p1 + 
     # new_scale_fill() + 
      geom_fruit(
          geom=geom_tile,
          mapping=aes(y=label,  fill=Loc_Ord2),
          #offset=0.08,   # The distance between external layers, default is 0.03 times of x range of tree.
          pwidth=5 # width of the external layer, default is 0.2 times of x range of tree.
      ) #+ 
     #scale_fill_manual(
     #    values=c("#339933", "#dfac03"),
     #    guide=guide_legend(keywidth=0.5, keyheight=0.5, order=3)
     #) 
p2 <- p2 + geom_cladelab(node=408, 
                   label="label", 
                   align=TRUE,
                   hjust=-0.3,
                   vjust = 1,
                   angle=315,
                   offset.text=60, 
                   offset = 50.5,
                   barsize=1.5, 
                   fontsize=4) 
```

```{r}
#tre3 <- ggtree(tr) + theme_tree2() 
#tre2 <- revts(tre3)
tre3 <- ggtree(tr, layout = "fan", open.angle=6, size=0.5) 
tre2 <- revts(tre3) 

tre1 <- tre2 + 
  geom_treescale(x=-189, y = 242, width=39, color='black', linesize = 1,  fontsize = 0) +
  geom_treescale(x=-150, y = 242, width=50, color='grey80', linesize = 1,  fontsize = 0) +
  geom_treescale(x=-100, y = 242, width=50, color='black', linesize = 1,  fontsize = 0) +
  geom_treescale(x=-50, y = 242, width=50, color='grey80', linesize = 1,  fontsize = 0) 
  
#tre1 <- tre2 + geom_treescale(x=-190, width=5, color='red', offset = -5, linesize = 10, fontsize = 0)
tre1 + geom_cladelab(node=408, 
                   label="label", 
                   align=TRUE,
                   hjust=-0.3,
                   vjust = 1,
                   angle=315,
                   offset.text=60, 
                   offset = 50.5,
                   barsize=1.5, 
                   fontsize=4)
```


Code for 2 heatmaps
p1 <- tre1 + 
     # new_scale_fill() + 
      geom_fruit(
          geom=geom_tile,
          mapping=aes(y=label,  fill=Loc_bin),
          offset=-0.95,   # The distance between external layers, default is 0.03 times of x range of tree.
          pwidth=10 # width of the external layer, default is 0.2 times of x range of tree.
      ) + scale_fill_grey(end = 0.95, start = 0)

```{r}
p1 <- tre1 + 
  geom_tippoint(aes(color = Loc_bin), 
                shape = 16, 
                size = 2.5) +
  scale_color_grey(end = 0.9, 
                   start = 0.1, 
                   name = "Binary\nLocomotion", 
                   label = c("Climbing", "Non-Climbing")) 

p2 <- p1 + 
  ggnewscale::new_scale_fill() + 
  geom_fruit(
    geom=geom_tile,
    mapping=aes(y=label,  
                fill=Loc_Ord2),
    offset=-0.96,   # The distance between external layers, default is 0.03 times of x range of tree.
    pwidth=7 # width of the external layer, default is 0.2 times of x range of tree.
      ) + 
  scale_fill_grey(end = 0.9, 
                  start = 0.1, 
                  name = "Ordinal\nLocomotion", 
                  label = c("Inter-Substrate", "Terrestrial", "Scansorial", "Arboreal")) +
  theme(legend.key.size = unit(8, 'mm')) +
  guides(colour = guide_legend(override.aes = list(size=8))) +
  annotate("text", x = -150, y = 235, label = "150") +
  annotate("text", x = -100, y = 239, label = "100") +
  annotate("text", x = -50, y = 240, label = "50") +
  annotate("text", x = -80, y = 236, label = "MYA")

p2 

ggsave(here("Plots","tre_test_fan.pdf"), width = 10, height = 9)
ggsave(here("Plots","tre_test_fan.png"), width = 10, height = 9)
```

## Clade Labels




# Reg Tree

## Build basic tree
```{r}
at = c(-150, -100, -50)
tre2 <- ggtree(tr) + theme_tree2() 
tre1 <- revts(tre2)  + 
  scale_x_continuous("MYA",
                     breaks = at,
                     labels = round(at*-1 , 1)) 

```

Additional things
```{r}
# for making the grey and white scalebar
#tre1 <- tre2 + 
#  geom_treescale(x=-189, y = 242, width=39, color='black', linesize = 1,  fontsize = 0) +
#  geom_treescale(x=-150, y = 242, width=50, color='grey80', linesize = 1,  fontsize = 0) +
#  geom_treescale(x=-100, y = 242, width=50, color='black', linesize = 1,  fontsize = 0) +
#  geom_treescale(x=-50, y = 242, width=50, color='grey80', linesize = 1,  fontsize = 0) 
  
#Testing a clade label
#tre1 + geom_cladelab(node=408, 
#                   label="label", 
#                   align=TRUE,
#                   hjust=-0.3,
#                   vjust = 1,
#                   angle=315,
#                   offset.text=60, 
#                   offset = 50.5,
#                   barsize=1.5, 
#                   fontsize=4)
```

#### Binary Tip labels -not now
```{r}
p1 <- tre1 + 
  geom_tippoint(aes(color = Loc_bin), 
                shape = 15, 
                size = 1) +
  scale_color_grey(end = 0.9, 
                   start = 0.1, 
                   name = "Binary\nLocomotion", 
                   label = c("Climbing", "Non-Climbing"))
```

## Two heat maps
```{r}
p1 <- tre1 + 
     # new_scale_fill() + 
      geom_fruit(
          geom=geom_tile,
          mapping=aes(y=label,  fill=Loc_bin),
          offset=-0.97,   # The distance between external layers, default is 0.03 times of x range of tree.
          pwidth=5.5 # width of the external layer, default is 0.2 times of x range of tree.
      ) + scale_fill_grey(end = 0.9, 
                   start = 0.1, 
                   name = "Binary\nLocomotion", 
                   label = c("Non-Climbing", "Climbing")) +  
  theme(legend.position = c(0.2, 0.7))

p2 <- p1 + 
  ggnewscale::new_scale_fill() + 
  geom_fruit(
    geom=geom_tile,
    mapping=aes(y=label,  
                fill=Loc_Ord2),
    offset=-1.9,   # The distance between external layers, default is 0.03 times of x range of tree.
    pwidth=5.5 # width of the external layer, default is 0.2 times of x range of tree.
      ) + 
  scale_fill_grey(end = 0.9, 
                  start = 0.1, 
                  name = "Ordinal\nLocomotion", 
                  label = c("Inter-Substrate", "Terrestrial", "Scansorial", "Arboreal"))

p2 + geom_cladelab(node=408, 
                   label="should we label\nclades like this?", 
                   #align=TRUE,
                   hjust=0.5,
                   vjust = 1.5,
                   angle=90,
                   #offset.text=60, 
                   offset = 20,
                   barsize=1, 
                   fontsize=4
                   ) +   coord_cartesian(clip = 'off') + 
  theme_tree2(plot.margin=margin(6, 50, 6, 6)) +  
  theme(legend.position = c(0.2, 0.7))
  #hexpand(.2, direction = 1)



ggsave(here("Plots","tre_test_rectangle.pdf"), width = 7, height = 7)
ggsave(here("Plots","tre_test_rectangle.png"), width = 7, height = 7)

ggsave(here("Plots","tre_test_rectangle_tall.pdf"), width = 7, height = 15)
```




