---
title: "Binary Interaction Classification"
output: html_notebook
---

Copy of `Binary_Missing_Models.Rmd` but with the interaction term!

Predicting binary climbing classifications (tree vs. ground) using postcranial measurements and interactions. Models will also incorperate intraspecific variation and phylogenetic variation.

# Preparation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))

source(here("Code","Name_Change.R"))
```

### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  filter(Genus_species !=  c('Leopardus_geoffroyi', 
                             'Urocyon_cinereoargenteus')) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family))
#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

## Description of Missing Data
Follows `Binary_Missing_Models.Rmd`

```{r}
var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))
```

```{r}
var_complete <- var_complete[c(1, 24:35)]
var_missing <- var_missing[c(22:34, 36)]
```

The percentages are stored in the df `Missing_Data_Percents.csv`

# Fit GM Models

## Geometric Mean Complete  

#### Prior 
same prior as above
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Sl * log_gm + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_b_gm <- vector(mode ="list")

for(i in var_complete){
  list_b_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "*log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing GM

Update cannot be used with multivariate models

Prior must be called in the loop



#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")*log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_gm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_gm %>% write_rds(here("Data","B_LSR_gm_mods.Rds"))
```



# Fit Size Free Models

## Geometric Mean Complete  

#### Prior 
same prior as above
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Sl  + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_b_nm <- vector(mode ="list")

for(i in var_complete){
  list_b_nm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing GM

Update cannot be used with multivariate models

Prior must be called in the loop



#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_nm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_nm %>% write_rds(here("Data","B_LSR_NOMASS_mods.Rds"))
```

# Fit GM NoInt Models


#### Prior  
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Uol + log_gm + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```


#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide'}

list_b_gm <- vector(mode ="list")

for(i in var_complete){
  list_b_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "+log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing log(Mass)

Update cannot be used with multivatiate models

Prior must be called in the loop


#### Run Loop

```{r message = FALSE, warning=FALSE, results = 'hide'}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")+log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_gm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 4,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_gm %>% write_rds(here("Data","B_LSR_gmNoInt_mods.Rds"))

```

# Plotting

```{r}
pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue, ggthemes, ggstar)


list_b_gm <- read_rds(here("Data","B_LSR_gmNoInt_mods.Rds"))
list_b_nm <- read_rds(here("Data","B_LSR_NOMASS_mods.Rds"))
list_b_igm <- read_rds(here("Data","B_LSR_gm_mods.Rds"))
```



```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the MASS SLOPE, then pivots in long, and scales it to probability
cln <- function(df) as_draws_df(df)[2] %>% 
  gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[2]))

# Same for missing
cln2 <- function(df) as_draws_df(df)[17] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[17]))

#for no mass
cln3 <- function(df) as_draws_df(df)[16] %>% gather(var, val) %>% 
  mutate(#val = inv_logit_scaled(val),
         var = names(as_draws_df(df)[16]))

#log_shape = c("lsSl", "lsHl", "lsHsw", "lsHdw", "lsUol", "lsUl", "lsRl", "lsFl", "lsFsw", "lsFdw", "lsTl", "lsTmw", "lsIpl", "lsPppl", "lsMtl", "lsPpl", "lsMcl", "lsTpw", "lsIsl", "lsIl", "lsPel", "lsHpw", "lsMcw", "lsPpw", "lsCl", "lsPipl")

```

```{r message = FALSE, warning=FALSE}
# Function -> pulls the th column, b_ or the slope, then pivots in long, and scales it to probability
lms <- map(list_b_igm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_igm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms_int <- lms %>% bind_rows(lms2) %>% 
  mutate(type = "GM_Interation") 
rm(lms, lms2)

lms <- map(list_b_nm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_nm[14:27], cln3) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms_no <- lms %>% bind_rows(lms2) %>% 
  mutate(type = "No_GM") 
rm(lms, lms2)

lms <- map(list_b_gm[2:13], cln) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "b_",""))

lms2 <- map(list_b_gm[14:27], cln2) %>% 
  bind_rows() %>% mutate(var = str_replace(var, "bsp_Locbin_mi",""))

lms_gm <- lms %>% bind_rows(lms2) %>% 
  mutate(type = "GM_No_Interaction") 
rm(lms, lms2)

lms_gm <- bind_rows(lms_gm, lms_int, lms_no)
```



##Good  Plot
```{r}
pal2 <- LaCroixColoR::lacroix_palette("Orange", n = 30, type = "continuous")[c(1,5,10,12,13,14,15,16,17,18,25,28)]

lms_gm %>% 
  group_by(var) %>% mutate(mean = mean(val)) %>% 
  ggplot(aes(x = val, y = tidytext::reorder_within(var, mean, type), color = mean)) +
  stat_pointinterval(.width = c(.66, .89)) +
  geom_vline(xintercept = 0, linetype = 3) + 
  scale_fill_manual(values = pal) +
  tidytext::scale_y_reordered("") +
  labs(x = "Measurement effect size") +
  #scico::scale_color_scico(palette = "hawaii", end = 0.9, begin = 0.1) +
  scale_color_gradientn(colours = rev(pal2)) +
  artyfarty::theme_scientific() + 
  facet_wrap(~type, scales = 'free_y') +
  theme(strip.background = element_blank(),
        legend.position="none")

ggsave(here("Plots", "Bin_Gm_Compare_plot.pdf"))
```