---
title: "Binary Interaction Classification"
output: html_notebook
---

Copy of `Binary_Missing_Models.Rmd` but with the interaction term!

Predicting binary climbing classifications (tree vs. ground) using postcranial measurements and interactions. Models will also incorperate intraspecific variation and phylogenetic variation.

# Preparation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse,  brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()

var_complete <- read_rds(here("Data", "var_complete.Rds"))
var_missing <- read_rds(here("Data", "var_missing.Rds"))


var_complete_lsr <- var_complete[24:35]
var_complete <- var_complete[1:23]

var_missing_lsr <- var_missing[22:36]
var_missing <- var_missing[1:21]

source(here("Code","Name_Change.R"))
```

### Load data  
All data loading and wrangling in `Code/Data_Load.Rmd`
```{r}
dat <- read_csv(here("Data", "Extant_Master.csv")) %>% 
  filter(Genus_species !=  c('Leopardus_geoffroyi', 
                             'Urocyon_cinereoargenteus')) %>% 
  mutate(Family = case_when(
    Family == 'Callitrichidae (Cebidae)' ~ 'Callitrichidae',
    Family == 'Prionodontidae (Viverridae)' ~ 'Prionodontidae',
    TRUE ~ Family))
#species in dataset
spp_obs <- dat$Taxon_Upham_style %>% unique()

#Color palette
pal = c('#62361B', '#f48a1a', '#e6ab02', '#66a61e', '#31c1bb', '#0d57ff', '#5e1ea6', '#f9581c' , '#f384f8')
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- ape::keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

## Description of Missing Data
Follows `Binary_Missing_Models.Rmd`

The percentages are stored in the df `Missing_Data_Percents.csv`

# Fit Models

## Log(Mass) Complete  

#### Prior  
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Uol * log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```


#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide'}

list_b_lm <- vector(mode ="list")

for(i in var_complete){
  list_b_lm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "*log_Mass+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing log(Mass)

Update cannot be used with multivatiate models

Prior must be called in the loop


#### Run Loop

```{r message = FALSE, warning=FALSE, results = 'hide'}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")*log_Mass+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_Mass + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_lm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_lm %>% write_rds(here("Data","B_lm_int_mods_mis.Rds"))
```



# Fit Models

## Geometric Mean Complete  

#### Prior 
same prior as above
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Sl * log_gm + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_b_gm <- vector(mode ="list")

for(i in var_complete){
  list_b_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "*log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing GM

Update cannot be used with multivariate models

Prior must be called in the loop



#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")*log_gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_gm[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_gm %>% write_rds(here("Data","B_gm_int_mods_mis.Rds"))
```


# Fit LSR Models

## LSR Complete  

#### Prior 
same prior as above
```{r message = FALSE, warning=FALSE, include = FALSE}

p1 = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(normal(0, 0.3), class = sd))
```

#### Prelim model  

```{r message = FALSE, warning=FALSE, include = FALSE, cache=TRUE}
#initial fit
mm <- brm(Loc_bin ~ Sl+  (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = bernoulli(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```

#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

list_b_lsr <- vector(mode ="list")

for(i in var_complete_lsr){
  list_b_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_bin ~", i, "+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = bernoulli(),
                         newdata=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = p1,
                         seed = 145
                         ) 
}

```


## Missing GM

Update cannot be used with multivariate models

Prior must be called in the loop



#### Run Loop
```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}

for(i in var_missing_lsr){
  bin_mod <-  bf(paste0("Loc_bin ~ mi(", i, ")+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")) + bernoulli()
  imp_mod <- bf(paste0(i,"| mi() ~ log_gm + Sl +  
       Hl + Hsw + Hdw + Uol + Ul + Rl + 
       Fl + Fsw + Fdw + Tl + Tmw + 
       (1|gr(Taxon_Upham_style, cov = A))")) + gaussian()
  m_form <- bin_mod + imp_mod + set_rescor(FALSE)
  
  pri <- get_prior(m_form,
  data2 = list(A = A),
           data = dat) %>% 
  mutate(
    prior = case_when(
      class == "b"  ~ "normal(0, 2)",
      class == "sd" ~ "normal(0, 0.3)",
      class == "Intercept" ~ "normal(0, 5)",
      class == "sigma" ~ "normal(0, 0.5)",
      TRUE ~ prior
      ))

  list_b_lsr[[i]]<- brm(m_form,
                         data=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = pri,
                         seed = 145
                         ) 
}

list_b_lsr %>% write_rds(here("Data","B_lsr_int_mods_mis.Rds"))
```

