---
title: "Ordinal 3 Models - No Burrow"
author: "Jon Nations"
date: "`r Sys.Date()`"
---

Predicting Ordinal Locomotion classifications with *3* rankings using postcranial measurements:
  - Arboreal
  - Scansorial
  - Terrestrial

We are dropping Burrowing from this run!

Models will also incorporate intraspecific variation and phylogenetic variation.

Same as `Ordinal_Models.Rmd` but with 4 categories:  

- Arboreal (arboreal and gliding)  
- Scansorial  
- Terrestrial  
- Burrowing (inter-substrate, ssemi-fossorial, substrate submerged?)

## Preperation  

### Load packages and functions  
```{r message = FALSE, warning=FALSE, include = FALSE}

pacman::p_load(tidyverse, googlesheets4, brms, cmdstanr, kableExtra, here, ape, tidybayes, patchwork, glue)

options(brms.backend = "cmdstanr")

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm)

here::i_am("README.md")
here()
```

### Load data  
### Load data  
```{r message = FALSE, warning=FALSE}
dat <- read_sheet("https://docs.google.com/spreadsheets/d/1-eknhyZ1JNnXqhg2kViyzVntC8NGZvILQX-aQQb1Jvk/edit#gid=325036460", na = c("NA", "?", "")) %>%
  select(!NOTES) %>% 
# Recode Ordinal Rankings
  mutate(Loc_Ord = case_when(Loc_mode_Ordinal == "G"  ~ "G",
                             Loc_mode_Ordinal == "A"  ~ "A",
                             Loc_mode_Ordinal == "Sc" ~ "Sc",
                             Loc_mode_Ordinal == "T"  ~ "T",
                             Loc_mode_Ordinal == "Is" ~ "Is",
                             Loc_mode_Ordinal == "Sf" ~ "Sf",
                             Loc_mode_Ordinal == "Ss" ~ "Ss",
                             TRUE ~ NA),
         Loc_Ord = as.ordered(Loc_Ord),
         Loc_Ord = fct_relevel(Loc_Ord, c("G","A","Sc","T","Is","Sf","Ss")),
         # Combining the Intersurface and Semifossorial
         Loc_Ord2 = case_when(Loc_mode_Ordinal == "G" ~ "A",
                              Loc_mode_Ordinal == "A" ~ "A",
                              Loc_mode_Ordinal == "Sc" ~ "Sc",
                              Loc_mode_Ordinal == "T" ~ "T",
                              Loc_mode_Ordinal == "Is" ~ "B",
                              Loc_mode_Ordinal == "Sf" ~ "B",
                              Loc_mode_Ordinal == "Ss" ~ "B",
                             TRUE ~ NA),
         Loc_Ord2 = as.ordered(Loc_Ord2),
         Loc_Ord2 = fct_relevel(Loc_Ord2, c("B","T","Sc","A")),
         # No Burrowing Species
         Loc_Ord3 = case_when(Loc_mode_Ordinal == "G" ~ "A",
                              Loc_mode_Ordinal == "A" ~ "A",
                              Loc_mode_Ordinal == "Sc" ~ "Sc",
                              Loc_mode_Ordinal == "T" ~ "T",
                             TRUE ~ NA),
         Loc_Ord3 = as.ordered(Loc_Ord3),
         Loc_Ord3 = fct_relevel(Loc_Ord3, c("T","Sc","A")),
         Loc_bin = case_when(Loc_mode_Bindary == "Ground" ~ 0,
                             Loc_mode_Bindary == "Tree" ~ 1,
                             TRUE ~ NA
                             ),
        # Loc_bin = as.factor(Loc_bin),
         Loc_mode_Categorical = as.factor(Loc_mode_Categorical),
         log_Mass = log(Mass_grams)) %>% 
    relocate(Loc_bin, .after = Loc_mode_Bindary) %>% 
  relocate(Loc_Ord, .after = Loc_mode_Ordinal) %>% 
  relocate(Loc_Ord2, .after = Loc_Ord) %>%
  relocate(Loc_Ord3, .after = Loc_Ord2) %>%
  relocate(log_Mass, .before = Skl) %>% 
#################
# DROP NAs FOR Loc_Ord 3 Prior to Indices!!
##################
  drop_na(Loc_Ord3) %>% 
#################
#Calculate Indices!
#################
  mutate(SI = Sh / Sl,             # Scapular Index
         HRI = Hsw / Hl,           # Humeral Robustness Index
         HPI = Hpw / Hl,           # Humeral Proximal Index
         HEB = Hdw / Hl,           # Humeral Epicondyle Breadth
         HHRI = Hhl / Hl,          # Humeral Head Robustness Index
         HHW = Hhw / Hhl,          # Humeral Head Shape Index
         DI = Hdcw / Hsw,          # Deltopectoral Crest Index
         OLI = Uol / Ul,           # Olecranon Process Length Index
         BI = Rl / Hl,             # Brachial Index
         IM = (Hl+Ul)/(Fl+Tl),     # Intermembral Index
         PRTI = Mcl/(Hl+Rl),       # Palm Robustness Index
         MRI = Mcw / Mcl,          # Metacarpal Robustness
         MANUS = Ppl / Mcl,        # MANUS index
         MANUS2 = (Ppl+Ipl)/Mcl,   # MANUS index with intermed. phalanx
         IRI = Fgh / Fl,           # Gluteal Index
         FRI = Fsw / Fl,           # Femoral Robustness
         FEB = Fdw / Fl,           # Femoral Epicondyle Breadth
         CI = Tl / Fl,             # Crural Index
         TRI = Tmw / Tl,           # Tibial Robustness Index
         #ANR = Anl / Al,          # Astragular Neck Robustness Index
         #CAR = Cal / Cl,          # Calcaneal Robustness Index
         IRI = Il / Pel,           # Illium Robustness Index
         PR = Il / Isl,            # Pelvic Index
         PES = Pppl / Mtl,         # PES INdex
         PES2 = (Pppl+Pipl)/Mtl    # PES with intermediate Phalanx
         ) %>% 
    # geometric mean
  drop_na(Tmw, Fdw, Tl, Fl, Fsw , Sh, Sl, Hdw, Hl, Hsw, Rl, Ul, Uol) %>%
  mutate(gm = ( Tmw * Fdw * Tl * Fl * Fsw  * Sh * Sl * Hdw * Hl * Hsw * Rl * Ul * Uol)^(1/13)) %>%
  relocate(gm, .before = log_Mass) %>% 
  mutate_at(vars(20:74), log) %>% 
  mutate_at(vars(18:96), scale2)

spp_obs <- dat$Taxon_Upham_style %>% unique()
```

### Load Tree & Get Cor Matrix

```{r}
tr <- ape::read.nexus(
  here("Data","MCC_Upham_all_mammals.nex"))
tr <- keep.tip(tr, spp_obs)
A <- ape::vcv.phylo(tr, corr = TRUE)
```

### Fit Models 


Looping over all of the variables to see which ones do a good job predicting the binary tree vs. no-tree categorization

#### Get Prior

```{r message = FALSE, warning=FALSE, results = 'hide'}

p1 <- get_prior(Loc_Ord3 ~ Sl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
  data2 = list(A = A),
           family = cumulative(),
           data = dat) %>% 
    mutate(
      prior = case_when(
        class == "b"  ~ "normal(0, 1)",
        class == "sd" ~ "normal(0, 1)",
        class == "Intercept" ~ "normal(0, 1)",
        TRUE ~ prior
      )
    )
```


```{r message = FALSE, warning=FALSE,  cache=TRUE, results = 'hide'}
#initial fit
mm <- brm(Loc_Ord3 ~ Sl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(),
          data = dat, refresh = 0, cores = 4,
          prior = p1)
```



```{r}
pal = c( '#e6ab02',  '#7570b3', '#66a61e')
pal2 = c('#4d90cd', '#fdb927',   '#0f586c')
cols = c("#7570b3" ,  "#85D4E3" , "#0D7E9A",'#f5f5cb', '#c7e6d4', '#8cd2cd', '#55c3cf', '#3fa4b0', '#187389','#f48a1a', '#e6ab02', '#66a61e', '#85D4E3', '#0D7E9A', '#7570b3','#f6d03d', '#fe7b30', '#ef4a27', '#f384f8', '#625afc', '#0d57ff', '#47a7ff','#5771ff', '#6bae9e', '#31c1bb', '#7af1e1', '#d5e1af', '#f48130','#C60C30', '#00A1DE', '#62361B', '#009B3A', '#f9581c', '#522398', '#E27EA6', '#F9E300', '#565A5C')
```

```{r}
plot(conditional_effects(mm, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)
```

#### Log Mass Loop

```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}
varis <- colnames(dat)[19:95]

list_o3_lm <- vector(mode ="list")

for(i in varis){
  list_o3_lm[[i]]<- update(mm,
                         formula=(paste0("Loc_Ord3 ~", i, "+log_Mass+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = p1
                         ) 
}

list_o3_lm %>% write_rds(here("Data","ordinal3_lm_models.Rds"))
```


#### Geometric Mean Loop

```{r  message = FALSE, warning=FALSE, results = 'hide', cache = TRUE}
varis <- colnames(dat)[19:95]

list_o3_gm <- vector(mode ="list")

for(i in varis){
  list_o3_gm[[i]]<- update(mm,
                         formula=(paste0("Loc_Ord3 ~", i, "+gm+(1|Genus_species)+(1|gr(Taxon_Upham_style,cov = A))")),
                         family = cumulative(),
                         newdata=dat,
                         refresh = 0,
                         cores = 2,
                         data2 = list(A = A),
                         prior = p1
                         ) 
}

list_o3_gm %>% write_rds(here("Data","ordinal3_gm_models.Rds"))
```


```{r}
plot(conditional_effects(list_o3_lm$Ppl, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)

plot(conditional_effects(list_o3_lm$HPI, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)
```



## Model tuning 


I'm not sure how to help the divergent transitions. They seem to appear with the intraspecific variation and the phylogenetic variation. 


```{r message = FALSE}
source("Dirichlet_Prior.R")

ps1 <- get_prior(Loc_Ord3 ~ Ppl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)), data2 = list(A = A),family = cumulative(), data = dat) %>%  mutate(prior = case_when(
  class == "b"  ~ "normal(0,1)",
  class == "sd" ~ "normal(0, 1)",
  class == "Intercept" ~ "student_t(2,0,2)",
  TRUE ~ prior ) )

ps2 <- ps1 %>%  mutate(prior = case_when(
  class == "b"  ~ "student_t(3,0,1)",
  class == "sd" ~ "normal(0, 1)",
  class == "Intercept" ~ "student_t(1,0,2)",
  TRUE ~ prior ) )

ps3 <- ps1 %>%  mutate(prior = case_when(
  class == "b"  ~ "normal(0, 1)",
  class == "sd" ~ "normal(0, 1)",
  class == "Intercept" ~ "normal(0, 1)",
  TRUE ~ prior ) )

ps4 =  c(set_prior("induced_dirichlet(rep_vector(1, nthres+1),0", class = "Intercept"),
          set_prior("student_t(2,0,2)", class = "sd"),
          set_prior("normal(0,1)", class = "b"))

ps5 =  c(set_prior("induced_dirichlet(rep_vector(1, nthres+1),0", class = "Intercept"),
          set_prior("normal(0,1)", class = "sd"),
          set_prior("normal(0,1)", class = "b"))
```


```{r warning = FALSE}

ms_1 <- brm( Loc_Ord3 ~ Ppl + log_Mass + (1|Genus_species)+ (1|gr(Taxon_Upham_style,cov = A)), family = cumulative(), data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = ps1)

ms_2 <- brm( Loc_Ord3 ~Ppl +  + log_Mass +(1|Genus_species)+ (1|gr(Taxon_Upham_style,cov = A)), family = cumulative(), data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = ps2)

ms_3 <- brm( Loc_Ord3 ~ Ppl +  log_Mass +  (1|Genus_species)+ (1|gr(Taxon_Upham_style,cov = A)), family = cumulative(), data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = ps3)

ms_4 <- brm( Loc_Ord3 ~ Ppl +  log_Mass +  (1|Genus_species)+ (1|gr(Taxon_Upham_style,cov = A)), family = cumulative(), data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = ps4, stanvars = dirichlet_prior_stanvar)

ms_5 <- brm( Loc_Ord3 ~ Ppl +  log_Mass +  (1|Genus_species)+ (1|gr(Taxon_Upham_style,cov = A)), family = cumulative(), data=dat, refresh = 0, cores = 4, data2 = list(A = A), prior = ps5, stanvars = dirichlet_prior_stanvar)
```


```{r}
waic(ms_1, ms_2, ms_3, ms_4, ms_5)
```

```{r}
plot(conditional_effects(ms_4, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)

plot(conditional_effects(ms_3, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)

plot(ms_4, N=3, ask=F)
```

## Probit vs. logit
```{r warning = F}
ml <- brm(Loc_Ord3 ~ Ppl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(link = "logit"),
          data = dat, refresh = 0, cores = 4,
          prior = c(set_prior("normal(0,1)", class = "sd"),
                      set_prior("normal(0,1)",  class = "b")))

mp <- brm(Loc_Ord3 ~ Ppl + log_Mass + (1 | Genus_species) +  (1|gr(Taxon_Upham_style, cov = A)),
          data2 = list(A = A),
          family = cumulative(link = "probit"),
          data = dat, refresh = 0, cores = 4,
          prior = c(set_prior("normal(0,1)", class = "sd"),
                      set_prior("normal(0,1)",  class = "b")))
```

```{r}
loo(ml, mp)
```

```{r}
pp_check(ml, type = 'bars', ndraws = 1000)
pp_check(mp, type = 'bars', ndraws = 1000)
```

```{r}
plot(conditional_effects(mp, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)

plot(conditional_effects(ml, categorical = TRUE), plot = F)[[1]] +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal)
```

